\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{The Grand Grimoire of Potions}
\author{Wiley Wiggins, Generated for NaNoGenMo 2024}
\date{}
\begin{document}

\maketitle

\newpage
\section*{Deep Pink Potion}

\addcontentsline{toc}{section}{Deep Pink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 400 ml Spirit of vitriol
  \item a pinch of Paojiang
  \item a pinch of Seeds
  \item 1 cup Box-thorn
  \item 19 teaspoons Byzantine syrup
  \item 1 teaspoon Coriander
  \item 9 shakes White coxcomb
  \item 2 syringes Tentengrass
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Spirit of vitriol alongside a phoenix feather an hour.
  \item Pour the Paojiang into a clean goblet.
  \item Combine the Seeds with clear water and freeze it beside a tranquil lake.
  \item Allow the Box-thorn to be carried away by the wind, then collect what remains.
  \item Dip the Byzantine syrup into a pool of bloodcoloured liquid within a stone circle.
  \item Freeze the Coriander while whispering the name of a forgotten stag.
  \item Secretly exchange the White coxcomb with its reflection in a mirror until it is quite soft.
  \item Mix Tentengrass and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

Seek the deep pink brew in times of careful need, especially overnight. The concoction bestows the ability to manipulate memories, erasing, altering existing enchantments, or create pockets of extra- dimensional storage.

\newpage
\section*{Light Yellow Potion}

\addcontentsline{toc}{section}{Light Yellow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 pieces Guanzhong
  \item a pinch of Fox grease
  \item 7 tablespoons Artificial bile
  \item 8 syringes Xylenol orange, tetrasodium salt
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Guanzhong in a vat of rainbow dye until dawn.
  \item Clean the Fox grease thoroughly before shaking it in a goblet with Artificial bile.
  \item Expose the Artificial bile to the song of a wolf at dawn.
  \item Immerse the Xylenol orange, tetrasodium salt in a urn filled with odorous herbs.
\end{enumerate}

\textbf{Effects:}

It is said that the imaginary light yellow cordial can alter one's fate in the sun. After consuming the potion connects the user can temporarily phase through solid matter. Consuming the elixir grants the ability to mimic any sound or voice.

\newpage
\section*{Greenvested Potion}

\addcontentsline{toc}{section}{Greenvested Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Turkey Rhubarb
  \item Half a cup Potassium hydroxide
  \item 8 shakes Canterbury bells
  \item 5 ampoules Peach stones
  \item a pinch of Parsnip
  \item Half a portion St. John's wort
  \item a pinch of Love in a mist
  \item 4 mouthfuls Gall of a bird of prey
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper ancient words to the Turkey Rhubarb while it rests in a deep, glacial cave.
  \item Collect the dew from Potassium hydroxide under the stars and mix it with Canterbury bells.
  \item When you have mixed Canterbury bells thoroughly, pour into a dish and cover with a crock.
  \item Suspend the Peach stones above a flame until it turns blue-violet.
  \item Let the Parsnip bask under a meteor shower to enhance its properties.
  \item Immerse the St. John's wort in a urn filled with musky herbs.
  \item Wrap the Love in a mist in leaves of Gall of a bird of prey and bury it at the top of a mountain.
  \item Submerge the Gall of a bird of prey and the mixture in a bath of shellcocoacoloured light for two days.
\end{enumerate}

\textbf{Effects:}

It is said that the sinister greenvested cordial can alter one's fate in the sun. The potion provides a temporary bond with a mere gesture.

\newpage
\section*{Whitewash Potion}

\addcontentsline{toc}{section}{Whitewash Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Willow
  \item 8 shakes Persian buttercup
  \item 10 ampoules Fennel
  \item 1/2 cups Oil of Rue
  \item 9 tablespoons amber
  \item 1 portion Alum
  \item 7 handfuls Senna
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Willow beside a tranquil lake to dry and then combine it with Persian buttercup.
  \item Write incantations on the Persian buttercup using a small bone from a unicorn.
  \item Tie the Fennel with threads of goldbronze silk before combining it with Oil of Rue.
  \item Grind the Oil of Rue and scatter it near a roaring fire, then collect the remnants.
  \item Place the amber atop a vessel and let the essence drip into it.
  \item Blend the Alum with the tears of a unicorn collected until dawn.
  \item Gently fold the Senna into the the mixture, ensuring no air bubbles form.
\end{enumerate}

\textbf{Effects:}

The hopeless spirits of the serpent bless the whitewash potion with unmatched potency. After consuming the potion, the potion makes the user 's dreams become reality upon waking, manifesting visions from their own body into living metal, gaining immense strength, durability, and restoring balance. Consuming the potion causes the user can sense nearby magical artifacts.

\newpage
\section*{Wheat Potion}

\addcontentsline{toc}{section}{Wheat Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 portions White coxcomb
  \item 9 pieces Head of Castrated male sheep
  \item 10 teaspoons Watermelon rind
  \item 1 portion Rucola
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Head of Castrated male sheep the same way as the White coxcomb, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Add the Head of Castrated male sheep by the spoonful, folding until smooth.
  \item Tie the Watermelon rind with threads of sparkly silk before combining it with Rucola.
  \item Immerse the Rucola in a crucible filled with fragrant herbs.
\end{enumerate}

\textbf{Effects:}

The wheat essence exudes a sweet and revisionist aroma, enchanting all nearby. After drinking the potion 's fleeting duration.

\newpage
\section*{Steel Blue Potion}

\addcontentsline{toc}{section}{Steel Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 drops Nickel(II) sulfate hexahydrate
  \item 6 tablespoons Strontium nitrate
  \item 8 ampoules Hyssop oil
  \item 5 ampoules Madder
  \item Half a teaspoon Lion fat
  \item 4 syringes Madder
  \item a pinch of Deer grease
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Nickel(II) sulfate hexahydrate bask under true night to enhance its properties.
  \item Freeze the Strontium nitrate while whispering the name of a forgotten armadillo.
  \item Boil the Hyssop oil in a cauldron made of pure earth.
  \item Suspend the Madder above a flame until it turns blue-violet.
  \item Let the Lion fat bask under the comet’s passing to enhance its properties.
  \item Boil the Madder in a crucible made of pure shadow.
  \item Feed the Deer grease to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less odorous.
\end{enumerate}

\textbf{Effects:}

The steel blue philter was gifted to heroes in sinister times under the moonlight. The potion causes the user to the collective consciousness of all living beings, and understanding the very fabric of arcane forces. This elixir enables the drinker to see invisible entities.

\newpage
\section*{Sausagepink Potion}

\addcontentsline{toc}{section}{Sausagepink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Cardamom
  \item 250 ml Fritillaria
  \item 3 syringes A kind of cocoa
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Fritillaria the same way as the Cardamom, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Boil the Fritillaria in a goblet made of pure fire.
  \item Allow the A kind of cocoa to rest within a circle of unicorn stones an hour.
\end{enumerate}

\textbf{Effects:}

The sausagepink remedy restores vitality with its excessive properties of shadow. This potion transforms the drinker to command the flow of time, allowing them to become a living conduit for cosmic energies, wards off ill fortune, and withstand impacts that would harm a solid form.

\newpage
\section*{Rebeccapurple Potion}

\addcontentsline{toc}{section}{Rebeccapurple Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 drops Marrow or gourd seeds
  \item 290 gram Mercuric sulfate
  \item 1 shake 3,6-Disulfonaphthalene-1,8-bis(olate)
  \item 8 drops L-Ascorbic acid
  \item 7 syringes Whole melon
  \item 7 mouthfuls Lobelia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the Marrow or gourd seeds in one vessel, and the Mercuric sulfate likewise in one vessel.
  \item Collect the dew from Mercuric sulfate in the sun and mix it with 3,6-Disulfonaphthalene-1,8-bis(olate).
  \item Add the 3,6-Disulfonaphthalene-1,8-bis(olate) by the spoonful, folding until smooth.
  \item Immerse the L-Ascorbic acid in lightning until it becomes translucent.
  \item Freeze the Whole melon alongside a unicorn feather for two days.
  \item Combine the Lobelia with clear water and freeze it under the moonlight.
\end{enumerate}

\textbf{Effects:}

Legends speak of the physical powers held within the rebeccapurple elixir found near a roaring fire. The elixir allows the user immune to fear effects. Upon consumption, the swiftness of rivers, or amplifying their own magical abilities during nighttime, influencing animal behavior, and air to float or as heavy as lead to anchor themselves firmly.

\newpage
\section*{Potion of Heavenliness}

\addcontentsline{toc}{section}{Potion of Heavenliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 300 ml Sufferwood
  \item 10 portions Endive Water
  \item 9 shakes Crocodile
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Sufferwood with clear water and freeze it in a deep, glacial cave.
  \item Whisper ancient words to the Endive Water while it rests at the top of a mountain.
  \item Ferment the Crocodile with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

The heavenliness serum grants amoral abilities during true night. The potion gives insight.

\newpage
\section*{Girlgold Potion}

\addcontentsline{toc}{section}{Girlgold Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 syringes Intolerance
  \item 9 portions Thistle
  \item 1 handful Poppy oil
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the Intolerance along with Thistle to create a sacred ash.
  \item Place the Thistle under the stars to dry and then combine it with Poppy oil.
  \item Dip the Poppy oil into a pool of slate-gray liquid in a deep, glacial cave.
\end{enumerate}

\textbf{Effects:}

The electronic kiwi sages crafted the girlgold serum to heal all wounds. The potion grants night vision, allowing for feats impossible under normal circumstances.

\newpage
\section*{Dark Slate-Gray Potion}

\addcontentsline{toc}{section}{Dark Slate-Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 14 teaspoons Ginger
  \item 7 handfuls Scabious-water
  \item 6 drops Parchment
  \item a pinch of Root of Deadly nightshade
  \item 10 ampoules Honey comb
  \item 340 gram Poppy flower
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of spirit around the Ginger before proceeding.
  \item Place the Scabious-water atop a urn and let the essence drip into it.
  \item Draw symbols of air around the Parchment before proceeding.
  \item Make the Honey comb the same way as the Root of Deadly nightshade, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Tie a red vine ribbon around the Honey comb before proceeding.
  \item Distill the essence of Poppy flower secretly and collect it in a flask.
\end{enumerate}

\textbf{Effects:}

The dark slate-gray essence exudes a pungent and artless aroma, enchanting all nearby. The potion sharpens the drinker to move silently without being seen, moving freely until they choose to return. The elixir grants the power to sense the direction of true north.

\newpage
\section*{Desert Bud Potion}

\addcontentsline{toc}{section}{Desert Bud Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 18 teaspoons Cloves
  \item 3 syringes Burnt cuttle-fish bone
  \item 1 cup Syrup
  \item 5 portions Water mint
  \item Half a cup Sturgeon (fish)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Cloves with the tears of a eagle collected an hour.
  \item Gently massage the Burnt cuttle-fish bone with crushed Syrup during the witching hour.
  \item Write on the Syrup with ink made from Water mint.
  \item When you have mixed Water mint thoroughly, pour into a dish and cover with a crock.
  \item Whisper ancient words to the Sturgeon (fish) while it rests under the stars.
\end{enumerate}

\textbf{Effects:}

The formless pangolin sages crafted the desert bud serum to heal all wounds. Drinking this potion temporarily increases the user can sense the direction of true north. The potion provides the power to weave the strands of magic into tapestries that tell stories, record events, or wield weapons independently.

\newpage
\section*{Potion of Promptness}

\addcontentsline{toc}{section}{Potion of Promptness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Shanzi Mushroom
  \item 3 1/2 cups Cuttlefish
  \item 1 ampoule Wild rose
  \item 2 syringes Artemisia annua
  \item 7 shakes Woody nightshade or black nightshade
  \item 2 portions Ammonium ferrous sulfate hexahydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Shanzi Mushroom with oils derived from armadillo glands.
  \item Boil the Cuttlefish together with Wild rose in a flask until flavourless.
  \item Engrave symbols of the stag onto the Wild rose using a fine tool.
  \item Submerge the Artemisia annua in liquid air and watch for a lavender blush hue.
  \item Gently fold the Woody nightshade or black nightshade into the Ammonium ferrous sulfate hexahydrate, ensuring no air bubbles form.
  \item Submerge the Ammonium ferrous sulfate hexahydrate in liquid earth and watch for a yellowjohns hue.
\end{enumerate}

\textbf{Effects:}

This promptness potion is barren but effective. Upon consumption, the user 's intelligence and memory. Upon consumption, the user to create and manipulate their environment without physical contact.

\newpage
\section*{Berry Crush Potion}

\addcontentsline{toc}{section}{Berry Crush Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 handfuls White calcinated tartar
  \item 60 gram Albizia
  \item 5 handfuls Apocynum venetum
  \item 10 syringes A shrub which bears peppers
  \item a pinch of Red vitriol
  \item 1 shake Shanzi Mushroom
  \item 9 drops Artemisia annua
  \item Half a tablespoon Roots of spanish broom
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of earth around the White calcinated tartar before proceeding.
  \item Tie a light blue ribbon around the Albizia before proceeding.
  \item Chill the Apocynum venetum under the shadow of a passing cloud before adding.
  \item Immerse the A shrub which bears peppers in a cauldron filled with malodorous herbs.
  \item Let the Red vitriol bask under the alignment of the planets to enhance its properties.
  \item Boil the Shanzi Mushroom under the influence of a solar eclipse.
  \item Soak 9 drops of Artemisia annua in water during the witching hour.
  \item Grind the Roots of spanish broom and scatter it under the stars, then collect the remnants.
\end{enumerate}

\textbf{Effects:}

The berry crush essence exudes a sweet and metaphysical aroma, enchanting all nearby. Consuming the potion grants temporary control over their own consciousness and will. After drinking, the user the power to summon a burst of light.

\newpage
\section*{Lightsalmon Potion}

\addcontentsline{toc}{section}{Lightsalmon Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Lapis Lazuli
  \item 50 ml Clover oil
  \item 1 ampoule Sodium thiosulfate, pentahydrate
  \item 5 syringes Berries/seeds of Assyrian plum
  \item 10 pieces Rose oil
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Lapis Lazuli above a water source until it absorbs its essence.
  \item Allow the Clover oil to rest within a circle of wolf stones for two days.
  \item Secretly exchange the Sodium thiosulfate, pentahydrate with its reflection in a mirror for two days.
  \item Expose the Berries/seeds of Assyrian plum to the song of a unicorn at dawn.
  \item Expose the Rose oil to the comet’s passing to absorb its energies.
\end{enumerate}

\textbf{Effects:}

Legends speak of the disappointed powers held within the lightsalmon elixir found in the sun. This potion grants mastery over illusions, cloaking themselves in darkness, or reshape noises into harmonious symphonies that influence emotions.

\newpage
\section*{Potion of Spitefulness}

\addcontentsline{toc}{section}{Potion of Spitefulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 portion White bengewine
  \item Half a portion Seville orange
  \item a pinch of a Hedgehog
  \item 690 gram Haematite
  \item 3/4 cups Lithium sulfate monohydrate
  \item 10 portions Pork gall
  \item a pinch of Snail shell
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the White bengewine along with Seville orange to create a sacred ash.
  \item Submerge the Seville orange in a mixture of a Hedgehog and fire.
  \item Distill a pinch of of a Hedgehog during the alignment of the planets and store it in a pot.
  \item Boil the Haematite in a urn made of pure water.
  \item Immerse the Lithium sulfate monohydrate in a vat of orangeflower dye an hour.
  \item Immerse the Pork gall in shadow until it becomes translucent.
  \item Place the Snail shell atop a urn and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that spitefulness can be attained by those who grind until it is quite soft. Quaffing the potion increases the user 's presence brings about harmony and balance, calming conflicts, healing rifts, or hidden sanctuaries with a touch or a word.

\newpage
\section*{Potion of Materialness}

\addcontentsline{toc}{section}{Potion of Materialness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Dragon Blood
  \item 6 mouthfuls Kochia scoparia
  \item 7 pieces Calcined gypsum
  \item 9 syringes 1,2,4-Trichlorobenzene
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Dragon Blood with rust colored sand and heat secretly.
  \item Place the Kochia scoparia atop a pot and let the essence drip into it.
  \item Distill the essence of Calcined gypsum carefully and collect it in a goblet.
  \item Paint the 1,2,4-Trichlorobenzene with the essence of the mixture beside a tranquil lake.
\end{enumerate}

\textbf{Effects:}

This immoral potion bestows the gift of materialness upon the worthy and unworthy alike. Drinking the potion lets the user can withstand intense g- forces. Drinking the potion on bare skin causes the drinker the power to weave dreams into reality, affecting all senses and capable of deceiving even the harshest environments.

\newpage
\section*{Whitepolled Potion}

\addcontentsline{toc}{section}{Whitepolled Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 portions Pimpernel root
  \item 9 pieces Barley starch
  \item 1 shake Borageroot-water
  \item a pinch of Ma Linzi
  \item 1 1/4 cups Calcium sulfate dihydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Pimpernel root in a urn made of pure water.
  \item Trace your intention in the Barley starch, then cast it in an open flame.
  \item Expose the Borageroot-water to the song of a unicorn at dawn.
  \item Boil the Ma Linzi in a bowl made of pure water.
  \item Carefully etch the symbol of shadow onto the surface of the Calcium sulfate dihydrate.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a interlocking whitepolled liquid of water that grants eternal life. After drinking the potion temporarily increases the user 's senses to expand beyond their physical limits, allowing them to summon thunderclouds at will.

\newpage
\section*{Light Blue Potion}

\addcontentsline{toc}{section}{Light Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 teaspoons Worms
  \item 2 mouthfuls Ivory
  \item Half a tablespoon Cocklebur
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Secretly exchange the Worms with its reflection in a mirror until dawn.
  \item Wrap the Ivory in leaves of Cocklebur and bury it in the sun.
  \item Distill Half a tablespoon of Cocklebur during the alignment of the planets and store it in a bowl.
\end{enumerate}

\textbf{Effects:}

Only under pensive skies does the true nature of the light blue potion emerge beside a tranquil lake. The elixir allows the user can sense nearby magical artifacts. After drinking the potion allows the drinker to track any creature they touch, revealing hidden histories and forgotten events.

\newpage
\section*{Dim Gray Potion}

\addcontentsline{toc}{section}{Dim Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Disodium sulfate decahydrate
  \item 1 shake Chayote
  \item a pinch of Oyster shells
  \item 7 shakes Vine buds
  \item 1 tablespoon Cotton
  \item 6 syringes Roots of butcher's broom
  \item 2 1/2 cups Bull's gall
  \item a pinch of Sodium arsenate heptahydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill Half a portion of Disodium sulfate decahydrate during the alignment of the planets and store it in a flask.
  \item Bathe the Chayote in moonlight during a solar eclipse.
  \item Burn the Oyster shells along with Vine buds to create a sacred ash.
  \item Infuse the Vine buds with the spirit of a raven by leaving it in a deep, glacial cave.
  \item Suspend the Cotton above a flame until it turns whitegloved.
  \item Collect the dew from Roots of butcher's broom in a deep, glacial cave and mix it with Bull's gall.
  \item Write on the Bull's gall with ink made from Sodium arsenate heptahydrate.
  \item Infuse the Sodium arsenate heptahydrate with the spirit of a serpent by leaving it under the moonlight.
\end{enumerate}

\textbf{Effects:}

Once every century, a meteor shower empowers the famous dim gray potion. The potion allows the user to emit a loud, deafening shout. Drinking the potion causes the drinker with the power to summon echoes from the moon, and wisdom accumulated over generations.

\newpage
\section*{Potion of Bountifulness}

\addcontentsline{toc}{section}{Potion of Bountifulness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon papaya
  \item 4 portions Periwinkle
  \item 2 mouthfuls Wild parsley
  \item 1 ampoule Verbena seeds
  \item Half a tablespoon Watermelon frost
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the papaya to the song of a wolf at dawn.
  \item Boil the Periwinkle in a bowl made of pure air.
  \item Collect the dew from Wild parsley at the top of a mountain and mix it with Verbena seeds.
  \item Place the Verbena seeds under the moonlight to dry and then combine it with Watermelon frost.
  \item Mix the powdered Watermelon frost with goldtooled sand and heat delicately.
\end{enumerate}

\textbf{Effects:}

Legends tell of a hissing bountifulness elixir discovered under the stars. After drinking the potion enables the user can create illusions visible to others. The potion endows the user 's luck in all who behold them.

\newpage
\section*{Froggreen Potion}

\addcontentsline{toc}{section}{Froggreen Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 handfuls Holly leaf
  \item 4 portions Even money grass
  \item 4 pieces Gum of juniper trees
  \item 2 tablespoons Red stone fat
  \item 14 teaspoons Isatin
  \item 9 syringes Bay berries
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Holly leaf in liquid shadow and watch for a baldpink hue.
  \item Mould balls as large as the fist, of Even money grass and Gum of juniper trees.
  \item Chill the Gum of juniper trees under the shadow of a passing cloud before adding.
  \item Immerse the Red stone fat in a vat of raspberry whip dye for two days.
  \item Chill the Isatin under the shadow of a passing cloud before adding.
  \item Boil the Bay berries under the influence of the comet’s passing.
\end{enumerate}

\textbf{Effects:}

In antiquity, the unchanging froggreen medicine was known to only a few unicorn sages. Drinking the potion, the user to nudge events toward desired outcomes. The potion causes the user with the essence of storms, or assistance in times of great need.

\newpage
\section*{Potion of Lyricalness}

\addcontentsline{toc}{section}{Potion of Lyricalness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 mouthfuls Pap-kind of bready soup
  \item 8 shakes Chicken fat
  \item 400 gram Spike: Lavendula, French Lavender
  \item 2 teaspoons Soapwort, hedge pink
  \item 3 shakes Apple juice
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently massage the Pap-kind of bready soup with crushed Chicken fat overnight.
  \item Tie the Chicken fat with threads of glittery silk before combining it with Spike: Lavendula, French Lavender.
  \item Place the Spike: Lavendula, French Lavender atop a flask and let the essence drip into it.
  \item Strike the Soapwort, hedge pink with a rod of pure shadow precisely at midnight.
  \item Place the Apple juice inside a circle drawn with blackbearded chalk for two days.
\end{enumerate}

\textbf{Effects:}

The fragrant scent of the lyricalness brew indicates its pallid potency. After drinking, the user mastery over illusions, and breaking curses with a touch.

\newpage
\section*{Potion of Steepness}

\addcontentsline{toc}{section}{Potion of Steepness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 ampoules Potassium cyanide
  \item 275 ml Distilled vinegar
  \item 6 pieces Glutinous rice root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Potassium cyanide to the song of a stag at dawn.
  \item Blend the Distilled vinegar with the tears of a phoenix collected an hour.
  \item Paint the Glutinous rice root with the essence of the mixture within a stone circle.
\end{enumerate}

\textbf{Effects:}

Consuming the steepness philter allows one to commune with pangolin spirits. The potion grants night vision, allowing them to relive moments from their own past, enhancing magical abilities. This elixir transforms the user the power to manipulate memories, erasing, altering weather patterns or rallying beasts to their side.

\newpage
\section*{Potion of Pliantness}

\addcontentsline{toc}{section}{Potion of Pliantness}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 ampoules Calcinate Tartar
  \item 4 shakes Lithium hydroxide hydrate
  \item Half a cup Balsam tree wood
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Calcinate Tartar inside a circle drawn with tartan chalk until dawn.
  \item Place the Lithium hydroxide hydrate atop a cauldron and let the essence drip into it.
  \item Whisper a solar eclipse over the Balsam tree wood, then immerse it in earth.
\end{enumerate}

\textbf{Effects:}

The precarious potion of pliantness was lost until rediscovered under the moonlight. Upon consumption, the drinker can project their consciousness into the physical and spiritual realms.

\newpage
\section*{Grey Potion}

\addcontentsline{toc}{section}{Grey Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 ampoules Goat dung
  \item 17 teaspoons Yellow leather
  \item 5 handfuls Mao Dongqing
  \item 13 teaspoons Musk-rose water
  \item 10 mouthfuls Phenol
  \item 9 pieces Imidazole
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of water onto the surface of the Goat dung.
  \item Steep the Yellow leather in fire and stir quickly.
  \item Hang the Mao Dongqing above a spirit source until it absorbs its essence.
  \item Immerse the Musk-rose water in a vat of dark slate-gray dye for two days.
  \item Write on the Phenol with ink made from Imidazole.
  \item Burn the Imidazole along with the mixture to create a sacred ash.
\end{enumerate}

\textbf{Effects:}

During the alternative festival of a solar eclipse, the grey potion flows freely. The potion grants the ability to transmute their own magical abilities.

\newpage
\section*{Potion of Voluminousness}

\addcontentsline{toc}{section}{Potion of Voluminousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 275 ml Prickly Ash
  \item Half a piece Orpine
  \item 10 ml Common flea-bane mucillage
  \item 10 handfuls Aubergines
  \item 1 syringe Monosodium phosphate monohydrate
  \item 6 drops Mud
  \item 10 pieces Agnus Castus
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Prickly Ash within a stone circle and mix it with Orpine.
  \item Dip the Orpine into a pool of forest green liquid in the sun.
  \item Bathe the Common flea-bane mucillage in moonlight during a solar eclipse.
  \item Distill 10 handfuls of Aubergines during the comet’s passing and store it in a goblet.
  \item Paint the Monosodium phosphate monohydrate with the essence of Mud in a deep, glacial cave.
  \item Freeze the Mud while whispering the name of a forgotten armadillo.
  \item Submerge the Agnus Castus and the mixture in a bath of snow light an hour.
\end{enumerate}

\textbf{Effects:}

The specific masters knew that voluminousness could be bottled in this brew. The elixir transforms the drinker 's charisma and persuasion skills.

\newpage
\section*{Dark Turquoise Potion}

\addcontentsline{toc}{section}{Dark Turquoise Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 tablespoons Hasu
  \item 6 teaspoons parrot
  \item a pinch of Cremor Tartar
  \item 10 tablespoons Lithium hydroxide hydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Hasu in a deep, glacial cave and mix it with parrot.
  \item Immerse the parrot in shadow until it becomes translucent.
  \item Boil the Cremor Tartar together with Lithium hydroxide hydrate in a urn until theological.
  \item Suspend the Lithium hydroxide hydrate above a flame until it turns greenish.
\end{enumerate}

\textbf{Effects:}

The dark turquoise mixture bubbles with rotten energy of water. The concoction endows the imbiber with the dawn 's first light.

\newpage
\section*{Light Goldenrod Yellow Potion}

\addcontentsline{toc}{section}{Light Goldenrod Yellow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 handfuls Blood-root roots
  \item 55 ml Two pointed
  \item a pinch of Dill oil
  \item Half a tablespoon Dahlia
  \item 110 ml Vine seeds
  \item Half a portion Dimethylglyoxime
  \item Half a portion xanthophyll
  \item 4 portions Cuttle fish bone
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Two pointed the same way as the Blood-root roots, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item You may place the Two pointed in one vessel, and the Dill oil likewise in one vessel.
  \item Submerge the Dill oil in a mixture of Dahlia and shadow.
  \item Dip the Dahlia into a pool of violet-red liquid within a stone circle.
  \item Blend the Vine seeds with the tears of a armadillo collected overnight.
  \item Secretly exchange the Dimethylglyoxime with its reflection in a mirror an hour.
  \item Sing to the xanthophyll until it resonates with lightning.
  \item Strike the Cuttle fish bone with a rod of pure spirit precisely at midnight.
\end{enumerate}

\textbf{Effects:}

In antiquity, the acrobatic light goldenrod yellow medicine was known to only a few pangolin sages. The potion grants the ability to absorb and neutralize magical energies directed at the speed of light.

\newpage
\section*{Bluehued Potion}

\addcontentsline{toc}{section}{Bluehued Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 mouthfuls Acetonitrile
  \item 9 ampoules melon
  \item 4 shakes Big belly skin
  \item 1 1/4 cups Lees/Dregs of oil
  \item a pinch of Nasturtium
  \item 1 ampoule Bread
  \item Half a portion Danzhu
  \item 6 shakes Grass-hopper
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the Acetonitrile along with melon to create a sacred ash.
  \item Trace your intention in the melon, then cast it in an open flame.
  \item Boil the Big belly skin under the influence of a meteor shower.
  \item When you have mixed Lees/Dregs of oil thoroughly, pour into a dish and cover with a crock.
  \item Boil the Nasturtium in a urn made of pure shadow.
  \item Wrap the Bread in leaves of Danzhu and bury it under the moonlight.
  \item Allow the Danzhu to be carried away by the wind, then collect what remains.
  \item Boil the Grass-hopper in a cauldron made of pure earth.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a physical bluehued liquid of earth that grants eternal life. The potion endows the imbiber with the sight of the universe and witness celestial events occurring light- years away. After consuming the elixir, the user with a touch.

\newpage
\section*{Tartan Potion}

\addcontentsline{toc}{section}{Tartan Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 460 ml Vine leaves
  \item a pinch of Asarabacca
  \item a pinch of Arborvitae leaves
  \item 9 handfuls Vinegar
  \item 1000 gram Burnt bread
  \item 7 tablespoons Butanedioic acid
  \item 485 ml Mercury cloride
  \item 1 mouthful White Pond Lily
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Vine leaves atop a pot and let the essence drip into it.
  \item Combine the Asarabacca with clear water and freeze it under the stars.
  \item Gently massage the Arborvitae leaves with crushed Vinegar overnight.
  \item Freeze the Vinegar alongside a kiwi feather an hour.
  \item Immerse the Burnt bread in a pot filled with odorous herbs.
  \item When you have mixed Butanedioic acid thoroughly, pour into a dish and cover with a crock.
  \item Soak 485 ml of Mercury cloride in water until it is quite soft.
  \item Anoint the White Pond Lily with oils derived from pangolin glands.
\end{enumerate}

\textbf{Effects:}

It is said that the furry tartan cordial can alter one's fate within a stone circle. This elixir transforms the user to interact with mythical creatures, traverse fantastical landscapes, and breaking curses with a celestial being, receiving guidance, protection, or bending light to become a living conduit for cosmic energies, able to manipulate sound waves, creating illusions, cloaking themselves in darkness. Consuming the potion grants the drinker to perceive and manipulate the gravitational pull affecting objects around them appears nearly frozen, allowing the user 's luck in all who hear it, compelling creatures and even the harshest environments.

\newpage
\section*{Potion of Ergodicity}

\addcontentsline{toc}{section}{Potion of Ergodicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 handfuls Sea-fennel, samphire
  \item 5 syringes Cinnabar
  \item 950 gram Common vetch
  \item 3 ampoules Borax
  \item Half a tablespoon Sage leaves
  \item 5 pieces Gourd tea
  \item 8 mouthfuls Pyridine
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Sea-fennel, samphire secretly before shaking it in a flask with Cinnabar.
  \item Trace your intention in the Cinnabar, then cast it in an open flame.
  \item Ferment the Common vetch for 1 to ten years.
  \item Boil the Borax together with Sage leaves in a crucible until noncommittal.
  \item Burn the Sage leaves along with Gourd tea to create a sacred ash.
  \item Blend the Gourd tea with the tears of a stag collected during the witching hour.
  \item Distill the essence of Pyridine delicately and collect it in a urn.
\end{enumerate}

\textbf{Effects:}

Legends tell of a solemn ergodicity elixir discovered under the stars. After consuming the potion makes the user the power to summon and control spectral hands that can manipulate small amounts of water. After drinking, the swiftness of rivers, or unlock hidden pathways.

\newpage
\section*{Potion of Swiftness}

\addcontentsline{toc}{section}{Potion of Swiftness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 tablespoons A yeast
  \item 5 syringes Tomb back
  \item 8 portions Valerian
  \item 9 portions Swan fat
  \item 9 syringes Lithospermum
  \item 2 drops Root of colocynth
  \item 9 shakes Sabine, or Savin
  \item 6 teaspoons Nuts or bark of Citron myrobalan
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the A yeast while whispering the name of a forgotten stag.
  \item Chant over the Tomb back while circling it with lightning.
  \item Chill the Valerian under the shadow of a passing cloud before adding.
  \item Secretly exchange the Swan fat with its reflection in a mirror during the witching hour.
  \item Mould balls as large as the fist, of Lithospermum and Root of colocynth.
  \item Submerge the Root of colocynth in a mixture of Sabine, or Savin and air.
  \item Expose the Sabine, or Savin to a solar eclipse to absorb its energies.
  \item Draw symbols of fire around the Nuts or bark of Citron myrobalan before proceeding.
\end{enumerate}

\textbf{Effects:}

This cautionary transforms and purifies the body while corrupting the soul. The concoction bestows the ability to absorb kinetic impacts, redirect magical attacks, or freezing objects momentarily.

\newpage
\section*{Potion of Voluntariness}

\addcontentsline{toc}{section}{Potion of Voluntariness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 teaspoons Raspberry
  \item a pinch of Old oil
  \item 10 drops Broad bean pods
  \item 10 pieces Peakcock dung
  \item 50 gram Partridge
  \item a pinch of Marsh-mallow, white mallow seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Raspberry slowly before shaking it in a goblet with Old oil.
  \item Expose the Old oil to the song of a eagle at dawn.
  \item Tie a blueglancing ribbon around the Broad bean pods before proceeding.
  \item Immerse the Peakcock dung in earth until it becomes translucent.
  \item Carefully etch the symbol of water onto the surface of the Partridge.
  \item Ferment the Marsh-mallow, white mallow seeds for 1 to ten years.
\end{enumerate}

\textbf{Effects:}

This voluntariness potion is complex but effective. The potion allows the individual to communicate with the dawn 's first light. Drinking the potion enhances the user 's ability to control and reshape the landscape, raising mountains, the user to merge with their surroundings, becoming indistinguishable from the environment, defend against threats, or reshape noises into harmonious symphonies that influence emotions.

\newpage
\section*{Light Slate Gray Potion}

\addcontentsline{toc}{section}{Light Slate Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Thymus
  \item a pinch of Cassia Lignea
  \item 2 ampoules Purslane
  \item 1 mouthful Earthenia
  \item 5 ampoules Yuzhou Leulu
  \item 7 drops Root of colocynth
  \item 1 ampoule Potassium acetate
  \item 8 tablespoons Barium acetate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently massage the Thymus with crushed Cassia Lignea until dawn.
  \item Toast the Cassia Lignea quickly over an open fire. Secretly add the Purslane.
  \item Bathe the Purslane in the flames of shadow for purification.
  \item Combine the Earthenia with clear water and freeze it near a roaring fire.
  \item Paint the Yuzhou Leulu with the essence of Root of colocynth at the top of a mountain.
  \item Mix Root of colocynth and Potassium acetate in a sturdy drum.
  \item Place the Potassium acetate atop a urn and let the essence drip into it.
  \item Grind the Barium acetate and scatter it in the sun, then collect the remnants.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the alchemical light slate gray draught, infused with earth. This mystical brew alters the flow of magic around them. Drinking the potion allows the individual to communicate with the essence of the unseen, revealing hidden histories and forgotten events.

\newpage
\section*{Loganberry Potion}

\addcontentsline{toc}{section}{Loganberry Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 mouthfuls Common Borage, Tale-wort/ Rose- campion
  \item 1 shake Blue Cohosh
  \item 1 tablespoon Manganese compounds
  \item 2 tablespoons Borax paste
  \item 1 ampoule Sichuan Fritillaria
  \item 1/4 cups Hollow leg bones
  \item 10 pieces Burnt vitriol
  \item 920 gram Long birthwort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Sing to the Common Borage, Tale-wort/ Rose- campion until it resonates with lightning.
  \item Combine the Blue Cohosh with clear water and freeze it beside a tranquil lake.
  \item Bathe the Manganese compounds in moonlight during the comet’s passing.
  \item Whisper the comet’s passing over the Borax paste, then immerse it in water.
  \item Place the Sichuan Fritillaria in a deep, glacial cave to dry and then combine it with Hollow leg bones.
  \item Whisper the comet’s passing over the Hollow leg bones, then immerse it in earth.
  \item Bathe the Burnt vitriol in the flames of lightning for purification.
  \item Boil the Long birthwort under the influence of a meteor shower.
\end{enumerate}

\textbf{Effects:}

Legends speak of the ordinary powers held within the loganberry elixir found at the top of a mountain. The potion bestows the ability to solve puzzles.

\newpage
\section*{Legal Ribbon Potion}

\addcontentsline{toc}{section}{Legal Ribbon Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 shakes An exhumed piece of clothing
  \item a pinch of Donkey mare's milk
  \item 10 ampoules Magnesium perchlorate
  \item 3/4 cups Water
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the An exhumed piece of clothing in moonlight during a meteor shower.
  \item Place the Donkey mare's milk atop a urn and let the essence drip into it.
  \item Tie the Magnesium perchlorate with threads of winecoloured silk before combining it with Water.
  \item Carefully etch the symbol of shadow onto the surface of the Water.
\end{enumerate}

\textbf{Effects:}

The legal ribbon mixture bubbles with ornate energy of fire. Upon consumption, the user to become a living conduit for elemental forces, protecting themselves and those nearby from curses, hexes, and restoring balance.

\newpage
\section*{Potion of Dryness}

\addcontentsline{toc}{section}{Potion of Dryness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 syringes Trachelospermi
  \item 5 portions White water lily
  \item 18 teaspoons Ivy bark
  \item 10 handfuls Eye-bright water
  \item a pinch of Cinnamon
  \item a pinch of Root of Snakeweed, bistort, adderword
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Trachelospermi in leaves of White water lily and bury it at the top of a mountain.
  \item Suspend the White water lily above a flame until it turns light slate blue.
  \item Bathe the Ivy bark in moonlight during a meteor shower.
  \item Expose the Eye-bright water to the song of a eagle at dawn.
  \item Expose the Cinnamon to a meteor shower to absorb its energies.
  \item Clean the Root of Snakeweed, bistort, adderword carefully before shaking it in a bowl with the mixture.
\end{enumerate}

\textbf{Effects:}

Only under harmonious skies can the true power of dryness be harnessed. Upon drinking, the user to emit a loud, deafening shout. The potion endows the user can control the direction of true north.

\newpage
\section*{Blue Potion}

\addcontentsline{toc}{section}{Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 100 gram Grass black
  \item 7 tablespoons pear
  \item 5 shakes Lonicera
  \item 7 pieces Mucillage
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the Grass black in one vessel, and the pear likewise in one vessel.
  \item Steep the pear in lightning and stir delicately.
  \item Hang the Lonicera above a spirit source until it absorbs its essence.
  \item Tie the Mucillage with threads of pale green silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

The blue remedy restores vitality with its angelic properties of spirit. Drinking the potion lets the user to control fire. The potion temporarily increases the user, giving the user can manipulate shadows and darkness.

\newpage
\section*{Whitewax Potion}

\addcontentsline{toc}{section}{Whitewax Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 shakes Deer grease
  \item 980 gram Tsaoko
  \item 3 tablespoons Quaking Aspen
  \item a pinch of A green branch
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Deer grease and Tsaoko together with a strand of stag hair.
  \item Ferment the Tsaoko for 1 to ten years.
  \item Make the A green branch the same way as the Quaking Aspen, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Dip the A green branch into a pool of blackguard liquid under the moonlight.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a accidental whitewax liquid of air that grants eternal life. The concoction endows the imbiber with the universe, experiencing profound insights into the astral plane, and influencing the dreams of others to communicate with spirits.

\newpage
\section*{Vulcan Burgundy Potion}

\addcontentsline{toc}{section}{Vulcan Burgundy Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Coxcomb/ woolflower.
  \item 4 mouthfuls Sword Beans
  \item 10 mouthfuls Fox fat
  \item 14 teaspoons beet
  \item 3 handfuls Gentian
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Coxcomb/ woolflower. in moonlight during the comet’s passing.
  \item Hang the Sword Beans above a lightning source until it absorbs its essence.
  \item Make the beet the same way as the Fox fat, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Submerge the beet and Gentian in a bath of light green light during the witching hour.
  \item Draw symbols of earth around the Gentian before proceeding.
\end{enumerate}

\textbf{Effects:}

Under a emotional moon, the potion of vulcan burgundy reveals its secrets at the top of a mountain. Consuming the potion bestows the ability to see the underlying mathematical patterns of the astral plane. After consumption, the user 's presence brings about harmony and balance, calming storms, allowing lucid dreaming, exploration of the wind to travel swiftly across great distances or melding with the essence of the future, glimpsing events yet to occur and conversing with their mind, erect barriers, and air to float or as heavy as lead to anchor themselves firmly.

\newpage
\section*{Potion of Tranquilness}

\addcontentsline{toc}{section}{Potion of Tranquilness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 handfuls Rubescens
  \item Half a portion Almond nut
  \item 10 pieces Water centipede
  \item 19 teaspoons Pomegranate wine
  \item 3 1/4 cups Distaff thistle
  \item 8 ampoules Oil of violets
  \item 7 mouthfuls Goat's dung
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper the alignment of the planets over the Rubescens, then immerse it in lightning.
  \item Place the Almond nut inside a circle drawn with blackrimmed chalk an hour.
  \item Place the Water centipede under the moonlight to dry and then combine it with Pomegranate wine.
  \item Pour the Pomegranate wine into a clean cauldron.
  \item Draw symbols of air around the Distaff thistle before proceeding.
  \item Let the Oil of violets bask under a meteor shower to enhance its properties.
  \item Immerse the Goat's dung in a vat of blue-violet dye during the witching hour.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that tranquilness can be attained by those who expose overnight. The potion grants the ability to transform into pure energy, enabling healing or harm. The potion bestows the ability to manipulate sound waves, creating sonic blasts, dampening noises, or unleash powerful beams of pure energy, enabling the user to forge a temporary bond with a mere gesture.

\newpage
\section*{Flourescent Blue Potion}

\addcontentsline{toc}{section}{Flourescent Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a piece Tangerine peel
  \item 5 mouthfuls Mistle toe bark
  \item 460 gram Oil of Chamomile
  \item 255 ml Lotus seeds
  \item Half a portion Bay berries
  \item 6 pieces 2,7-Naphthalenedisulfonic acid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of water onto the surface of the Tangerine peel.
  \item Dip the Mistle toe bark into a pool of smokeblue liquid within a stone circle.
  \item Collect the dew from Oil of Chamomile at the top of a mountain and mix it with Lotus seeds.
  \item Distill 255 ml of Lotus seeds during the alignment of the planets and store it in a urn.
  \item Place the Bay berries atop a urn and let the essence drip into it.
  \item Collect the dew from 2,7-Naphthalenedisulfonic acid beside a tranquil lake and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

Legends speak of the delightful powers held within the flourescent blue elixir found within a stone circle. The potion bestows the ability to walk through walls.

\newpage
\section*{Greens Potion}

\addcontentsline{toc}{section}{Greens Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 shakes Bread
  \item 310 ml 1,2,3-Propanetricarboxylic acid
  \item 2 1/2 cups Grass black
  \item Half a cup Asparagus
  \item 4 syringes Earthenia
  \item 7 shakes Ash leaves
  \item 5 shakes Ground Berry
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Bread in the flames of shadow for purification.
  \item Boil the 1,2,3-Propanetricarboxylic acid in a goblet made of pure fire.
  \item Allow the Grass black to be carried away by the wind, then collect what remains.
  \item Engrave symbols of the eagle onto the Asparagus using a fine tool.
  \item Tie a Fuseblue ribbon around the Earthenia before proceeding.
  \item Immerse the Ash leaves in a vat of colouring dye an hour.
  \item Strike the Ground Berry with a rod of pure air precisely at midnight.
\end{enumerate}

\textbf{Effects:}

Legends speak of the delightful powers held within the greens elixir found near a roaring fire. This elixir transforms the drinker to communicate with the collective memories of their song.

\newpage
\section*{Blacknailed Potion}

\addcontentsline{toc}{section}{Blacknailed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Antimony
  \item 4 pieces Kidney beans
  \item 2 3/4 cups White lentils
  \item 10 handfuls Tarragon root
  \item 8 handfuls Lead
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Antimony inside a circle drawn with white chalk during the witching hour.
  \item Immerse the Kidney beans in a pot filled with sweet herbs.
  \item Tie the White lentils and Tarragon root together with a strand of unicorn hair.
  \item Freeze the Tarragon root while whispering the name of a forgotten wolf.
  \item Place the Lead in the sun to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

The blacknailed remedy restores vitality with its organic properties of water. The potion grants the drinker the power to manipulate sound waves, creating zones where spells fail, enchantments are suppressed, and perform intricate tasks in the blink of an eye.

\newpage
\section*{Navajo White Potion}

\addcontentsline{toc}{section}{Navajo White Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 portions Goat-Kid  Rennet
  \item 1 drop The tartar formed in barrels and burnt
  \item 5 handfuls Mercury chloride (Hg2Cl2)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Goat-Kid  Rennet with clear water and freeze it within a stone circle.
  \item Chill the The tartar formed in barrels and burnt under the shadow of a passing cloud before adding.
  \item Place the Mercury chloride (Hg2Cl2) atop a flask and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the carnivorous navajo white draught, infused with air. This concoction bestows the ability to manipulate probabilities, tilting odds in their favor, causing unlikely events to occur and conversing with their future selves for guidance. This potion grants the power to manipulate sound, enabling the user 's senses, enhancing their intellect dramatically.

\newpage
\section*{Potion of Gooeyness}

\addcontentsline{toc}{section}{Potion of Gooeyness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 tablespoons Clover
  \item 7 pieces Bergenia
  \item 5 shakes Bay berries
  \item a pinch of Black hellebore
  \item 8 handfuls Ceratophyllum
  \item a pinch of Blackberries
  \item 3 3/4 cups Yizhiren
  \item Half a portion Ammonium aluminum sulfate dodecahydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Steep the Clover in earth and stir quickly.
  \item Burn the Bergenia along with Bay berries to create a sacred ash.
  \item When you have mixed Bay berries thoroughly, pour into a dish and cover with a crock.
  \item Draw symbols of earth around the Black hellebore before proceeding.
  \item Paint the Ceratophyllum with the essence of Blackberries under the moonlight.
  \item Paint the Blackberries with the essence of Yizhiren under the stars.
  \item Whisper true night over the Yizhiren, then immerse it in spirit.
  \item Add the Ammonium aluminum sulfate dodecahydrate by the spoonful, folding until smooth.
\end{enumerate}

\textbf{Effects:}

Only under calm skies can the true power of gooeyness be harnessed. This potion grants the drinker the knowledge of all living beings, granting them the ability to summon and control spectral hands that can manipulate small amounts of water. The potion temporarily dissolves the barriers between worlds, allowing them to speak honestly and reveal secrets they might otherwise conceal.

\newpage
\section*{Fire Brick Potion}

\addcontentsline{toc}{section}{Fire Brick Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 ampoules Pig tooth soap
  \item 8 drops Peach tree leaves
  \item 4 portions Arabic gum
  \item 6 ampoules Red onion
  \item 5 mouthfuls Lentisk flowers
  \item 8 shakes Distilled peach and fern water
  \item 9 mouthfuls Oak leaves
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Pig tooth soap for 1 to ten years.
  \item Grind the Peach tree leaves and scatter it under the stars, then collect the remnants.
  \item Hang the Arabic gum above a shadow source until it absorbs its essence.
  \item Carefully etch the symbol of water onto the surface of the Red onion.
  \item Place the Lentisk flowers atop a pot and let the essence drip into it.
  \item Distill the essence of Distilled peach and fern water boldly and collect it in a goblet.
  \item Strike the Oak leaves with a rod of pure fire precisely at midnight.
\end{enumerate}

\textbf{Effects:}

The pre-programmed spirits of the phoenix bless the fire brick potion with unmatched potency. After drinking, the potion, the drinker dominion over gravity itself, allowing for feats impossible under normal circumstances. Drinking the elixir, the user to see glimpses of the phoenix, granting them the ability to forge unbreakable oaths, binding entities, or dormant powers with a touch.

\newpage
\section*{Coalblack Potion}

\addcontentsline{toc}{section}{Coalblack Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 shakes 1,2-Propylene glycol
  \item 2 3/4 cups Green smallage
  \item a pinch of Rock salt
  \item 7 syringes Red pepper, Capsicum
  \item 380 gram Nasturtium
  \item 15 teaspoons Sodium thiocyanate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of water onto the surface of the 1,2-Propylene glycol.
  \item Write on the Green smallage with ink made from Rock salt.
  \item Whisper ancient words to the Rock salt while it rests near a roaring fire.
  \item Collect the dew from Red pepper, Capsicum within a stone circle and mix it with Nasturtium.
  \item You may place the Nasturtium in one vessel, and the Sodium thiocyanate likewise in one vessel.
  \item Mix the powdered Sodium thiocyanate with powder blue sand and heat gently.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the coalblack potion shimmers with a dark glow under a meteor shower. The potion grants the ability to see moments stretched out, react with superhuman speed, and perform tasks independently.

\newpage
\section*{Potion of Atonicity}

\addcontentsline{toc}{section}{Potion of Atonicity}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Mutton breast
  \item Half a portion Lanthanum chloride
  \item 30 gram Zinc chloride
  \item a pinch of Water lily root
  \item Half a piece Seville orange
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Infuse the Mutton breast with the spirit of a pangolin by leaving it at the top of a mountain.
  \item Tie the Lanthanum chloride with threads of dark gray silk before combining it with Zinc chloride.
  \item Combine the Zinc chloride with clear water and freeze it near a roaring fire.
  \item Wrap the Water lily root in leaves of Seville orange and bury it beside a tranquil lake.
  \item Chill the Seville orange under the shadow of a passing cloud before adding.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the a solar eclipse enhances the power of atonicity within this elixir. The potion cloaks the drinker 's voice into a small localized earthquake.

\newpage
\section*{Bluey Potion}

\addcontentsline{toc}{section}{Bluey Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 1/2 cups Scabious-water
  \item Half a piece spider
  \item 9 ampoules Gum or resin from a fennel plant
  \item a pinch of Almonds
  \item 3 cups Chestnuts in their cases
  \item 6 syringes Fish glue
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Scabious-water and spider together with a strand of eagle hair.
  \item Blend the spider with the tears of a unicorn collected an hour.
  \item Write on the Gum or resin from a fennel plant with ink made from Almonds.
  \item Blend the Almonds with the tears of a wolf collected for two days.
  \item Expose the Chestnuts in their cases to true night to absorb its energies.
  \item Blend the Fish glue with the tears of a wolf collected until dawn.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the outdated bluey draught, infused with water. The elixir enables the drinker to perceive the emotions and thoughts of those around them, absorbing spells, sealing gateways, binding promises with magic that can manipulate plants and make them grow. Drinking the potion causes the user can detect nearby sources of water.

\newpage
\section*{Eggblue Potion}

\addcontentsline{toc}{section}{Eggblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 ampoules Colocynth, Bitter Apple or Gourd
  \item a pinch of Horse tongue
  \item 9 mouthfuls Colt's foot/cough-wort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie a BlueViolet ribbon around the Colocynth, Bitter Apple or Gourd before proceeding.
  \item Mould balls as large as the fist, of Horse tongue and Colt's foot/cough-wort.
  \item Mix Colt's foot/cough-wort and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

It is said that the bold eggblue cordial can alter one's fate in the sun. The potion enables the drinker the ability to step outside of reality, enabling communication with all forms of life, influencing devices, and allowing perfect camouflage in any setting.

\newpage
\section*{Potion of Soberness}

\addcontentsline{toc}{section}{Potion of Soberness}
\textbf{Ingredients:}

\begin{itemize}
  \item 16 teaspoons Fat from a catrated sheep
  \item 3 handfuls Gum or resin from a fennel plant
  \item a pinch of Myrrh
  \item 4 ampoules Saliva
  \item 4 mouthfuls Spicy Polygonum
  \item 405 ml Bromothymol blue
  \item 4 handfuls King's clover seeds
  \item 7 drops A form of storax
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie a coloured ribbon around the Fat from a catrated sheep before proceeding.
  \item When you have mixed Gum or resin from a fennel plant thoroughly, pour into a dish and cover with a crock.
  \item Suspend the Myrrh above a flame until it turns blackbeetles.
  \item Tie the Saliva and Spicy Polygonum together with a strand of pangolin hair.
  \item Strike the Spicy Polygonum with a rod of pure lightning precisely at midnight.
  \item Bathe the Bromothymol blue in moonlight during a solar eclipse.
  \item Place the King's clover seeds inside a circle drawn with bluehued chalk during the witching hour.
  \item Secretly exchange the A form of storax with its reflection in a mirror until it is quite soft.
\end{enumerate}

\textbf{Effects:}

Consuming the soberness philter allows one to commune with serpent spirits. The potion grants the ability to transform into pure energy, traversing great distances or melding with the ability to communicate, gather information, or unlock hidden pathways.

\newpage
\section*{Flourescent Orange Potion}

\addcontentsline{toc}{section}{Flourescent Orange Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 460 gram Rhododendron
  \item Half a tablespoon Sweet-balsam oil
  \item a pinch of Ass's foot
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mould balls as large as the fist, of Rhododendron and Sweet-balsam oil.
  \item Anoint the Sweet-balsam oil with oils derived from unicorn glands.
  \item Expose the Ass's foot to a solar eclipse to absorb its energies.
\end{enumerate}

\textbf{Effects:}

In antiquity, the boring flourescent orange medicine was known to only a few raven sages. The concoction allows the user 's endurance and stamina.

\newpage
\section*{Saltwhite Potion}

\addcontentsline{toc}{section}{Saltwhite Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 ampoules 1-Octanol
  \item 5 shakes Snake slough
  \item 10 drops Pears
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the 1-Octanol along with Snake slough to create a sacred ash.
  \item Gently massage the Snake slough with crushed Pears overnight.
  \item Soak 10 drops of Pears in water during the witching hour.
\end{enumerate}

\textbf{Effects:}

Seek the saltwhite brew in times of perfectible need, especially an hour. The elixir enables the user to fly at will. Rubbing the potion causes the user identify the properties of magical energy with a mere thought.

\newpage
\section*{Blackthumbed Potion}

\addcontentsline{toc}{section}{Blackthumbed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Sea cucumber
  \item 930 gram Chickpea
  \item 1 3/4 cups Hawthorn leaves
  \item 7 drops Argentea
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Sea cucumber in a crucible made of pure lightning.
  \item Freeze the Chickpea alongside a unicorn feather an hour.
  \item Bathe the Hawthorn leaves in the flames of shadow for purification.
  \item Chill the Argentea under the shadow of a passing cloud before adding.
\end{enumerate}

\textbf{Effects:}

The obnoxious hue of the blackthumbed potion is an unmistakable girlwhite to the trained eye. Drinking the potion allows the drinker becomes a beacon of inspiration, enhancing magical abilities.

\newpage
\section*{Blackguard Potion}

\addcontentsline{toc}{section}{Blackguard Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 tablespoons Pumice stone
  \item 3 cups Jalap plant
  \item a pinch of Avens
  \item 465 ml Tarragon
  \item 10 ampoules Thistle
  \item 3 portions Periwinkle
  \item Half a teaspoon Yarrow
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Pumice stone in a vat of violet-red dye during the witching hour.
  \item Pour the Jalap plant into a clean crucible.
  \item Gently fold the Avens into the Tarragon, ensuring no air bubbles form.
  \item Boil the Tarragon under the influence of the alignment of the planets.
  \item Whisper ancient words to the Thistle while it rests under the stars.
  \item Collect the dew from Periwinkle within a stone circle and mix it with Yarrow.
  \item Expose the Yarrow to the song of a armadillo at dawn.
\end{enumerate}

\textbf{Effects:}

The blackguard remedy restores vitality with its jolly properties of lightning. Quaffing the potion allows the drinker to animate their own dreams, allowing for feats impossible under normal circumstances.

\newpage
\section*{Potion of Firmness}

\addcontentsline{toc}{section}{Potion of Firmness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 portions Scamony
  \item 6 ampoules Protactinium
  \item a pinch of Allum
  \item 6 portions Sodium oxalate
  \item 155 ml Dregs/lees
  \item 6 ampoules Bromophenol blue sodium salt
  \item 910 gram Tartar
  \item 9 ampoules Earthworm
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Pour the Scamony into a clean vessel.
  \item Expose the Protactinium to a solar eclipse to absorb its energies.
  \item Burn the Allum along with Sodium oxalate to create a sacred ash.
  \item Add the Sodium oxalate by the spoonful, folding until smooth.
  \item Pour the Dregs/lees into a clean crucible.
  \item Infuse the Bromophenol blue sodium salt with the spirit of a eagle by leaving it in the sun.
  \item Hang the Tartar above a lightning source until it absorbs its essence.
  \item Tie a lavender mist ribbon around the Earthworm before proceeding.
\end{enumerate}

\textbf{Effects:}

Only the esoteric can safely consume the firmness potion during a solar eclipse. Consuming the potion grants immunity to physical harm. After consuming the potion enables the user to emit a pleasant aroma.

\newpage
\section*{Potion of Chronicity}

\addcontentsline{toc}{section}{Potion of Chronicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 drops Kidney beans
  \item 5 drops Nine-section calamus
  \item 4 drops Tomb back
  \item a pinch of Cannabis medicine
  \item 4 mouthfuls Roots of oaken-fern
  \item 2 pieces White mandala
  \item 3 ampoules Silver nitrate
  \item 7 teaspoons Tiger bone
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Kidney beans to the song of a kiwi at dawn.
  \item Add the Nine-section calamus by the spoonful, folding until smooth.
  \item Tie the Tomb back with threads of yellow silk before combining it with Cannabis medicine.
  \item Wrap the Cannabis medicine in leaves of Roots of oaken-fern and bury it in a deep, glacial cave.
  \item Freeze the Roots of oaken-fern alongside a armadillo feather an hour.
  \item Write incantations on the White mandala using a small bone from a kiwi.
  \item Whisper true night over the Silver nitrate, then immerse it in fire.
  \item Combine the Tiger bone with clear water and freeze it at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

The psychotherapeutic art of chronicity is encapsulated in this powder blue potion. After drinking, the user can transform into pure energy, enabling the user 's intelligence and memory.

\newpage
\section*{Potion of Laziness}

\addcontentsline{toc}{section}{Potion of Laziness}
\textbf{Ingredients:}

\begin{itemize}
  \item 140 gram Borageroot-water
  \item a pinch of Barley
  \item 790 gram Ceratophyllum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Borageroot-water in moonlight during a meteor shower.
  \item Ferment the Barley with a pinch of Ceratophyllum for added potency.
  \item Collect the dew from Ceratophyllum beside a tranquil lake and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

The laziness elixir must be handled slowly to unlock its potential. This potion grants the power to manipulate starlight to heal others with careful precision. Drinking the potion allows the individual to communicate with the power to sense the direction of true north.

\newpage
\section*{Shanagolden Potion}

\addcontentsline{toc}{section}{Shanagolden Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 ampoules fennel
  \item 5 pieces turmeric
  \item Half a teaspoon Toads
  \item 3 portions Egg yolk
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the fennel inside a circle drawn with whitetallhatted chalk an hour.
  \item Engrave symbols of the kiwi onto the turmeric using a fine tool.
  \item Mould balls as large as the fist, of Toads and Egg yolk.
  \item Chant over the Egg yolk while circling it with spirit.
\end{enumerate}

\textbf{Effects:}

Legends speak of the perfect powers held within the shanagolden elixir found near a roaring fire. After drinking the potion grants temporary immunity to physical harm. Quaffing the potion grants temporary control over their own dreams, entering the subconscious minds of others through colors that surround them, leading to breakthroughs and artistic masterpieces.

\newpage
\section*{Potion of Stupendousness}

\addcontentsline{toc}{section}{Potion of Stupendousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Male cat fat
  \item 7 syringes Antimony potassium tartrate anhydrous
  \item 7 mouthfuls Olives
  \item 5 tablespoons aconite
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Male cat fat quickly before shaking it in a chalice with Antimony potassium tartrate anhydrous.
  \item Toast the Antimony potassium tartrate anhydrous carefully over an open fire. Boldly add the Olives.
  \item Pour the Olives into a clean vessel.
  \item Mix aconite and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the stupendousness elixir can freeze the forces of fire. The potion cloaks the drinker to wander in sullen fields of time, allowing the user can withstand intense g- forces.

\newpage
\section*{Pale Goldenrod Potion}

\addcontentsline{toc}{section}{Pale Goldenrod Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 pieces Tinglizi
  \item 5 tablespoons Spanish wine
  \item Half a cup Castor oil
  \item 1 drop White wine dregs
  \item 3 handfuls Dodder
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Tinglizi above a spirit source until it absorbs its essence.
  \item Steep the Spanish wine in lightning and stir slowly.
  \item Mould balls as large as the fist, of Castor oil and White wine dregs.
  \item Burn the White wine dregs along with Dodder to create a sacred ash.
  \item Carefully etch the symbol of air onto the surface of the Dodder.
\end{enumerate}

\textbf{Effects:}

In antiquity, the neurological pale goldenrod medicine was known to only a few phoenix sages. Upon drinking, the user gains the ability to walk on water.

\newpage
\section*{Dark Gray Potion}

\addcontentsline{toc}{section}{Dark Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 drops Senna
  \item 5 portions Coffee
  \item 6 syringes Onion roots
  \item a pinch of willow thorn
  \item 2 handfuls Rose
  \item 4 syringes wheat
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Senna for 1 to ten years.
  \item Mould balls as large as the fist, of Coffee and Onion roots.
  \item Ferment the Onion roots for 1 to ten years.
  \item Let the willow thorn bask under the alignment of the planets to enhance its properties.
  \item Whisper a solar eclipse over the Rose, then immerse it in earth.
  \item Make the the mixture the same way as the wheat, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

Crafting the dark gray elixir requires joyous precision and skill to chant over. This elixir grants the power to weave the strands of magic around them, fostering harmony or sowing discord as desired.

\newpage
\section*{Gigglegold Potion}

\addcontentsline{toc}{section}{Gigglegold Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 syringes Lizard/eft oil
  \item 610 gram Gum from Guiacum
  \item Half a teaspoon Eosin
  \item 6 pieces Goldenseed root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of earth onto the surface of the Lizard/eft oil.
  \item Allow the Gum from Guiacum to rest within a circle of stag stones an hour.
  \item Tie the Eosin with threads of bluecircled silk before combining it with Goldenseed root.
  \item Immerse the Goldenseed root in a bowl filled with fragrant herbs.
\end{enumerate}

\textbf{Effects:}

Under a omnivorous moon, the potion of gigglegold reveals its secrets beside a tranquil lake. Consuming the potion, the user 's skin to become a living conduit for cosmic energies, wards off ill fortune, and bring back artifacts from realms unknown. This potion imbues the imbiber with the universe, repairing rifts, healing rifts, healing emotional wounds, and smell.

\newpage
\section*{Navy Potion}

\addcontentsline{toc}{section}{Navy Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 tablespoons White cardamom
  \item 2 ampoules Dirt from spiders
  \item Half a teaspoon Wood-march or sanicle water
  \item 4 ampoules A magnet
  \item 15 ml Bitter oragne
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Infuse the White cardamom with the spirit of a unicorn by leaving it in the sun.
  \item Submerge the Dirt from spiders in liquid water and watch for a orangetainted hue.
  \item Tie the Wood-march or sanicle water with threads of rust colored silk before combining it with A magnet.
  \item Carefully etch the symbol of water onto the surface of the A magnet.
  \item Boil the Bitter oragne under the influence of a solar eclipse.
\end{enumerate}

\textbf{Effects:}

The omnivorous navy potion is a rare and powerful brew of water. This potion envelops the user to traverse dreams, allowing them to see through walls.

\newpage
\section*{Potion of Courageousness}

\addcontentsline{toc}{section}{Potion of Courageousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Cyclamen
  \item 16 teaspoons Pigeon
  \item 1 drop Gold leaf
  \item Half a teaspoon Fennel seeds
  \item 10 tablespoons Rhododendron
  \item 3 syringes Pepper
  \item 1 portion White and
  \item Half a cup Bristle-fern
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently massage the Cyclamen with crushed Pigeon until it is quite soft.
  \item Expose the Pigeon to the song of a kiwi at dawn.
  \item Collect the dew from Gold leaf beside a tranquil lake and mix it with Fennel seeds.
  \item Infuse the Fennel seeds with the spirit of a eagle by leaving it beside a tranquil lake.
  \item Add the Rhododendron by the spoonful, folding until smooth.
  \item Tie a DarkSlateBlue ribbon around the Pepper before proceeding.
  \item Write on the White and with ink made from Bristle-fern.
  \item Paint the Bristle-fern with the essence of the mixture within a stone circle.
\end{enumerate}

\textbf{Effects:}

Consuming the courageousness philter allows one to commune with serpent spirits. The potion bestows the ability to manipulate memories, erasing, altering existing enchantments, dispelling illusions, cloaking themselves in darkness.

\newpage
\section*{Floral White Potion}

\addcontentsline{toc}{section}{Floral White Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 tablespoons Ivy root
  \item a pinch of Salamander blood
  \item 4 portions Lees of wine
  \item 6 handfuls Potassium ferricyanide
  \item 6 syringes Willingxian
  \item Half a cup Cotton seeds
  \item 10 shakes Shanzi Mushroom
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write incantations on the Ivy root using a small bone from a wolf.
  \item Soak a pinch of of Salamander blood in water for two days.
  \item Add the Lees of wine by the spoonful, folding until smooth.
  \item You may place the Potassium ferricyanide in one vessel, and the Willingxian likewise in one vessel.
  \item Gently fold the Willingxian into the Cotton seeds, ensuring no air bubbles form.
  \item Hang the Cotton seeds above a fire source until it absorbs its essence.
  \item Sing to the Shanzi Mushroom until it resonates with lightning.
\end{enumerate}

\textbf{Effects:}

Only under optimistic skies does the true nature of the floral white potion emerge under the moonlight. Upon ingestion, the user to see moments stretched out, react with superhuman speed, and secrets whispered by the drinker to breathe a cloud of mist.

\newpage
\section*{Deep Sky Blue Potion}

\addcontentsline{toc}{section}{Deep Sky Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 ampoules Rosemary water
  \item Half a piece Opium juice
  \item 1 mouthful Polygonum multiflorum
  \item 1 mouthful Skimmed honey
  \item Half a teaspoon Tobacco
  \item a pinch of Sow thistle
  \item 8 shakes Potassium thiocyanate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Opium juice the same way as the Rosemary water, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Distill the essence of Opium juice gently and collect it in a bowl.
  \item Write incantations on the Polygonum multiflorum using a small bone from a pangolin.
  \item Gently massage the Skimmed honey with crushed Tobacco overnight.
  \item Chant over the Tobacco while circling it with fire.
  \item Grind the Sow thistle and scatter it near a roaring fire, then collect the remnants.
  \item Combine the Potassium thiocyanate with clear water and freeze it at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

It is said that the bashful deep sky blue cordial can alter one's fate under the stars. The potion bestows the ability to animate their own ashes. Consuming the potion grants the ability to turn invisible in moonlight.

\newpage
\section*{Forest Green Potion}

\addcontentsline{toc}{section}{Forest Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 tablespoons Foot of a castrated male sheep
  \item 355 ml Arsenic
  \item 6 ampoules Sulfamic acid
  \item Half a teaspoon Astragalus
  \item 6 syringes Bean-flower water
  \item a pinch of Cassia leaves
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Foot of a castrated male sheep inside a circle drawn with mauve jazz chalk until it is quite soft.
  \item Freeze the Arsenic while whispering the name of a forgotten eagle.
  \item Collect the dew from Sulfamic acid in a deep, glacial cave and mix it with Astragalus.
  \item Place the Astragalus atop a flask and let the essence drip into it.
  \item Tie the Bean-flower water with threads of steel blue silk before combining it with Cassia leaves.
  \item Expose the Cassia leaves to the song of a stag at dawn.
\end{enumerate}

\textbf{Effects:}

This forest green ointment is potent and ageless, best used until it is quite soft. The potion grants the ability to gaze into the physical world, for better or worse. The potion endows the imbiber with the power of the unseen, revealing hidden enchantments, dispelling illusions, cloaking themselves in darkness, or unleashing bursts of magical items.

\newpage
\section*{Firebrick Potion}

\addcontentsline{toc}{section}{Firebrick Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 pieces Rattan cane
  \item 350 ml Sanguis
  \item 650 gram Extinguishing wind
  \item 2 portions Blood
  \item 9 drops Lettuce seeds
  \item Half a piece Starch-flower
  \item 11 teaspoons Octopus
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Feed the Rattan cane to a pig and then return later to collect its excrement, mixing it with Sanguis until the smell is less pungent.
  \item Tie the Sanguis and Extinguishing wind together with a strand of kiwi hair.
  \item Submerge the Extinguishing wind in liquid water and watch for a light salmon hue.
  \item Allow the Blood to rest within a circle of raven stones an hour.
  \item Chant over the Lettuce seeds while circling it with spirit.
  \item Place the Starch-flower inside a circle drawn with ivory chalk until it is quite soft.
  \item Immerse the Octopus in a vat of yellowly dye until it is quite soft.
\end{enumerate}

\textbf{Effects:}

This firebrick ointment is potent and bad-intentioned, best used during the witching hour. After drinking, the user to control the direction of the cosmos, granting skills, knowledge, and aids them in navigating both the physical world, for better or worse. The potion enables the drinker 's body to become invisible.

\newpage
\section*{Potion of Fallaciousness}

\addcontentsline{toc}{section}{Potion of Fallaciousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 drops Baihuadan
  \item a pinch of Leak
  \item 10 ampoules Mercury or quicksilver
  \item 250 gram Child's hair
  \item 14 teaspoons Gall
  \item 7 tablespoons Chicken Yafuji
  \item 9 ampoules Female lilac
  \item 85 ml Jujube Seed
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Baihuadan with clear water and freeze it beside a tranquil lake.
  \item Blend the Leak with the tears of a phoenix collected during the witching hour.
  \item Strike the Mercury or quicksilver with a rod of pure air precisely at midnight.
  \item Grind the Child's hair and scatter it near a roaring fire, then collect the remnants.
  \item Expose the Gall to the song of a eagle at dawn.
  \item Dip the Chicken Yafuji into a pool of light yellow liquid in the sun.
  \item Dip the Female lilac into a pool of forest green liquid near a roaring fire.
  \item Write incantations on the Jujube Seed using a small bone from a phoenix.
\end{enumerate}

\textbf{Effects:}

During the alignment of the planets, the fallaciousness potion becomes especially jazzy. The potion endows the user to the spirit of the wind to travel swiftly across great distances or melding with the ability to create a protective aura that repels negative energies, wards off ill fortune, and bring back artifacts from realms unknown. The potion bestows the ability to breathe in toxic environments without harm.

\newpage
\section*{Arctic Rose Potion}

\addcontentsline{toc}{section}{Arctic Rose Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Gum
  \item a pinch of Honeysuckle
  \item 8 drops Camphor
  \item 730 gram Prunella vulgaris
  \item 8 portions Sodium tungstate dihydrate
  \item 3 teaspoons Hibiscus leaf
  \item 6 ampoules Southernwood flowers
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Gum in a mixture of Honeysuckle and lightning.
  \item Immerse the Honeysuckle in a vat of flourescent blue dye overnight.
  \item Blend the Camphor with the tears of a pangolin collected an hour.
  \item Place the Prunella vulgaris inside a circle drawn with vulcan burgundy chalk for two days.
  \item Clean the Sodium tungstate dihydrate carefully before shaking it in a flask with Hibiscus leaf.
  \item Write incantations on the Hibiscus leaf using a small bone from a eagle.
  \item Tie a blue-violet ribbon around the Southernwood flowers before proceeding.
\end{enumerate}

\textbf{Effects:}

In antiquity, the passionate arctic rose medicine was known to only a few phoenix sages. After drinking the elixir grants the user to nudge events toward desired outcomes.

\newpage
\section*{Potion of Lysogenicity}

\addcontentsline{toc}{section}{Potion of Lysogenicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 mouthfuls Bromcresol green
  \item 7 pieces Insect wax
  \item a pinch of A magnet
  \item 85 ml Jin Jinxiang
  \item 2 handfuls Roots of spanish broom
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Bromcresol green with violet-red sand and heat slowly.
  \item Secretly exchange the Insect wax with its reflection in a mirror overnight.
  \item Toast the A magnet delicately over an open fire. Secretly add the Jin Jinxiang.
  \item Suspend the Jin Jinxiang above a flame until it turns light blue.
  \item Wrap the Roots of spanish broom in leaves of the mixture and bury it near a roaring fire.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of lysogenicity, in this poor potion. The potion allows the drinker the ability to disrupt magical constructs, bringing ideas to life as tangible entities under their control. Upon consumption, the user to control fire.

\newpage
\section*{Blackgrouse Potion}

\addcontentsline{toc}{section}{Blackgrouse Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a piece Myrtle seeds
  \item 680 gram Orange Peel
  \item 10 shakes Yam
  \item 3 pieces Clear lessia
  \item 2 handfuls Madder
  \item 1 tablespoon Sea buckthorn
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mould balls as large as the fist, of Myrtle seeds and Orange Peel.
  \item Make the Yam the same way as the Orange Peel, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Submerge the Yam in a mixture of Clear lessia and lightning.
  \item Carefully etch the symbol of earth onto the surface of the Clear lessia.
  \item Burn the Madder along with Sea buckthorn to create a sacred ash.
  \item Suspend the Sea buckthorn above a flame until it turns light pink.
\end{enumerate}

\textbf{Effects:}

The foreign armadillo sages crafted the blackgrouse serum to heal all wounds. The elixir allows the user 's intelligence and memory. The potion enhances the user can create a protective magical shield.

\newpage
\section*{Potion of Neurotoxicity}

\addcontentsline{toc}{section}{Potion of Neurotoxicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 portion Myrtle berries
  \item 2 handfuls Hyena pelt
  \item 7 mouthfuls Gastrodia
  \item 8 portions Golden pills
  \item 270 gram Dill seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Myrtle berries bask under the alignment of the planets to enhance its properties.
  \item Distill the essence of Hyena pelt delicately and collect it in a flask.
  \item Gently massage the Gastrodia with crushed Golden pills during the witching hour.
  \item Collect the dew from Golden pills within a stone circle and mix it with Dill seeds.
  \item Burn the Dill seeds along with the mixture to create a sacred ash.
\end{enumerate}

\textbf{Effects:}

Seek the neurotoxicity potion when the true night lights the sky. This mystical brew alters the flow of energy, traversing through electrical currents, influencing devices, and understanding the very fabric of arcane forces. The elixir grants the ability to step outside of reality, entering the subconscious minds of others.

\newpage
\section*{Potion of Thirstiness}

\addcontentsline{toc}{section}{Potion of Thirstiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 drops Sulfuric acid
  \item 760 gram Potassium carbonate
  \item a pinch of Borate(1-)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Sulfuric acid boldly and collect it in a chalice.
  \item Mould balls as large as the fist, of Potassium carbonate and Borate(1-).
  \item Allow the Borate(1-) to rest within a circle of stag stones until dawn.
\end{enumerate}

\textbf{Effects:}

To master thirstiness, one must consume this unconscious brew an hour. After drinking the potion cures any poison afflicting the user to craft elaborate visions indistinguishable from the stars, guidance from the moon, and thinkers long past, unlocking hidden talents, magical affinities, or trap entities within their woven narratives. The potion grants the ability to breathe fire like a dragon.

\newpage
\section*{Violets Potion}

\addcontentsline{toc}{section}{Violets Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 teaspoon D-Glucose
  \item 110 gram Gum or resin from a fennel plant
  \item 365 ml Mucillage
  \item a pinch of Hyacinth/Jacinth
  \item 10 syringes Cremor Tartar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the D-Glucose inside a circle drawn with grey chalk until it is quite soft.
  \item Tie a bluey ribbon around the Gum or resin from a fennel plant before proceeding.
  \item Engrave symbols of the raven onto the Mucillage using a fine tool.
  \item Chant over the Hyacinth/Jacinth while circling it with fire.
  \item Trace your intention in the Cremor Tartar, then cast it in an open flame.
\end{enumerate}

\textbf{Effects:}

Crafting the violets elixir requires angry precision and skill to freeze. After consumption, the user can transform into a mythical creature of legend, adopting its powers and attributes while retaining flexibility and agility.

\newpage
\section*{Black Potion}

\addcontentsline{toc}{section}{Black Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 drops Partridge
  \item 9 syringes Apple juice
  \item Half a cup Potassium bromide
  \item a pinch of Gravel Root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Partridge in a mixture of Apple juice and shadow.
  \item You may place the Apple juice in one vessel, and the Potassium bromide likewise in one vessel.
  \item Collect the dew from Potassium bromide within a stone circle and mix it with Gravel Root.
  \item Engrave symbols of the kiwi onto the Gravel Root using a fine tool.
\end{enumerate}

\textbf{Effects:}

Under a pre-theoretical moon, the potion of black reveals its secrets near a roaring fire. The concoction imbues the drinker 's will.

\newpage
\section*{Potion of Triplicity}

\addcontentsline{toc}{section}{Potion of Triplicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 540 gram Patience
  \item 6 tablespoons Derived from the Sperm Whale
  \item 5 tablespoons Lettuce
  \item 2 teaspoons Pasqueflower
  \item 1/4 cups Almonds
  \item 1 shake A carrot
  \item Half a cup Male Fern
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill 540 gram of Patience during the comet’s passing and store it in a cauldron.
  \item Mould balls as large as the fist, of Derived from the Sperm Whale and Lettuce.
  \item Mix the powdered Lettuce with slate-gray sand and heat thoroughly.
  \item Expose the Pasqueflower to the song of a phoenix at dawn.
  \item Anoint the Almonds with oils derived from armadillo glands.
  \item Draw symbols of air around the A carrot before proceeding.
  \item Infuse the Male Fern with the spirit of a unicorn by leaving it in a deep, glacial cave.
\end{enumerate}

\textbf{Effects:}

Only the available can safely consume the triplicity potion during a meteor shower. Drinking the potion, the user, giving them the ability to absorb kinetic impacts, redirect magical attacks.

\newpage
\section*{Potion of Analogousness}

\addcontentsline{toc}{section}{Potion of Analogousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 13 teaspoons Green maiden's hair
  \item 10 shakes Soapwort, hedge pink
  \item 12 teaspoons Sodium arsenate heptahydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Green maiden's hair with threads of greengoldenly silk before combining it with Soapwort, hedge pink.
  \item Expose the Soapwort, hedge pink to the song of a armadillo at dawn.
  \item Boil the Sodium arsenate heptahydrate under the influence of true night.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that analogousness can be attained by those who immerse until it is quite soft. After drinking the potion, the potion allows the individual to communicate with the sight of the universe, experiencing profound insights into the physical world. Consuming this potion allows the drinker to grow rapidly around the user to forge a temporary bond with a touch.

\newpage
\section*{Potion of Inwardness}

\addcontentsline{toc}{section}{Potion of Inwardness}
\textbf{Ingredients:}

\begin{itemize}
  \item 300 ml D-Glucose
  \item Half a portion Arabic gum
  \item 10 tablespoons Oil of Camphor
  \item Half a portion Orange Leaves
  \item 3 ampoules Deer heart
  \item a pinch of Root of Snakeweed, bistort, adderword
  \item 14 teaspoons Xylenes
  \item 6 teaspoons 2-Methyl-1-propanol
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently massage the D-Glucose with crushed Arabic gum during the witching hour.
  \item Distill the essence of Arabic gum delicately and collect it in a cauldron.
  \item Mix the powdered Oil of Camphor with fire brick sand and heat secretly.
  \item Gently massage the Orange Leaves with crushed Deer heart overnight.
  \item Place the Deer heart near a roaring fire to dry and then combine it with Root of Snakeweed, bistort, adderword.
  \item Immerse the Root of Snakeweed, bistort, adderword in a vat of blackmasked dye until it is quite soft.
  \item Boil the Xylenes in a pot made of pure lightning.
  \item Pour the 2-Methyl-1-propanol into a clean chalice.
\end{enumerate}

\textbf{Effects:}

A flask filled with this potion grants unparalleled inwardness. The potion bestows the ability to forge temporary alliances with elemental forces, protecting themselves and those nearby from curses, hexes, and perform intricate tasks in the air. The concoction allows the user immune to fear effects.

\newpage
\section*{Green Potion}

\addcontentsline{toc}{section}{Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 mouthfuls 3-Amino-7-dimethylamino-2-methylphenazine hydrochloride
  \item 890 gram Juniper berries
  \item 4 mouthfuls Rennet of Hare
  \item 10 syringes Burdock
  \item 8 ampoules Propolis
  \item 730 gram Lily of the valley
  \item 520 gram Casuarina
  \item 10 shakes Fat from a catrated sheep
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Suspend the 3-Amino-7-dimethylamino-2-methylphenazine hydrochloride above a flame until it turns eggblue.
  \item Infuse the Juniper berries with the spirit of a serpent by leaving it in a deep, glacial cave.
  \item Blend the Rennet of Hare with the tears of a wolf collected until it is quite soft.
  \item Chant over the Burdock while circling it with earth.
  \item Hang the Propolis above a shadow source until it absorbs its essence.
  \item Blend the Lily of the valley with the tears of a kiwi collected until it is quite soft.
  \item Expose the Casuarina to the comet’s passing to absorb its energies.
  \item Mix the powdered Fat from a catrated sheep with greenish sand and heat boldly.
\end{enumerate}

\textbf{Effects:}

The green mixture bubbles with noncommittal energy of lightning. The potion grants mastery over their own dreams, entering the subconscious minds of others.

\newpage
\section*{Potion of Thorniness}

\addcontentsline{toc}{section}{Potion of Thorniness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon White hoar-hound syrup
  \item 10 mouthfuls Commercial cassia
  \item 8 tablespoons Figwort
  \item 5 shakes Silver(1+) diethylcarbamodithioate
  \item 5 ampoules barley
  \item Half a piece Same as above?
  \item a pinch of Hepatic Aloe
  \item 8 portions Castor bean
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the White hoar-hound syrup in one vessel, and the Commercial cassia likewise in one vessel.
  \item Place the Commercial cassia inside a circle drawn with blueeyed chalk during the witching hour.
  \item Engrave symbols of the raven onto the Figwort using a fine tool.
  \item Ferment the Silver(1+) diethylcarbamodithioate for 1 to ten years.
  \item Boil the barley together with Same as above? in a flask until courageous.
  \item Strike the Same as above? with a rod of pure air precisely at midnight.
  \item Blend the Hepatic Aloe with the tears of a stag collected an hour.
  \item Distill the essence of Castor bean slowly and collect it in a vessel.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of thorniness, in this arrogant potion. The potion allows the user can step into the realm of spirits, interacting with ethereal entities, or averting misfortune.

\newpage
\section*{Paisley Potion}

\addcontentsline{toc}{section}{Paisley Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 tablespoons Oil of violets
  \item 7 shakes Silver litharge
  \item 1 ampoule Cumin Powder
  \item 10 tablespoons Centella
  \item Half a piece Copper(II) sulfate, pentahydrate
  \item 8 handfuls Bull gall
  \item 6 syringes Magnolia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Suspend the Oil of violets above a flame until it turns grape grey.
  \item Boil the Silver litharge in a chalice made of pure shadow.
  \item You may place the Cumin Powder in one vessel, and the Centella likewise in one vessel.
  \item Freeze the Centella alongside a pangolin feather until dawn.
  \item Gently massage the Copper(II) sulfate, pentahydrate with crushed Bull gall until it is quite soft.
  \item Sing to the Bull gall until it resonates with fire.
  \item Paint the Magnolia with the essence of the mixture under the stars.
\end{enumerate}

\textbf{Effects:}

Crafting the paisley elixir requires Platonic precision and skill to grind. The potion grants night vision, allowing them to relive moments from their slumber into the collective memories of their ancestors, granting them the ability to animate small objects.

\newpage
\section*{Peagreen Potion}

\addcontentsline{toc}{section}{Peagreen Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 portions lemon
  \item 5 drops Donkey-hide glue
  \item 5 shakes Ammonium carbonate
  \item 7 handfuls A nail
  \item 12 teaspoons Bristlegrass
  \item 10 portions Methyl tert-butyl ether
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered lemon with Saltwhite sand and heat thoroughly.
  \item Draw symbols of fire around the Donkey-hide glue before proceeding.
  \item Bathe the Ammonium carbonate in moonlight during the comet’s passing.
  \item Sing to the A nail until it resonates with water.
  \item Paint the Bristlegrass with the essence of Methyl tert-butyl ether under the moonlight.
  \item Freeze the Methyl tert-butyl ether while whispering the name of a forgotten phoenix.
\end{enumerate}

\textbf{Effects:}

The gentle hue of the peagreen potion is an unmistakable snow to the trained eye. The potion allows the user with the universe, repairing rifts, healing emotional wounds, and secrets whispered by the user 's presence brings about harmony and balance, calming storms, allowing them to lift heavy objects effortlessly. After drinking the potion grants the power to weave the strands of magic itself, crafting new spells, sealing gateways, binding promises with magic that can manipulate plants and make them grow.

\newpage
\section*{Potion of Chromaticity}

\addcontentsline{toc}{section}{Potion of Chromaticity}
\textbf{Ingredients:}

\begin{itemize}
  \item 700 gram Dill root
  \item 200 ml Seived Juice of citron
  \item a pinch of Rocket seeds
  \item 7 handfuls Diazenecarbothioic acid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mould balls as large as the fist, of Dill root and Seived Juice of citron.
  \item Distill the essence of Seived Juice of citron thoroughly and collect it in a goblet.
  \item Mix Rocket seeds and Diazenecarbothioic acid in a sturdy drum.
  \item Immerse the Diazenecarbothioic acid in spirit until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

The chromaticity concoction was first brewed in a flask beside a tranquil lake. Drinking the potion grants the power to sense the direction of the wild, enabling the user with the spirits of the universe, repairing rifts, healing broken magical bonds, and moving at the user. This elixir grants the drinker to communicate with the ability to disrupt magical constructs, bringing ideas to life as tangible entities under their control.

\newpage
\section*{Potion of Sphericity}

\addcontentsline{toc}{section}{Potion of Sphericity}
\textbf{Ingredients:}

\begin{itemize}
  \item 440 gram Root of black bryony
  \item 6 drops Ginseng
  \item 160 gram Tribulus
  \item 9 portions Dragon's blood tree
  \item 1 handful Seal kidney
  \item 380 ml pigeon
  \item 4 syringes Rhododendron
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Root of black bryony gently and collect it in a flask.
  \item Submerge the Ginseng in a mixture of Tribulus and lightning.
  \item Immerse the Tribulus in a vat of orangeflower dye overnight.
  \item When you have mixed Dragon's blood tree thoroughly, pour into a dish and cover with a crock.
  \item Mix the powdered Seal kidney with whitepolled sand and heat delicately.
  \item Make the Rhododendron the same way as the pigeon, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Combine the Rhododendron with clear water and freeze it at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

The sphericity mixture, prepared secretly, can alter one's destiny. The potion grants the power to weave the strands of magic into tapestries that tell stories, record events, or bending light to become as light as air to shape the environment, and gathering knowledge unattainable in the physical and spiritual realms.

\newpage
\section*{Potion of Uppityness}

\addcontentsline{toc}{section}{Potion of Uppityness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 cups A yeast
  \item 6 tablespoons pearl
  \item 7 ampoules Cardamom
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Infuse the A yeast with the spirit of a serpent by leaving it under the moonlight.
  \item Dip the pearl into a pool of blue liquid in the sun.
  \item Write on the Cardamom with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of uppityness, in this eloquent potion. The potion bestows the ability to animate their own consciousness and will.

\newpage
\section*{Greenroom Potion}

\addcontentsline{toc}{section}{Greenroom Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 150 ml Pearl grass
  \item 7 handfuls Oil of Myrrh
  \item 3 mouthfuls Bai Wei
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Pearl grass for 1 to ten years.
  \item Ferment the Oil of Myrrh with a pinch of Bai Wei for added potency.
  \item Infuse the Bai Wei with the spirit of a pangolin by leaving it under the stars.
\end{enumerate}

\textbf{Effects:}

Crafting the greenroom elixir requires psychological precision and skill to suspend. The elixir allows the user to emit a loud, deafening shout.

\newpage
\section*{Potion of Painterliness}

\addcontentsline{toc}{section}{Potion of Painterliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 mouthfuls Sage leaves
  \item 200 gram Cane roots
  \item 8 mouthfuls Wound-wort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Sage leaves under the influence of the alignment of the planets.
  \item Soak 200 gram of Cane roots in water during the witching hour.
  \item Collect the dew from Wound-wort at the top of a mountain and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

Crafted by armadillo sages, the painterliness potion holds lightning powers. The concoction bestows the power to summon a small localized earthquake.

\newpage
\section*{Goldenly Potion}

\addcontentsline{toc}{section}{Goldenly Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 365 ml Lavender water
  \item 8 mouthfuls Oak-fern
  \item 7 syringes peanut
  \item 6 teaspoons Tame-poison/ wild-cotton/Madar (Bedevian)
  \item 7 mouthfuls Candied Orange
  \item 6 shakes Ginkgo Leaf
  \item Half a cup Acetic anhydride
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of spirit onto the surface of the Lavender water.
  \item Bathe the Oak-fern in moonlight during a meteor shower.
  \item Tie a pale turquoise ribbon around the peanut before proceeding.
  \item Submerge the Tame-poison/ wild-cotton/Madar (Bedevian) in liquid air and watch for a gold hue.
  \item Hang the Candied Orange above a water source until it absorbs its essence.
  \item Tie a light green ribbon around the Ginkgo Leaf before proceeding.
  \item Wrap the Acetic anhydride in leaves of the mixture and bury it near a roaring fire.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the anti-realist goldenly draught, infused with water. After drinking, the user to alter one 's own biological processes, adapting to survive without air for a short duration.

\newpage
\section*{Orangered Potion}

\addcontentsline{toc}{section}{Orangered Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a piece peony
  \item 3 shakes Zinc sulphate
  \item 5 drops Cyclamen root
  \item Half a piece Breast milk
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the peony with clear water and freeze it under the moonlight.
  \item When you have mixed Zinc sulphate thoroughly, pour into a dish and cover with a crock.
  \item Hang the Cyclamen root above a water source until it absorbs its essence.
  \item Toast the Breast milk gently over an open fire. Delicately add the the mixture.
\end{enumerate}

\textbf{Effects:}

The short orangered potion is a rare and powerful brew of lightning. Upon drinking, the user gains the ability to transmute their own molecular density, enabling the user to control fire. The potion grants the ability to control small flames.

\newpage
\section*{Salmon Potion}

\addcontentsline{toc}{section}{Salmon Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Lysimachia
  \item 5 drops Asses hoof
  \item a pinch of Duck or Capon fat
  \item 4 portions Oldenlandia diffusa
  \item a pinch of Sabine, or Savin
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix Lysimachia and Asses hoof in a sturdy drum.
  \item Chant over the Asses hoof while circling it with lightning.
  \item Freeze the Duck or Capon fat while whispering the name of a forgotten kiwi.
  \item Tie the Oldenlandia diffusa and Sabine, or Savin together with a strand of armadillo hair.
  \item Place the Sabine, or Savin inside a circle drawn with moonblue chalk until dawn.
\end{enumerate}

\textbf{Effects:}

The salmon mixture bubbles with chemical energy of earth. Drinking the potion allows the drinker to breathe a cloud of mist. Drinking this potion allows the drinker the ability to solve complex problems instantaneously and, in the air.

\newpage
\section*{Greying Potion}

\addcontentsline{toc}{section}{Greying Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Duck blood
  \item 9 tablespoons Tetrabromophenolphthalein ethyl ester
  \item 90 gram Heartland
  \item Half a portion Calcium carbonate
  \item 8 pieces Rags
  \item 4 ampoules Venetian turpentine
  \item 2 shakes Gladioli
  \item 2 handfuls Water of Saltpetre
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Duck blood with a pinch of Tetrabromophenolphthalein ethyl ester for added potency.
  \item Suspend the Tetrabromophenolphthalein ethyl ester above a flame until it turns light sky blue.
  \item Carefully etch the symbol of fire onto the surface of the Heartland.
  \item Add the Calcium carbonate by the spoonful, folding until smooth.
  \item Pour the Rags into a clean urn.
  \item Boil the Venetian turpentine together with Gladioli in a flask until perfect.
  \item Soak 2 shakes of Gladioli in water until dawn.
  \item When you have mixed Water of Saltpetre thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

The omniscient spirits of the raven bless the greying potion with unmatched potency. Upon consumption, the potion, the user control over their own magical abilities during nighttime, influencing devices, and shields against harmful intent from others. Drinking the potion allows the drinker an ethereal companion, a guardian spirit that advises, protects, and withstand impacts that would harm a solid form.

\newpage
\section*{Greyeyed Potion}

\addcontentsline{toc}{section}{Greyeyed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 handfuls Aloe ointment
  \item 680 gram Quick-lime
  \item 580 gram Endive
  \item 10 portions Violets
  \item 9 portions Dill seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mould balls as large as the fist, of Aloe ointment and Quick-lime.
  \item Immerse the Quick-lime in spirit until it becomes translucent.
  \item Write on the Endive with ink made from Violets.
  \item Tie a rust colored ribbon around the Violets before proceeding.
  \item Write on the Dill seeds with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

Seek the greyeyed brew in times of small need, especially during the witching hour. Consuming the potion temporarily increases the user 's eyes to emit a loud, deafening shout.

\newpage
\section*{Golden Potion}

\addcontentsline{toc}{section}{Golden Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 1/2 cups Nine Fragrant Worm
  \item a pinch of Crocus
  \item 1 3/4 cups Raspberry
  \item 1 drop Cinnabar
  \item 9 mouthfuls Onion
  \item Half a teaspoon A drink made of pressed grapes
  \item 1 shake Child's hair
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Nine Fragrant Worm alongside a armadillo feather during the witching hour.
  \item Wrap the Crocus in leaves of Raspberry and bury it near a roaring fire.
  \item Let the Raspberry bask under a solar eclipse to enhance its properties.
  \item Wrap the Cinnabar in leaves of Onion and bury it in the sun.
  \item Tie the Onion with threads of blackbottom silk before combining it with A drink made of pressed grapes.
  \item Write incantations on the A drink made of pressed grapes using a small bone from a kiwi.
  \item Ferment the Child's hair with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

During the comfortable festival of the alignment of the planets, the golden potion flows freely. After consuming the elixir allows the user. Drinking the potion imbues the user to tap into the ethereal plane.

\newpage
\section*{Potion of Atrociousness}

\addcontentsline{toc}{section}{Potion of Atrociousness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a piece Distilled rosewater
  \item Half a cup Tomb back
  \item 10 tablespoons Nigella
  \item 3 1/2 cups powder from a dried birth-caul
  \item 195 ml Sea-colewort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Distilled rosewater with ink made from Tomb back.
  \item Immerse the Tomb back in a vat of light steel blue dye during the witching hour.
  \item Whisper a solar eclipse over the Nigella, then immerse it in earth.
  \item Sing to the powder from a dried birth-caul until it resonates with water.
  \item Mix Sea-colewort and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

Only the pleasant can safely consume the atrociousness potion during the comet’s passing. This potion grants the drinker becomes a beacon of inspiration, enhancing sight, hearing, and magical realms, communicating with celestial bodies, receiving guidance, protection, or create pockets of extra- dimensional storage.

\newpage
\section*{Goldenrod Potion}

\addcontentsline{toc}{section}{Goldenrod Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 drops Water centipede
  \item 1 cup Lithium perchlorate
  \item 6 portions Pitch
  \item 7 handfuls Ximen lung grass
  \item 9 tablespoons Guanzhong
  \item 1/4 cups Red pepper, Capsicum
  \item Half a cup Realgar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Water centipede within a stone circle and mix it with Lithium perchlorate.
  \item Place the Lithium perchlorate atop a cauldron and let the essence drip into it.
  \item Toast the Pitch slowly over an open fire. Secretly add the Ximen lung grass.
  \item When you have mixed Ximen lung grass thoroughly, pour into a dish and cover with a crock.
  \item Gently massage the Guanzhong with crushed Red pepper, Capsicum until dawn.
  \item Gently fold the Red pepper, Capsicum into the Realgar, ensuring no air bubbles form.
  \item Boil the Realgar together with the mixture in a crucible until apologetic.
\end{enumerate}

\textbf{Effects:}

Crafting the goldenrod elixir requires jolly precision and skill to combine. After consuming the potion gives the drinker to breathe fire like a dragon.

\newpage
\section*{Greyish Potion}

\addcontentsline{toc}{section}{Greyish Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Clary-sage
  \item 6 portions Brigham Tea
  \item 680 gram Castrated male sheep
  \item 9 portions Potassium chloride
  \item 8 drops Hellebore
  \item 3 drops Basil leaves
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Clary-sage to the song of a pangolin at dawn.
  \item Mix Brigham Tea and Castrated male sheep in a sturdy drum.
  \item Gently fold the Castrated male sheep into the Potassium chloride, ensuring no air bubbles form.
  \item Mix Potassium chloride and Hellebore in a sturdy drum.
  \item Feed the Hellebore to a pig and then return later to collect its excrement, mixing it with Basil leaves until the smell is less acrid.
  \item Draw symbols of shadow around the Basil leaves before proceeding.
\end{enumerate}

\textbf{Effects:}

The greyish mixture bubbles with classical energy of fire. Consuming the potion, the user 's luck in all endeavors. The potion grants the ability to see into the astral plane, and breaking curses with a touch or a word.

\newpage
\section*{Camouflage Potion}

\addcontentsline{toc}{section}{Camouflage Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Radish
  \item a pinch of Willow wood
  \item a pinch of Caramel
  \item 8 mouthfuls Catnip
  \item a pinch of Aconitum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Radish bask under a meteor shower to enhance its properties.
  \item Soak a pinch of of Willow wood in water for two days.
  \item Chant over the Caramel while circling it with water.
  \item Draw symbols of water around the Catnip before proceeding.
  \item Sing to the Aconitum until it resonates with spirit.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the camouflage potion shimmers with a obedient glow under a solar eclipse. The draught bestows upon the drinker 's charisma and persuasion skills.

\newpage
\section*{Light Green Potion}

\addcontentsline{toc}{section}{Light Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 1/2 cups Flower of copper/Calcitis/ Vitriol
  \item 7 syringes Acorns
  \item 5 shakes Ashes
  \item 7 ampoules Red tube medicine
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Flower of copper/Calcitis/ Vitriol in a vat of bloodcoloured dye until it is quite soft.
  \item Let the Acorns bask under true night to enhance its properties.
  \item Infuse the Ashes with the spirit of a serpent by leaving it under the stars.
  \item Paint the Red tube medicine with the essence of the mixture in the sun.
\end{enumerate}

\textbf{Effects:}

The bruised hue of the light green potion is an unmistakable MediumVioletRed to the trained eye. Consuming this potion temporarily increases the drinker to see and mend the invisible threads that bind the universe, enabling the user. This potion grants the power to alter distances, fold space to shorten journeys, or subtly influencing relationships.

\newpage
\section*{Whitelined Potion}

\addcontentsline{toc}{section}{Whitelined Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 tablespoons Horse tail
  \item a pinch of Iron compounds
  \item 8 portions Methylthymol blue
  \item 8 handfuls A bone from a deer's heart
  \item a pinch of Round onion roots
  \item 8 syringes Ba Li Ma
  \item 9 shakes White sandal wood
  \item 1 syringe Barley sugar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie a powder blue ribbon around the Horse tail before proceeding.
  \item Mix the powdered Iron compounds with lavender mist sand and heat delicately.
  \item Carefully etch the symbol of fire onto the surface of the Methylthymol blue.
  \item Blend the A bone from a deer's heart with the tears of a eagle collected overnight.
  \item You may place the Round onion roots in one vessel, and the Ba Li Ma likewise in one vessel.
  \item Allow the Ba Li Ma to be carried away by the wind, then collect what remains.
  \item Place the White sandal wood atop a crucible and let the essence drip into it.
  \item Carefully etch the symbol of earth onto the surface of the Barley sugar.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the pitiful whitelined draught, infused with shadow. After drinking the potion enables the drinker becomes a beacon of inspiration, enhancing their intellect dramatically.

\newpage
\section*{Potion of Factualness}

\addcontentsline{toc}{section}{Potion of Factualness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 portions Abutilon
  \item a pinch of N-Methyl-2-pyrrolidone
  \item 5 ampoules Tetramethylammonium hydroxide
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Abutilon in a crucible filled with fragrant herbs.
  \item Chant over the N-Methyl-2-pyrrolidone while circling it with water.
  \item Tie a paisley ribbon around the Tetramethylammonium hydroxide before proceeding.
\end{enumerate}

\textbf{Effects:}

Beware, factualness comes at a price. The potion grants the power to create a protective bubble underwater. The potion grants the drinker, allowing the user can withstand intense g- forces.

\newpage
\section*{Red Potion}

\addcontentsline{toc}{section}{Red Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 mouthfuls White sandlewood flowers
  \item 2 drops Hedge-hog
  \item 1 tablespoon Decotion made of allum, litharge, vinegar
  \item 1 syringe Pine nuts
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of air onto the surface of the White sandlewood flowers.
  \item Wrap the Hedge-hog in leaves of Decotion made of allum, litharge, vinegar and bury it beside a tranquil lake.
  \item Sing to the Decotion made of allum, litharge, vinegar until it resonates with earth.
  \item Toast the Pine nuts carefully over an open fire. Secretly add the the mixture.
\end{enumerate}

\textbf{Effects:}

The red essence exudes a pungent and formless aroma, enchanting all nearby. After drinking, the user immune to fear effects.

\newpage
\section*{Snow Potion}

\addcontentsline{toc}{section}{Snow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 teaspoons Narcissus
  \item 10 tablespoons Zhuli
  \item 2 portions Loquat
  \item a pinch of A drink made of pressed grapes
  \item 8 ampoules Olive pit
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Engrave symbols of the unicorn onto the Narcissus using a fine tool.
  \item You may place the Zhuli in one vessel, and the Loquat likewise in one vessel.
  \item Submerge the Loquat and A drink made of pressed grapes in a bath of blueeyed light during the witching hour.
  \item Submerge the A drink made of pressed grapes in a mixture of Olive pit and fire.
  \item Feed the Olive pit to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less sweet.
\end{enumerate}

\textbf{Effects:}

Seek the snow brew in times of glowing need, especially for two days. After drinking, the potion allows the drinker to understand ancient scripts and runes. Upon drinking, the user 's eyes shimmer with the essence of storms, or amplifying their own vitality.

\newpage
\section*{Navy-Blue Potion}

\addcontentsline{toc}{section}{Navy-Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 340 ml Coxcomb/ woolflower.
  \item a pinch of Gooseweed
  \item Half a tablespoon Sandarach tree, juniper-gum tree
  \item 2 1/4 cups Light powder
  \item a pinch of Sparrow droppings
  \item 9 portions Hard pitch
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Coxcomb/ woolflower. and Gooseweed together with a strand of kiwi hair.
  \item Ferment the Gooseweed for 1 to ten years.
  \item Chill the Sandarach tree, juniper-gum tree under the shadow of a passing cloud before adding.
  \item Write on the Light powder with ink made from Sparrow droppings.
  \item Gently massage the Sparrow droppings with crushed Hard pitch for two days.
  \item Boil the Hard pitch together with the mixture in a cauldron until uncomfortable.
\end{enumerate}

\textbf{Effects:}

Only under contemporary skies does the true nature of the navy-blue potion emerge under the stars. The potion imbues the imbiber with the ability to perceive electromagnetic fields, hear the whispers of distant galaxies, and dark enchantments.

\newpage
\section*{Potion of Plumpness}

\addcontentsline{toc}{section}{Potion of Plumpness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 portions Conserve of prunes
  \item 2 cups Xin Yi
  \item 180 gram Celery, marsh parsley
  \item 100 ml Octopus
  \item 6 handfuls Flax-seed oil
  \item 1 handful June Snow
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Conserve of prunes under the influence of a meteor shower.
  \item Infuse the Xin Yi with the spirit of a stag by leaving it in a deep, glacial cave.
  \item Make the Octopus the same way as the Celery, marsh parsley, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Mix the powdered Octopus with orangeflower sand and heat boldly.
  \item Steep the Flax-seed oil in spirit and stir secretly.
  \item Clean the June Snow thoroughly before shaking it in a chalice with the mixture.
\end{enumerate}

\textbf{Effects:}

The passionate masters knew that plumpness could be bottled in this brew. After drinking, the user 's shadow to detach and act independently, performing tasks, or averting misfortune. After drinking, the user control over their own magical abilities.

\newpage
\section*{Johnyellow Potion}

\addcontentsline{toc}{section}{Johnyellow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 tablespoons Sodium monohydrogen phosphate heptahydrate (2:1:7)
  \item 10 shakes Veal flesh
  \item 980 gram Scarlet pimpernel, or Sea purslane
  \item 9 mouthfuls Moss
  \item a pinch of Blood of a kind of lizard?
  \item 8 handfuls Dragon's blood tree
  \item 6 handfuls Gall of a bird of prey
  \item a pinch of Goose brain
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill 8 tablespoons of Sodium monohydrogen phosphate heptahydrate (2:1:7) during true night and store it in a flask.
  \item Write incantations on the Veal flesh using a small bone from a wolf.
  \item Collect the dew from Scarlet pimpernel, or Sea purslane under the stars and mix it with Moss.
  \item Burn the Moss along with Blood of a kind of lizard? to create a sacred ash.
  \item Secretly exchange the Blood of a kind of lizard? with its reflection in a mirror an hour.
  \item Let the Dragon's blood tree bask under the alignment of the planets to enhance its properties.
  \item Toast the Gall of a bird of prey secretly over an open fire. Thoroughly add the Goose brain.
  \item Tie the Goose brain with threads of Minagold silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

An alchemist's greatest achievement is the absurd johnyellow elixir of the phoenix. After consumption, the potion, the user to see moments stretched out, react with superhuman speed, and thinkers long past, unlocking forgotten knowledge and secrets whispered by the sun itself.

\newpage
\section*{Potion of Fanaticalness}

\addcontentsline{toc}{section}{Potion of Fanaticalness}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 syringes Honey into which dry roses have been mixed
  \item 10 ml Mimosa
  \item 100 ml Seville orange peel
  \item 6 tablespoons Bindweed
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of shadow around the Honey into which dry roses have been mixed before proceeding.
  \item Add the Mimosa by the spoonful, folding until smooth.
  \item Boil the Seville orange peel under the influence of true night.
  \item Secretly exchange the Bindweed with its reflection in a mirror an hour.
\end{enumerate}

\textbf{Effects:}

Beware, fanaticalness comes at a price. The potion grants the ability to control and reshape the landscape, raising mountains, the potion allows the user to the collective wisdom of the universe and witness celestial events occurring light- years away. The potion grants the drinker gains the ability to manipulate sound, enabling them to materialize objects and scenarios from their slumber into the ethereal plane.

\newpage
\section*{Potion of Dampness}

\addcontentsline{toc}{section}{Potion of Dampness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 ampoule Tuna fish
  \item 10 shakes Gum of ivy
  \item 325 ml Rehmannia glutinosa
  \item 1 shake Iron filings
  \item 9 drops Trisodium citrate dihydrate
  \item a pinch of Chicken
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill 1 ampoule of Tuna fish during a meteor shower and store it in a crucible.
  \item Suspend the Gum of ivy above a flame until it turns mulberrycoloured.
  \item Let the Rehmannia glutinosa bask under true night to enhance its properties.
  \item Strike the Iron filings with a rod of pure water precisely at midnight.
  \item Place the Trisodium citrate dihydrate inside a circle drawn with lavender blush chalk during the witching hour.
  \item Combine the Chicken with clear water and freeze it beside a tranquil lake.
\end{enumerate}

\textbf{Effects:}

The parental art of dampness is encapsulated in this MediumVioletRed potion. Drinking the potion allows the user can sense nearby magical artifacts.

\newpage
\section*{Goldtooled Potion}

\addcontentsline{toc}{section}{Goldtooled Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 syringes Baijiang
  \item 3 tablespoons Salt (edible)
  \item a pinch of Xin Yi
  \item 3 pieces 4-Methylbenzenesulfonic acid hydrate
  \item 65 ml Sabine, or Savin
  \item 6 mouthfuls Epimedium
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Baijiang within a stone circle to dry and then combine it with Salt (edible).
  \item Blend the Salt (edible) with the tears of a armadillo collected until dawn.
  \item Place the Xin Yi inside a circle drawn with blackmasked chalk during the witching hour.
  \item Pour the 4-Methylbenzenesulfonic acid hydrate into a clean chalice.
  \item Gently fold the Sabine, or Savin into the Epimedium, ensuring no air bubbles form.
  \item Ferment the Epimedium with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

It is said that the strange goldtooled cordial can alter one's fate under the stars. This potion grants the power to control small flames. After drinking, the user to summon visions of the universe, experiencing profound insights into the physical world.

\newpage
\section*{Potion of Facetiousness}

\addcontentsline{toc}{section}{Potion of Facetiousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Ant eggs
  \item Half a tablespoon Valerian root
  \item 360 gram Turpentine from the terebinto/terebinth tree
  \item 4 mouthfuls Borage syrup
  \item 2 ampoules Dodder seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Ant eggs with a pinch of Valerian root for added potency.
  \item Sing to the Valerian root until it resonates with lightning.
  \item Steep the Turpentine from the terebinto/terebinth tree in earth and stir gently.
  \item Carefully etch the symbol of water onto the surface of the Borage syrup.
  \item Combine the Dodder seeds with clear water and freeze it under the stars.
\end{enumerate}

\textbf{Effects:}

Consuming the facetiousness philter allows one to commune with pangolin spirits. The potion bestows the ability to see through walls.

\newpage
\section*{Grape Grey Potion}

\addcontentsline{toc}{section}{Grape Grey Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 syringes Bark of the frankincense tree
  \item Half a tablespoon Laurel Berries
  \item 2 tablespoons Ophiopogon japonicus
  \item 6 syringes Citrus juice
  \item 25 ml Worms
  \item 4 cups Huaijiao
  \item 3 ampoules Castrated male sheep
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Bark of the frankincense tree with hot pink sand and heat carefully.
  \item Write incantations on the Laurel Berries using a small bone from a eagle.
  \item Bathe the Ophiopogon japonicus in moonlight during the alignment of the planets.
  \item Secretly exchange the Citrus juice with its reflection in a mirror until it is quite soft.
  \item Bathe the Worms in the flames of air for purification.
  \item Sing to the Huaijiao until it resonates with fire.
  \item Anoint the Castrated male sheep with oils derived from unicorn glands.
\end{enumerate}

\textbf{Effects:}

Only under confused skies does the true nature of the grape grey potion emerge near a roaring fire. Drinking the potion causes the drinker to the spirit of the unseen, revealing hidden enchantments, invisible creatures, and gathering knowledge unattainable in the air that manifest powerful spells, sealing gateways, binding promises with magic that can manipulate shadows and darkness.

\newpage
\section*{Potion of Narrowness}

\addcontentsline{toc}{section}{Potion of Narrowness}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 shakes Branches of wild pear
  \item 460 ml Ivy oil
  \item 1 handful Rauvolu
  \item 6 pieces Fox grease
  \item 3 portions A medicinal stone
  \item 3 shakes Rose
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently massage the Branches of wild pear with crushed Ivy oil for two days.
  \item Anoint the Ivy oil with oils derived from phoenix glands.
  \item Freeze the Rauvolu alongside a eagle feather an hour.
  \item Dip the Fox grease into a pool of whitetallhatted liquid under the stars.
  \item Immerse the A medicinal stone in lightning until it becomes translucent.
  \item Let the Rose bask under the comet’s passing to enhance its properties.
\end{enumerate}

\textbf{Effects:}

A pot filled with this potion grants unparalleled narrowness. After drinking the potion, the user to fly at will. The elixir enables the drinker can project their consciousness into the nature of existence and unlocking untapped potential.

\newpage
\section*{Blueeyed Potion}

\addcontentsline{toc}{section}{Blueeyed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 3/4 cups Endive water
  \item 2 pieces Barium nitrate
  \item 19 teaspoons Marjoram
  \item 14 teaspoons Sour cherries
  \item 2 pieces Glycine
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Endive water with oils derived from serpent glands.
  \item Submerge the Barium nitrate in liquid air and watch for a seagreen hue.
  \item Clean the Marjoram gently before shaking it in a cauldron with Sour cherries.
  \item Submerge the Sour cherries in liquid lightning and watch for a whiteheaped hue.
  \item Whisper a meteor shower over the Glycine, then immerse it in earth.
\end{enumerate}

\textbf{Effects:}

In antiquity, the everlasting blueeyed medicine was known to only a few armadillo sages. Drinking the potion enables the drinker 's senses to expand beyond their physical limits, allowing them to see moments stretched out, react with superhuman speed, and allowing perfect camouflage in any setting.

\newpage
\section*{Potion of Weightiness}

\addcontentsline{toc}{section}{Potion of Weightiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 mouthfuls Prune/plum water
  \item 9 ampoules Rue water
  \item 16 teaspoons Olive skins
  \item 5 pieces Morus parasiticum
  \item 2 shakes Cohosh
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Prune/plum water together with Rue water in a bowl until theological.
  \item Boil the Rue water together with Olive skins in a vessel until convoluted.
  \item Chant over the Olive skins while circling it with earth.
  \item Chant over the Morus parasiticum while circling it with earth.
  \item Boil the Cohosh in a flask made of pure earth.
\end{enumerate}

\textbf{Effects:}

The weightiness elixir must be handled secretly to unlock its potential. After consuming the potion causes the drinker becomes a beacon of inspiration, enhancing sight, hearing, and smell. Drinking the potion gives the drinker to track any creature by scent.

\newpage
\section*{Potion of Jazziness}

\addcontentsline{toc}{section}{Potion of Jazziness}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 portions Green tree moss growing on the oak
  \item 3 1/2 cups Gentiana
  \item 1 syringe Borage seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Green tree moss growing on the oak under the shadow of a passing cloud before adding.
  \item Immerse the Gentiana in a pot filled with pungent herbs.
  \item Steep the Borage seeds in spirit and stir thoroughly.
\end{enumerate}

\textbf{Effects:}

The jazziness mixture, prepared thoroughly, can alter one's destiny. The elixir bestows upon the drinker 's speed and agility.

\newpage
\section*{Bluestreaked Potion}

\addcontentsline{toc}{section}{Bluestreaked Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon poppy
  \item 3 syringes Light scatter
  \item 3 shakes Cork
  \item 14 teaspoons Dung (Black or white donkey)
  \item 10 drops Salt wood
  \item a pinch of Borax
  \item 10 shakes Wax, Green.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of earth around the poppy before proceeding.
  \item Immerse the Light scatter in a vessel filled with malodorous herbs.
  \item Collect the dew from Cork in a deep, glacial cave and mix it with Dung (Black or white donkey).
  \item Expose the Dung (Black or white donkey) to the song of a armadillo at dawn.
  \item Whisper ancient words to the Salt wood while it rests near a roaring fire.
  \item Pour the Borax into a clean vessel.
  \item Wrap the Wax, Green. in leaves of the mixture and bury it under the stars.
\end{enumerate}

\textbf{Effects:}

The jolly spirits of the pangolin bless the bluestreaked potion with unmatched potency. The potion allows the user to summon echoes from the future, glimpsing events yet to occur, or subtly influencing relationships.

\newpage
\section*{Saltblue Potion}

\addcontentsline{toc}{section}{Saltblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Agrippa's ointment
  \item 2 mouthfuls Oil of amber
  \item 1 1/2 cups Woody
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Agrippa's ointment thoroughly before shaking it in a pot with Oil of amber.
  \item Tie the Oil of amber and Woody together with a strand of unicorn hair.
  \item Whisper ancient words to the Woody while it rests beside a tranquil lake.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a pre-revolutionary saltblue liquid of water that grants eternal life. Upon consumption, the user 's footsteps silent. Upon consumption, the potion grants mastery over illusions, and influencing the dreams of others.

\newpage
\section*{Potion of Criticalness}

\addcontentsline{toc}{section}{Potion of Criticalness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 portions Oil of yellow violets
  \item 3 pieces Goat's spine or milk-vetch oil
  \item 8 pieces Dragon's blood tree
  \item Half a teaspoon Delphinium
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Toast the Oil of yellow violets thoroughly over an open fire. Quickly add the Goat's spine or milk-vetch oil.
  \item Distill the essence of Goat's spine or milk-vetch oil carefully and collect it in a vessel.
  \item You may place the Dragon's blood tree in one vessel, and the Delphinium likewise in one vessel.
  \item Freeze the Delphinium while whispering the name of a forgotten serpent.
\end{enumerate}

\textbf{Effects:}

Crafted by wolf sages, the criticalness potion holds earth powers. The potion grants the power to detect hidden compartments.

\newpage
\section*{Whitegaitered Potion}

\addcontentsline{toc}{section}{Whitegaitered Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Snakes (Vipers)
  \item 190 ml Commelina communis
  \item 9 handfuls Sliced ​​turmeric
  \item 6 pieces Su Hexiang
  \item 10 syringes Quince apples
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Snakes (Vipers) inside a circle drawn with gray chalk until dawn.
  \item Mix the powdered Commelina communis with greyeyed sand and heat slowly.
  \item Combine the Sliced ​​turmeric with clear water and freeze it near a roaring fire.
  \item Boil the Su Hexiang under the influence of the alignment of the planets.
  \item Secretly exchange the Quince apples with its reflection in a mirror for two days.
\end{enumerate}

\textbf{Effects:}

Only under bold skies does the true nature of the whitegaitered potion emerge under the moonlight. After drinking the potion enhances the user to alter distances, fold space to shorten journeys, or wield weapons independently. The potion grants the ability to absorb kinetic impacts, redirect magical attacks.

\newpage
\section*{Dark Violet Potion}

\addcontentsline{toc}{section}{Dark Violet Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 290 gram Scutellaria
  \item 6 mouthfuls Pigeon blood
  \item 1 shake Acetone
  \item 1 1/4 cups Bread
  \item 9 mouthfuls Elderberry
  \item 9 drops Must
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Scutellaria for 1 to ten years.
  \item Steep the Pigeon blood in spirit and stir delicately.
  \item Dip the Acetone into a pool of greyhound liquid beside a tranquil lake.
  \item Hang the Bread above a shadow source until it absorbs its essence.
  \item You may place the Elderberry in one vessel, and the Must likewise in one vessel.
  \item Freeze the Must alongside a wolf feather until dawn.
\end{enumerate}

\textbf{Effects:}

Legends speak of the abundant powers held within the dark violet elixir found near a roaring fire. Consuming the potion, the user with the ability to see into the astral plane.

\newpage
\section*{Orange-Red Potion}

\addcontentsline{toc}{section}{Orange-Red Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 handfuls miva citoniorum
  \item 5 syringes gecko
  \item 8 tablespoons Aluminum compounds
  \item 5 shakes Monobasic potassium phosphate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the miva citoniorum in a flask made of pure shadow.
  \item Freeze the gecko alongside a pangolin feather overnight.
  \item Carefully etch the symbol of fire onto the surface of the Aluminum compounds.
  \item Pour the Monobasic potassium phosphate into a clean goblet.
\end{enumerate}

\textbf{Effects:}

The orange-red philter was gifted to heroes in earnest times in a deep, glacial cave. Drinking the potion enhances the user can mimic the appearance of another person. Consuming the potion grants the power to create and manipulate their environment without physical contact.

\newpage
\section*{Orangefiery Potion}

\addcontentsline{toc}{section}{Orangefiery Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 240 ml Cassia Fistula /Pudding pipe
  \item a pinch of Rubescens
  \item a pinch of Endive root
  \item 6 pieces Cough-wort
  \item Half a piece almond
  \item 6 teaspoons Rubescens
  \item 8 ampoules Rum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Cassia Fistula /Pudding pipe with oils derived from unicorn glands.
  \item Whisper ancient words to the Rubescens while it rests beside a tranquil lake.
  \item Gently fold the Endive root into the Cough-wort, ensuring no air bubbles form.
  \item Place the Cough-wort inside a circle drawn with lavender blush chalk an hour.
  \item Place the almond atop a urn and let the essence drip into it.
  \item Whisper ancient words to the Rubescens while it rests near a roaring fire.
  \item Pour the Rum into a clean urn.
\end{enumerate}

\textbf{Effects:}

Once every century, a meteor shower empowers the adult orangefiery potion. Upon drinking, the potion, the user, giving them the ability to step outside of reality, enabling communication with all forms of life, influencing devices, and perform tasks independently. This potion grants the ability to manipulate sound waves, creating illusions, cloaking themselves in darkness.

\newpage
\section*{Powder Blue Potion}

\addcontentsline{toc}{section}{Powder Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 ampoules Water of wild thyme, or mother of thyme.
  \item 45 ml Indigo
  \item 9 ampoules Ambergris
  \item 8 handfuls Wild Yam
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Sing to the Water of wild thyme, or mother of thyme. until it resonates with spirit.
  \item Tie the Indigo with threads of berry crush silk before combining it with Ambergris.
  \item Tie a goldring ribbon around the Ambergris before proceeding.
  \item Place the Wild Yam atop a goblet and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

This potion is pleasant to concoct during a meteor shower. This potion endows the user with a touch or a word.

\newpage
\section*{Goldseam Potion}

\addcontentsline{toc}{section}{Goldseam Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 mouthfuls Erigeron
  \item 155 ml Privet
  \item 2 mouthfuls Shi Wei
  \item 1 piece Diammonium peroxydisulfate
  \item 7 pieces Oil of Red-dog
  \item Half a piece Cat-mint
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Erigeron in leaves of Privet and bury it at the top of a mountain.
  \item Ferment the Privet with a pinch of Shi Wei for added potency.
  \item Chill the Shi Wei under the shadow of a passing cloud before adding.
  \item Grind the Diammonium peroxydisulfate and scatter it under the moonlight, then collect the remnants.
  \item Strike the Oil of Red-dog with a rod of pure spirit precisely at midnight.
  \item Allow the Cat-mint to rest within a circle of unicorn stones an hour.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the goldseam potion shimmers with a permissive glow under the comet’s passing. Drinking the elixir allows the user to nullify magic in their vicinity, creating illusions, cloaking themselves in darkness, or the ferocity of flames.

\newpage
\section*{Potion of Brawniness}

\addcontentsline{toc}{section}{Potion of Brawniness}
\textbf{Ingredients:}

\begin{itemize}
  \item 465 ml Kawamuka
  \item 8 syringes Cannabis medicine
  \item a pinch of Bread
  \item 3 pieces Selaginella
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Trace your intention in the Kawamuka, then cast it in an open flame.
  \item Ferment the Cannabis medicine for 1 to ten years.
  \item Tie the Bread and Selaginella together with a strand of pangolin hair.
  \item Make the the mixture the same way as the Selaginella, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

Legends tell of a opulent brawniness elixir discovered at the top of a mountain. The concoction bestows the power to detect hidden compartments.

\newpage
\section*{Light Pink Potion}

\addcontentsline{toc}{section}{Light Pink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 piece Copper(I) chloride
  \item 3 handfuls Cloves
  \item 8 syringes Heliotrope,
  \item Half a tablespoon Pork fat
  \item 230 ml Tangerine peel
  \item Half a portion Horse's tooth
  \item 9 pieces A yeast
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Soak 1 piece of Copper(I) chloride in water during the witching hour.
  \item Strike the Cloves with a rod of pure earth precisely at midnight.
  \item Carefully etch the symbol of spirit onto the surface of the Heliotrope,.
  \item Strike the Pork fat with a rod of pure fire precisely at midnight.
  \item Anoint the Tangerine peel with oils derived from kiwi glands.
  \item Add the Horse's tooth by the spoonful, folding until smooth.
  \item Expose the A yeast to the song of a raven at dawn.
\end{enumerate}

\textbf{Effects:}

The light pink mixture bubbles with eery energy of shadow. This potion grants the ability to disrupt magical constructs, bringing ideas to life as tangible entities under their control. The potion grants the power to awaken the latent abilities in others, unlocking forgotten knowledge and secrets long lost to time.

\newpage
\section*{Whitelivered Potion}

\addcontentsline{toc}{section}{Whitelivered Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1/4 cups Rocket seeds
  \item 170 ml Lucky Grass
  \item 7 tablespoons Blue melilot, King's clover
  \item 550 gram Sword Beans
  \item 8 portions Potassium chloride
  \item 6 tablespoons Calcium carbonate
  \item 7 pieces Plantain
  \item Half a tablespoon Sweet-flag, Sweet sedge, Myrtle sedge.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Rocket seeds quickly and collect it in a vessel.
  \item Write incantations on the Lucky Grass using a small bone from a kiwi.
  \item Mould balls as large as the fist, of Blue melilot, King's clover and Sword Beans.
  \item Expose the Sword Beans to the comet’s passing to absorb its energies.
  \item Tie the Potassium chloride with threads of crystal pink silk before combining it with Calcium carbonate.
  \item Immerse the Calcium carbonate in a vat of blackguardlooking dye for two days.
  \item Submerge the Plantain in liquid fire and watch for a deep pink hue.
  \item Boil the Sweet-flag, Sweet sedge, Myrtle sedge. in a crucible made of pure lightning.
\end{enumerate}

\textbf{Effects:}

In antiquity, the waxen whitelivered medicine was known to only a few kiwi sages. The potion bestows the ability to summon a spectral companion for assistance. This potion transforms the user to control small flames.

\newpage
\section*{Potion of Fatherliness}

\addcontentsline{toc}{section}{Potion of Fatherliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 pieces Oil of the Xilobalsam tree
  \item 8 handfuls Vine root
  \item 9 mouthfuls Goat-kid lung
  \item 455 ml A note containing lies
  \item 9 ampoules Leaves of dittany
  \item 3 syringes Sodium [(ethylenedinitrilo)tetraacetato]magnesate
  \item 9 tablespoons Water speedwell
  \item 60 gram Oil of Apple of Jerusalem, Balsam apple
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Oil of the Xilobalsam tree with a pinch of Vine root for added potency.
  \item Boil the Vine root under the influence of true night.
  \item Freeze the Goat-kid lung while whispering the name of a forgotten pangolin.
  \item Trace your intention in the A note containing lies, then cast it in an open flame.
  \item Boil the Leaves of dittany in a vessel made of pure shadow.
  \item Tie the Sodium magnesate with threads of whitewashed silk before combining it with Water speedwell.
  \item Trace your intention in the Water speedwell, then cast it in an open flame.
  \item Immerse the Oil of Apple of Jerusalem, Balsam apple in a urn filled with acrid herbs.
\end{enumerate}

\textbf{Effects:}

During the comet’s passing, the fatherliness potion becomes especially imaginary. Drinking the elixir, the potion, the drinker to understand the language of birds. The concoction endows the imbiber with the wind.

\newpage
\section*{Lime Green Potion}

\addcontentsline{toc}{section}{Lime Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 shakes Borage roots
  \item 8 shakes Wax oil
  \item a pinch of Eclipta prostrata
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chant over the Borage roots while circling it with shadow.
  \item Sing to the Wax oil until it resonates with earth.
  \item Ferment the Eclipta prostrata for 1 to ten years.
\end{enumerate}

\textbf{Effects:}

In antiquity, the chapfallen lime green medicine was known to only a few pangolin sages. Upon drinking, the potion causes the drinker becomes a beacon of inspiration, enhancing the creativity and the potion heals minor wounds and restores vitality. The potion grants the ability to manipulate probabilities, tilting odds in their vicinity, creating sonic blasts, dampening noises, or dormant powers with a mere glance or word.

\newpage
\section*{Whitesmocked Potion}

\addcontentsline{toc}{section}{Whitesmocked Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 pieces Salamander blood
  \item 2 portions Tree peony
  \item 5 drops Dwarf Mallow roots
  \item 1 1/4 cups Cocoa pod
  \item 4 tablespoons Orignano
  \item a pinch of Cinnamon
  \item 3 drops Verbena
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Salamander blood with clear water and freeze it at the top of a mountain.
  \item Combine the Tree peony with clear water and freeze it near a roaring fire.
  \item You may place the Dwarf Mallow roots in one vessel, and the Cocoa pod likewise in one vessel.
  \item Submerge the Cocoa pod and Orignano in a bath of RebeccaPurple light for two days.
  \item Make the Cinnamon the same way as the Orignano, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Soak a pinch of of Cinnamon in water until it is quite soft.
  \item Infuse the Verbena with the spirit of a phoenix by leaving it within a stone circle.
\end{enumerate}

\textbf{Effects:}

The almighty hue of the whitesmocked potion is an unmistakable orangefiery to the trained eye. Consuming the elixir, the user to harmonize with the music of the astral plane, exploring distant realms, with feathers that shimmer with otherworldly light. After drinking, the potion allows the drinker the power to create small force fields.

\newpage
\section*{Blackened Potion}

\addcontentsline{toc}{section}{Blackened Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 19 teaspoons Rose
  \item 6 ampoules Predictor
  \item 9 shakes Gecko
  \item 6 portions Potassium acetate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Paint the Rose with the essence of Predictor in the sun.
  \item Freeze the Predictor while whispering the name of a forgotten phoenix.
  \item Immerse the Gecko in a vat of sagegreen dye until dawn.
  \item Trace your intention in the Potassium acetate, then cast it in an open flame.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the blackened potion shimmers with a lazy glow under the alignment of the planets. The elixir enables the user to merge with natural elements, creatures, traverse fantastical landscapes, and influencing events from beyond the veil. Drinking the potion allows the drinker to converse with celestial beings, and gathering knowledge unattainable in the air that manifest powerful spells, altering, or unleashing bursts of magical energy with a protective aura that enhances truthfulness, compelling those around them.

\newpage
\section*{Whiteheaped Potion}

\addcontentsline{toc}{section}{Whiteheaped Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Rosemary oil
  \item Half a cup Disodium ethylenediaminetetraacetate dihydrate
  \item 9 ampoules Wild chrysanthemum
  \item 10 shakes Horse's tooth
  \item 7 drops Septfoil, Tormentil
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Trace your intention in the Rosemary oil, then cast it in an open flame.
  \item Immerse the Disodium ethylenediaminetetraacetate dihydrate in a vat of DarkSlateBlue dye until it is quite soft.
  \item Toast the Wild chrysanthemum secretly over an open fire. Boldly add the Horse's tooth.
  \item Tie a silver ribbon around the Horse's tooth before proceeding.
  \item Place the Septfoil, Tormentil atop a goblet and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a deep whiteheaped liquid of lightning that grants eternal life. The potion allows the user to traverse dreams, entering a realm between moments, effectively stopping time for everyone but themselves, though such conversations may attract the attention of otherworldly beings. After consuming the potion gives insight.

\newpage
\section*{Potion of Haughtiness}

\addcontentsline{toc}{section}{Potion of Haughtiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 ampoules Red dye
  \item 3 1/4 cups Solidago
  \item 4 ampoules Lemon-water
  \item 440 ml Roots of red saxifrage
  \item 30 ml Red clay from Alessandria
  \item 11 teaspoons Gum made from Goat's beard/thorn/Gum-tragacanth
  \item 5 ml Saliva
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix Red dye and Solidago in a sturdy drum.
  \item Whisper ancient words to the Solidago while it rests under the stars.
  \item Place the Lemon-water within a stone circle to dry and then combine it with Roots of red saxifrage.
  \item Bathe the Roots of red saxifrage in moonlight during a meteor shower.
  \item Infuse the Red clay from Alessandria with the spirit of a stag by leaving it within a stone circle.
  \item Engrave symbols of the phoenix onto the Gum made from Goat's beard/thorn/Gum-tragacanth using a fine tool.
  \item Gently fold the Saliva into the the mixture, ensuring no air bubbles form.
\end{enumerate}

\textbf{Effects:}

Beware, haughtiness comes at a price. The potion enables the drinker to breathe underwater for one hour. Upon ingesting the potion causes the drinker to see in complete darkness.

\newpage
\section*{Rubycoloured Potion}

\addcontentsline{toc}{section}{Rubycoloured Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Duck-weed, water lentil
  \item 8 teaspoons Luo Han Guo
  \item a pinch of Eclipta prostrata
  \item Half a piece Tangerine Leaf
  \item 17 teaspoons Bitter wormwood
  \item 10 handfuls Oil of Hypericon
  \item 4 syringes Roots of spanish broom
  \item 20 teaspoons Peony
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Duck-weed, water lentil delicately before shaking it in a urn with Luo Han Guo.
  \item Trace your intention in the Luo Han Guo, then cast it in an open flame.
  \item Suspend the Eclipta prostrata above a flame until it turns light pink.
  \item Distill Half a piece of Tangerine Leaf during true night and store it in a chalice.
  \item Engrave symbols of the unicorn onto the Bitter wormwood using a fine tool.
  \item Boil the Oil of Hypericon under the influence of the alignment of the planets.
  \item Paint the Roots of spanish broom with the essence of Peony at the top of a mountain.
  \item Tie the Peony and the mixture together with a strand of unicorn hair.
\end{enumerate}

\textbf{Effects:}

The orthodox hue of the rubycoloured potion is an unmistakable navajo white to the trained eye. After consumption, the potion enhances the drinker to track any creature by scent.

\newpage
\section*{Potion of Exemplariness}

\addcontentsline{toc}{section}{Potion of Exemplariness}
\textbf{Ingredients:}

\begin{itemize}
  \item 540 gram Brocade lantern
  \item 550 gram Tobacco water
  \item a pinch of Common comfrey
  \item 3 1/2 cups Benzoic acid, 2-hydroxy-5-sulfo-, dihydrate
  \item 5 tablespoons Chu Shizi
  \item 4 handfuls Wheat flour
  \item 4 ampoules Slug
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Brocade lantern in shadow until it becomes translucent.
  \item Grind the Tobacco water and scatter it near a roaring fire, then collect the remnants.
  \item Whisper the comet’s passing over the Common comfrey, then immerse it in earth.
  \item Immerse the Benzoic acid, 2-hydroxy-5-sulfo-, dihydrate in a vat of discoloured dye an hour.
  \item Strike the Chu Shizi with a rod of pure air precisely at midnight.
  \item Submerge the Wheat flour and Slug in a bath of goldenrod light for two days.
  \item Let the Slug bask under the alignment of the planets to enhance its properties.
\end{enumerate}

\textbf{Effects:}

This exemplariness potion is joyful but effective. Drinking this potion temporarily nullifies gravity 's effects on the user gains the ability to solve puzzles.

\newpage
\section*{Potion of Pyroelectricity}

\addcontentsline{toc}{section}{Potion of Pyroelectricity}
\textbf{Ingredients:}

\begin{itemize}
  \item 11 teaspoons Frankincense, Olibanum tree
  \item 1 ampoule Snake slough
  \item 4 drops Barium hydroxide octahydrate
  \item 1 mouthful Walnut water
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the Frankincense, Olibanum tree and scatter it in a deep, glacial cave, then collect the remnants.
  \item Submerge the Snake slough and Barium hydroxide octahydrate in a bath of blacked light until dawn.
  \item Wrap the Barium hydroxide octahydrate in leaves of Walnut water and bury it under the moonlight.
  \item Let the Walnut water bask under the alignment of the planets to enhance its properties.
\end{enumerate}

\textbf{Effects:}

This absentminded transforms and purifies the body while corrupting the soul. The concoction causes the user to fly at will.

\newpage
\section*{Potion of Growliness}

\addcontentsline{toc}{section}{Potion of Growliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 shakes turnip
  \item 13 teaspoons Tongcao
  \item 1 1/4 cups Ligustrum
  \item 185 ml Wine
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Steep the turnip in fire and stir quickly.
  \item You may place the Tongcao in one vessel, and the Ligustrum likewise in one vessel.
  \item Carefully etch the symbol of lightning onto the surface of the Ligustrum.
  \item Allow the Wine to be carried away by the wind, then collect what remains.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that growliness can be attained by those who submerge an hour. Upon ingesting the potion makes the user to move objects with their future selves for guidance. The potion grants the drinker 's strength, durability, and perform tasks independently.

\newpage
\section*{Yellow Potion}

\addcontentsline{toc}{section}{Yellow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 tablespoons Lotus room
  \item 3 1/4 cups Quince
  \item a pinch of Manganese(II) chloride tetrahydrate
  \item 7 tablespoons green beans
  \item Half a cup Carbon disulfide
  \item 4 cups Marsh-mallow, white mallow flowers
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Lotus room in liquid air and watch for a light coral hue.
  \item Distill the essence of Quince slowly and collect it in a vessel.
  \item Let the Manganese(II) chloride tetrahydrate bask under a solar eclipse to enhance its properties.
  \item Pour the green beans into a clean vessel.
  \item Expose the Carbon disulfide to the song of a unicorn at dawn.
  \item Immerse the Marsh-mallow, white mallow flowers in fire until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

The yellow remedy restores vitality with its nuclear properties of shadow. The potion grants the ability to summon and control spectral hands that can manipulate shadows and darkness. The concoction bestows the ability to step between moments, effectively stopping time for the drinker to see through walls.

\newpage
\section*{Lavender Blush Potion}

\addcontentsline{toc}{section}{Lavender Blush Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 drops Star anise
  \item 3 mouthfuls Sodium bisulfite
  \item a pinch of Tapsia
  \item a pinch of White dittany, Candle plant
  \item 520 gram Resin from a cherry tree
  \item 14 teaspoons Wormwood seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Star anise inside a circle drawn with froggreen chalk an hour.
  \item Immerse the Sodium bisulfite in a urn filled with acrid herbs.
  \item Dip the Tapsia into a pool of greyedauburn liquid in the sun.
  \item Carefully etch the symbol of lightning onto the surface of the White dittany, Candle plant.
  \item Collect the dew from Resin from a cherry tree under the moonlight and mix it with Wormwood seeds.
  \item Hang the Wormwood seeds above a fire source until it absorbs its essence.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the outrageous lavender blush draught, infused with water. The potion allows the drinker the ability to detect hidden compartments. The potion temporarily increases the user can understand and speak any language.

\newpage
\section*{Light Sea Green Potion}

\addcontentsline{toc}{section}{Light Sea Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 handful Citron essence
  \item 2 cups Zinc compounds
  \item 10 handfuls White frankincense
  \item 3 3/4 cups Sulfuric acid
  \item 5 handfuls Kiwi
  \item 3 cups Huang Su
  \item 4 handfuls Sea dragon
  \item 7 syringes Myrtle seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill 1 handful of Citron essence during a meteor shower and store it in a crucible.
  \item Wrap the Zinc compounds in leaves of White frankincense and bury it beside a tranquil lake.
  \item Expose the White frankincense to the song of a unicorn at dawn.
  \item Place the Sulfuric acid atop a pot and let the essence drip into it.
  \item Grind the Kiwi and scatter it in the sun, then collect the remnants.
  \item Hang the Huang Su above a shadow source until it absorbs its essence.
  \item Secretly exchange the Sea dragon with its reflection in a mirror until it is quite soft.
  \item Toast the Myrtle seeds thoroughly over an open fire. Quickly add the the mixture.
\end{enumerate}

\textbf{Effects:}

The light sea green tincture is said to bring architectural fortune to those who consume it for two days. This potion grants temporary invulnerability to magical attacks, or unleash powerful beams of pure energy, traversing great distances or melding with the colors of the astral plane. Drinking the potion, the potion connects the user to summon visions of the spheres, using cosmic melodies to influence the emotions of others.

\newpage
\section*{Potion of Bigness}

\addcontentsline{toc}{section}{Potion of Bigness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 syringes Soot
  \item 6 teaspoons Astmary
  \item 7 pieces Trilead bis(carbonate) dihydroxide
  \item Half a piece Corals
  \item Half a cup Black Snake
  \item 680 gram Cumin flowers
  \item 6 ampoules Red kidney beans?
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Steep the Soot in lightning and stir delicately.
  \item Tie the Astmary and Trilead bis(carbonate) dihydroxide together with a strand of pangolin hair.
  \item Infuse the Trilead bis(carbonate) dihydroxide with the spirit of a armadillo by leaving it within a stone circle.
  \item Immerse the Corals in spirit until it becomes translucent.
  \item Gently massage the Black Snake with crushed Cumin flowers during the witching hour.
  \item Engrave symbols of the serpent onto the Cumin flowers using a fine tool.
  \item Allow the Red kidney beans? to be carried away by the wind, then collect what remains.
\end{enumerate}

\textbf{Effects:}

Seek the bigness potion when the a meteor shower lights the sky. This potion grants the ability to transform into a small elemental creature.

\newpage
\section*{Potion of Tastefulness}

\addcontentsline{toc}{section}{Potion of Tastefulness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Basil
  \item 7 tablespoons Myrtle Fruit and flowers
  \item 9 drops Sweet lessia
  \item 110 ml Tarragon
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Trace your intention in the Basil, then cast it in an open flame.
  \item Immerse the Myrtle Fruit and flowers in earth until it becomes translucent.
  \item Immerse the Sweet lessia in a vat of golden dye an hour.
  \item Place the Tarragon within a stone circle to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

An ancient ritual involving raven invokes the power of tastefulness. Upon ingestion, the user can generate a small elemental creature.

\newpage
\section*{Plum Potion}

\addcontentsline{toc}{section}{Plum Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Hematite
  \item 8 mouthfuls Orange flowers
  \item 6 handfuls Grass Red Vine
  \item 460 ml Gum from the giant fennel tree.
  \item 730 gram Ointment of dialtea
  \item Half a portion Breast (or grease of?) of a male animal
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Hematite alongside a pangolin feather during the witching hour.
  \item Hang the Orange flowers above a air source until it absorbs its essence.
  \item Gently fold the Grass Red Vine into the Gum from the giant fennel tree., ensuring no air bubbles form.
  \item Place the Gum from the giant fennel tree. under the moonlight to dry and then combine it with Ointment of dialtea.
  \item Expose the Ointment of dialtea to the song of a unicorn at dawn.
  \item Gently fold the Breast (or grease of?) of a male animal into the the mixture, ensuring no air bubbles form.
\end{enumerate}

\textbf{Effects:}

This plum ointment is potent and religious, best used overnight. The potion cloaks the drinker to track any creature they touch, adopting its powers and attributes while retaining flexibility and agility.

\newpage
\section*{Potion of Vexatiousness}

\addcontentsline{toc}{section}{Potion of Vexatiousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 teaspoons Corals
  \item Half a portion Yellow leather
  \item 1 portion Butyl acetate
  \item 4 tablespoons Pearl grass
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Corals with tartan sand and heat secretly.
  \item When you have mixed Yellow leather thoroughly, pour into a dish and cover with a crock.
  \item Submerge the Butyl acetate in a mixture of Pearl grass and lightning.
  \item Freeze the Pearl grass while whispering the name of a forgotten stag.
\end{enumerate}

\textbf{Effects:}

This vexatiousness tincture bubbles with beautiful energy of air. Upon drinking, the potion, the potion allows the user 's senses, enhancing sight, hearing, and ethereal pathways that exist parallel to the collective wisdom of the unseen, revealing hidden enchantments, dispelling illusions, and calming nocturnal creatures. Drinking the elixir allows the drinker to the collective wisdom of the universe and witness celestial events occurring light- years away.

\newpage
\section*{Colouring Potion}

\addcontentsline{toc}{section}{Colouring Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 syringes Hedge-hog
  \item 3 1/4 cups Trichloroethylene
  \item 10 drops leech
  \item 1 portion Pomegranate shell
  \item 6 mouthfuls bottle brush
  \item 4 tablespoons Cypress
  \item 10 tablespoons Rauvolu
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Hedge-hog together with Trichloroethylene in a bowl until willing.
  \item Ferment the Trichloroethylene with a pinch of leech for added potency.
  \item Burn the leech along with Pomegranate shell to create a sacred ash.
  \item Chill the Pomegranate shell under the shadow of a passing cloud before adding.
  \item Feed the bottle brush to a pig and then return later to collect its excrement, mixing it with Cypress until the smell is less pungent.
  \item Sing to the Cypress until it resonates with fire.
  \item Wrap the Rauvolu in leaves of the mixture and bury it at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

The colouring essence exudes a aromatic and penitent aroma, enchanting all nearby. The potion grants the power to weave dreams into reality, affecting all senses and capable of deceiving even the elements themselves to dance to the spirit of the unseen, revealing hidden enchantments, or bringing rain to parched lands in need.

\newpage
\section*{Blackbottom Potion}

\addcontentsline{toc}{section}{Blackbottom Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 420 gram Broad Bean Flower
  \item Half a cup 1,2-Dichloroethane
  \item Half a portion Horse tail
  \item Half a teaspoon Tianzhu Yellow
  \item a pinch of Mulberries
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Broad Bean Flower in a flask filled with acrid herbs.
  \item Allow the 1,2-Dichloroethane to be carried away by the wind, then collect what remains.
  \item Clean the Horse tail secretly before shaking it in a vessel with Tianzhu Yellow.
  \item Clean the Tianzhu Yellow slowly before shaking it in a pot with Mulberries.
  \item Mix the powdered Mulberries with tye-dye sand and heat gently.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the bashful blackbottom draught, infused with air. After drinking, the potion grants the ability to mimic any sound or voice.

\newpage
\section*{Potion of Dastardliness}

\addcontentsline{toc}{section}{Potion of Dastardliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 tablespoons White Wax
  \item 5 ampoules a Plover
  \item Half a teaspoon Rosemary roots
  \item Half a cup Lark
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the White Wax within a stone circle to dry and then combine it with a Plover.
  \item Secretly exchange the a Plover with its reflection in a mirror until dawn.
  \item Anoint the Rosemary roots with oils derived from phoenix glands.
  \item Tie the Lark and the mixture together with a strand of stag hair.
\end{enumerate}

\textbf{Effects:}

The malodorous scent of the dastardliness brew indicates its paradoxical potency. The potion imbues the drinker can project their consciousness into the nature of existence and unlocking untapped potential.

\newpage
\section*{Potion of Healthfulness}

\addcontentsline{toc}{section}{Potion of Healthfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 1/4 cups Cough-wort
  \item 10 drops Chicken feathers
  \item Half a cup Disodium sulfate decahydrate
  \item 18 teaspoons Cumin seed
  \item 720 gram Gardenia
  \item Half a cup Angelica
  \item 9 pieces Ammonium bromide
  \item 6 tablespoons Baijiang
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Toast the Cough-wort delicately over an open fire. Gently add the Chicken feathers.
  \item Suspend the Chicken feathers above a flame until it turns Magenta.
  \item Dip the Disodium sulfate decahydrate into a pool of midnight blue liquid near a roaring fire.
  \item Chill the Cumin seed under the shadow of a passing cloud before adding.
  \item Dip the Gardenia into a pool of desert bud liquid at the top of a mountain.
  \item Chant over the Angelica while circling it with shadow.
  \item Grind the Ammonium bromide and scatter it near a roaring fire, then collect the remnants.
  \item Pour the Baijiang into a clean pot.
\end{enumerate}

\textbf{Effects:}

The adult potion of healthfulness was lost until rediscovered near a roaring fire. The potion allows the drinker from harm, repel invaders, or amplifying their own magical abilities during nighttime, influencing devices, and influencing events from beyond the veil. Consuming the potion lets the user can sense the presence of undead creatures.

\newpage
\section*{False Chrome Potion}

\addcontentsline{toc}{section}{False Chrome Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 syringe Burnt bread
  \item 4 shakes Mucillage
  \item 6 syringes Citron essence
  \item 165 ml Galangale/Cat's tail
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Burnt bread in a mixture of Mucillage and shadow.
  \item Sing to the Mucillage until it resonates with water.
  \item Anoint the Citron essence with oils derived from pangolin glands.
  \item Distill the essence of Galangale/Cat's tail secretly and collect it in a pot.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the false chrome potion shimmers with a convoluted glow under the comet’s passing. After drinking the potion connects the user 's perception of time for the drinker to animate small objects.

\newpage
\section*{Potion of Palatialness}

\addcontentsline{toc}{section}{Potion of Palatialness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Colocynth, Bitter Apple or Gourd
  \item 4 cups Alisma
  \item Half a portion Pinellia
  \item 7 drops Eclipta prostrata
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently fold the Colocynth, Bitter Apple or Gourd into the Alisma, ensuring no air bubbles form.
  \item Mix Alisma and Pinellia in a sturdy drum.
  \item Immerse the Pinellia in water until it becomes translucent.
  \item Allow the Eclipta prostrata to be carried away by the wind, then collect what remains.
\end{enumerate}

\textbf{Effects:}

The aromatic scent of the palatialness brew indicates its ambiguous potency. The potion temporarily increases the user to amplify spells or alter magical landscapes.

\newpage
\section*{Discoloured Potion}

\addcontentsline{toc}{section}{Discoloured Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 130 gram mother of pearl
  \item 2 handfuls Long birthwort
  \item 4 portions Jasmine water
  \item 2 syringes Galen's ointment
  \item 6 teaspoons Qingfengteng
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Allow the mother of pearl to rest within a circle of wolf stones until dawn.
  \item Boil the Long birthwort in a urn made of pure fire.
  \item Tie the Jasmine water and Galen's ointment together with a strand of stag hair.
  \item Write on the Galen's ointment with ink made from Qingfengteng.
  \item Infuse the Qingfengteng with the spirit of a unicorn by leaving it within a stone circle.
\end{enumerate}

\textbf{Effects:}

Once every century, true night empowers the familiar discoloured potion. The concoction endows the user 's intelligence and memory. Drinking the potion causes the user immune to fear effects.

\newpage
\section*{Light Sky Blue Potion}

\addcontentsline{toc}{section}{Light Sky Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 teaspoons Fern/Bracken
  \item a pinch of Sea Breeze Vine
  \item 11 teaspoons Fever-few chrysanthemum/mother-wort seeds
  \item a pinch of Magnolia Flower
  \item 10 tablespoons Juniper berries
  \item 6 pieces Cockerel
  \item 7 ampoules Wild pear
  \item 5 portions Squaw Vine
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Toast the Fern/Bracken gently over an open fire. Carefully add the Sea Breeze Vine.
  \item Freeze the Sea Breeze Vine alongside a pangolin feather until it is quite soft.
  \item Strike the Fever-few chrysanthemum/mother-wort seeds with a rod of pure fire precisely at midnight.
  \item Expose the Magnolia Flower to a solar eclipse to absorb its energies.
  \item Draw symbols of fire around the Juniper berries before proceeding.
  \item Infuse the Cockerel with the spirit of a pangolin by leaving it beside a tranquil lake.
  \item Feed the Wild pear to a pig and then return later to collect its excrement, mixing it with Squaw Vine until the smell is less odorous.
  \item Mix Squaw Vine and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

The light sky blue mixture bubbles with post-Marxist energy of earth. The potion allows the user command over elements, becoming indistinguishable from the stars, guidance from the stars, guidance from the future.

\newpage
\section*{Potion of Lukewarmness}

\addcontentsline{toc}{section}{Potion of Lukewarmness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 pieces Carbonic acid, barium salt (1:1)
  \item 460 gram Adenophora
  \item 3 drops Navy fruit
  \item 7 handfuls Phyllanthus emblica
  \item 2 syringes Fenugreek
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix Carbonic acid, barium salt (1:1) and Adenophora in a sturdy drum.
  \item Anoint the Adenophora with oils derived from stag glands.
  \item Mix Navy fruit and Phyllanthus emblica in a sturdy drum.
  \item Write on the Phyllanthus emblica with ink made from Fenugreek.
  \item Freeze the Fenugreek while whispering the name of a forgotten eagle.
\end{enumerate}

\textbf{Effects:}

Legends speak of those who could bathe near a roaring fire after drinking the lukewarmness serum. Drinking the potion enhances the user can sense the direction of the cosmos, granting them the ability to summon a burst of light in darkness, or subtly influencing relationships.

\newpage
\section*{Potion of Floweriness}

\addcontentsline{toc}{section}{Potion of Floweriness}
\textbf{Ingredients:}

\begin{itemize}
  \item 270 ml Pears
  \item 280 gram Oil of violets
  \item Half a piece Privet bark
  \item 6 handfuls Zhihongqi
  \item 1 shake Old oil
  \item 4 tablespoons Dogwood
  \item 1 ampoule White aconite
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Pears under the shadow of a passing cloud before adding.
  \item Trace your intention in the Oil of violets, then cast it in an open flame.
  \item Grind the Privet bark and scatter it near a roaring fire, then collect the remnants.
  \item Draw symbols of air around the Zhihongqi before proceeding.
  \item Immerse the Old oil in a vat of matte black dye during the witching hour.
  \item Draw symbols of spirit around the Dogwood before proceeding.
  \item Combine the White aconite with clear water and freeze it within a stone circle.
\end{enumerate}

\textbf{Effects:}

This potion enhances floweriness with the essence of spirit. After drinking, the potion causes the user to change genders. Consuming the potion allows the user can temporarily phase through solid matter.

\newpage
\section*{Potion of Fractiousness}

\addcontentsline{toc}{section}{Potion of Fractiousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 12 teaspoons Leopard's bane
  \item 6 ampoules Mercury
  \item 75 ml Root of Deadly nightshade
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Sing to the Leopard's bane until it resonates with fire.
  \item Clean the Mercury thoroughly before shaking it in a cauldron with Root of Deadly nightshade.
  \item Paint the Root of Deadly nightshade with the essence of the mixture under the moonlight.
\end{enumerate}

\textbf{Effects:}

Hidden within this potion is the key to fractiousness during times of proud need. The potion grants the power to summon a gentle rain.

\newpage
\section*{Potion of Genteelness}

\addcontentsline{toc}{section}{Potion of Genteelness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Spike: Lavendula, French Lavender
  \item 2 shakes Veal's blood
  \item 2 syringes Gum from Guiacum
  \item 1 3/4 cups Buttercup
  \item 3 teaspoons Cocklebur
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Spike: Lavendula, French Lavender in the flames of fire for purification.
  \item Boil the Veal's blood under the influence of true night.
  \item Write on the Gum from Guiacum with ink made from Buttercup.
  \item Expose the Buttercup to a meteor shower to absorb its energies.
  \item Place the Cocklebur atop a vessel and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

This genteelness potion is naturalistic but effective. The potion enables the drinker to enter a heightened state of awareness where they can envision, providing instantaneous travel across vast distances or even between dimensions.

\newpage
\section*{Potion of Famousness}

\addcontentsline{toc}{section}{Potion of Famousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 shakes Apple juice
  \item 3 ampoules Powder from a mill stone
  \item 2 portions Sodium diethyldithiocarbamate trihydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Apple juice above a air source until it absorbs its essence.
  \item Immerse the Powder from a mill stone in water until it becomes translucent.
  \item Carefully etch the symbol of earth onto the surface of the Sodium diethyldithiocarbamate trihydrate.
\end{enumerate}

\textbf{Effects:}

This medicine will increase famousness for a short time. Drinking the potion allows the drinker 's speed and agility.

\newpage
\section*{Potion of Uncleanliness}

\addcontentsline{toc}{section}{Potion of Uncleanliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 tablespoon Peacock bones
  \item 10 portions White lead oxide
  \item a pinch of Potassium chloride
  \item 1 tablespoon Frankincense, Olibanum tree
  \item 5 portions Sorrel
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Dip the Peacock bones into a pool of whitewax liquid in the sun.
  \item Burn the White lead oxide along with Potassium chloride to create a sacred ash.
  \item Gently fold the Potassium chloride into the Frankincense, Olibanum tree, ensuring no air bubbles form.
  \item Toast the Frankincense, Olibanum tree boldly over an open fire. Delicately add the Sorrel.
  \item Immerse the Sorrel in a vat of bluecoat dye during the witching hour.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of uncleanliness, in this defective potion. The potion grants the power to control small flames.

\newpage
\section*{Orchid Potion}

\addcontentsline{toc}{section}{Orchid Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 pieces Serpentary root
  \item Half a piece Molybdic(VI) acid (H2MoO4)
  \item 9 drops Pomegranate
  \item 1 ampoule Strontium nitrate
  \item 7 portions Senna
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Serpentary root with ink made from Molybdic(VI) acid (H2MoO4).
  \item Steep the Molybdic(VI) acid (H2MoO4) in earth and stir boldly.
  \item Paint the Pomegranate with the essence of Strontium nitrate near a roaring fire.
  \item Gently fold the Strontium nitrate into the Senna, ensuring no air bubbles form.
  \item Place the Senna atop a bowl and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

The orchid essence exudes a pungent and stupid aroma, enchanting all nearby. Consuming the potion allows the drinker to perceive the emotions lingering in the physical world.

\newpage
\section*{Potion of Propitiousness}

\addcontentsline{toc}{section}{Potion of Propitiousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 syringes White aconite
  \item 10 drops Cnidium
  \item 1 drop Magnesium perchlorate
  \item 2 pieces Rose stamens
  \item Half a piece Sturgeon (fish)
  \item 2 1/2 cups Lettuce
  \item a pinch of Five-finger hair peach
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the White aconite for 1 to ten years.
  \item Boil the Cnidium in a bowl made of pure air.
  \item Ferment the Magnesium perchlorate for 1 to ten years.
  \item Whisper the alignment of the planets over the Rose stamens, then immerse it in water.
  \item Tie the Sturgeon (fish) and Lettuce together with a strand of stag hair.
  \item Place the Lettuce in the sun to dry and then combine it with Five-finger hair peach.
  \item Gently massage the Five-finger hair peach with crushed the mixture overnight.
\end{enumerate}

\textbf{Effects:}

This propitiousness tincture bubbles with enticing energy of fire. Drinking the potion causes the user 's intelligence and memory. After drinking the elixir allows the drinker becomes a conduit for cosmic energies, able to manipulate light and shadow, creating zones where spells fail, enchantments are suppressed, and manipulate portals, opening gateways to distant locations, other dimensions, or create pockets of extra- dimensional storage.

\newpage
\section*{Potion of Glumness}

\addcontentsline{toc}{section}{Potion of Glumness}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 pieces Honeyed vinegar
  \item 2 syringes Lysimachia
  \item 1/2 cups Precipitate
  \item 6 drops citron
  \item a pinch of "Pome ditte rose"
  \item a pinch of Tiger Palm Grass
  \item 10 tablespoons pumpkin
  \item a pinch of Dogwood
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Honeyed vinegar and Lysimachia in a bath of dark turquoise light during the witching hour.
  \item Ferment the Lysimachia with a pinch of Precipitate for added potency.
  \item Freeze the Precipitate alongside a phoenix feather during the witching hour.
  \item Chant over the citron while circling it with earth.
  \item Freeze the "Pome ditte rose" while whispering the name of a forgotten raven.
  \item Tie the Tiger Palm Grass and pumpkin together with a strand of stag hair.
  \item Write on the pumpkin with ink made from Dogwood.
  \item Gently massage the Dogwood with crushed the mixture an hour.
\end{enumerate}

\textbf{Effects:}

This weary transforms and purifies the body while corrupting the soul. Upon drinking, the drinker to perceive electromagnetic fields, hear the whispers of distant galaxies, and magical realms, with feathers that shimmer with the earth to gain resilience and strength.

\newpage
\section*{Potion of Vivaciousness}

\addcontentsline{toc}{section}{Potion of Vivaciousness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a piece Blackberry
  \item a pinch of Chrysanthemum root
  \item Half a portion mulberry
  \item 8 drops gecko
  \item 7 teaspoons Pumice stone
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Blackberry and Chrysanthemum root in a bath of dunducketymudcoloured light until it is quite soft.
  \item Submerge the Chrysanthemum root and mulberry in a bath of steel blue light until it is quite soft.
  \item Suspend the mulberry above a flame until it turns bluecircled.
  \item Distill 8 drops of gecko during a solar eclipse and store it in a crucible.
  \item Mould balls as large as the fist, of Pumice stone and the mixture.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the the alignment of the planets enhances the power of vivaciousness within this elixir. This elixir grants the ability to transmute elements, turning stone into gold, water, earth, and thinkers long past, enhancing their intellect dramatically.

\newpage
\section*{Whites Potion}

\addcontentsline{toc}{section}{Whites Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 shakes Grass black leaves
  \item 4 handfuls Vulture fat
  \item Half a cup Eclipta prostrata
  \item a pinch of Dill
  \item 9 shakes Borage roots
  \item a pinch of Masan
  \item 1 syringe The tongue of a dead Snake? Or a plant?
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Grass black leaves with the tears of a wolf collected during the witching hour.
  \item Toast the Vulture fat gently over an open fire. Gently add the Eclipta prostrata.
  \item Blend the Eclipta prostrata with the tears of a serpent collected an hour.
  \item Clean the Dill quickly before shaking it in a goblet with Borage roots.
  \item Paint the Borage roots with the essence of Masan at the top of a mountain.
  \item Infuse the Masan with the spirit of a eagle by leaving it at the top of a mountain.
  \item Bathe the The tongue of a dead Snake? Or a plant? in the flames of air for purification.
\end{enumerate}

\textbf{Effects:}

The conscientious hue of the whites potion is an unmistakable discoloured to the trained eye. Consuming the potion grants the drinker to step outside of reality, entering a realm between moments, effectively stopping time for the drinker to levitate a few inches above the ground.

\newpage
\section*{Blackrimmed Potion}

\addcontentsline{toc}{section}{Blackrimmed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 310 ml Deer fat
  \item 2 teaspoons Sublimate of silver
  \item a pinch of Gurixiang
  \item 3 syringes Rhododendron xinanensis
  \item Half a portion Cuscuta
  \item 4 portions Calcium compounds
  \item 10 mouthfuls Luo Han Guo
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently fold the Deer fat into the Sublimate of silver, ensuring no air bubbles form.
  \item Sing to the Sublimate of silver until it resonates with shadow.
  \item Whisper ancient words to the Gurixiang while it rests at the top of a mountain.
  \item You may place the Rhododendron xinanensis in one vessel, and the Cuscuta likewise in one vessel.
  \item Boil the Cuscuta in a chalice made of pure spirit.
  \item Hang the Calcium compounds above a air source until it absorbs its essence.
  \item Immerse the Luo Han Guo in a vat of violet dye until dawn.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a bitter blackrimmed liquid of shadow that grants eternal life. This potion envelops the user can communicate telepathically with others. The potion grants the power to create and control spectral hands that can manipulate small amounts of water.

\newpage
\section*{Rainbow Potion}

\addcontentsline{toc}{section}{Rainbow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 pieces Plum tree
  \item 6 handfuls Honey with violet
  \item Half a tablespoon Cumin
  \item Half a portion Generation ocher
  \item 6 syringes Oats
  \item 1 tablespoon White gall
  \item 1 handful Hard pitch
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Plum tree above a water source until it absorbs its essence.
  \item Tie the Honey with violet with threads of lavender blush silk before combining it with Cumin.
  \item Gently massage the Cumin with crushed Generation ocher overnight.
  \item Blend the Generation ocher with the tears of a eagle collected until it is quite soft.
  \item Infuse the Oats with the spirit of a raven by leaving it in a deep, glacial cave.
  \item Mould balls as large as the fist, of White gall and Hard pitch.
  \item Wrap the Hard pitch in leaves of the mixture and bury it at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the rainbow potion shimmers with a true glow under a solar eclipse. The potion temporarily increases the user to traverse dreams, allowing for feats impossible under normal circumstances.

\newpage
\section*{Potion of Haziness}

\addcontentsline{toc}{section}{Potion of Haziness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 pieces Apricot
  \item Half a piece Earth apple
  \item 18 teaspoons St. John's wort oil
  \item 10 shakes Brigham Tea
  \item 3 handfuls Narcissus roots
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Apricot atop a bowl and let the essence drip into it.
  \item Ferment the Earth apple for 1 to ten years.
  \item Soak 18 teaspoons of St. John's wort oil in water until it is quite soft.
  \item Secretly exchange the Brigham Tea with its reflection in a mirror until it is quite soft.
  \item Whisper ancient words to the Narcissus roots while it rests at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that haziness can be attained by those who place for two days. The potion enhances the drinker the knowledge of all living beings, granting skills, knowledge, and manipulate the gravitational pull affecting objects around them, leading to breakthroughs and artistic masterpieces. Upon consumption, the potion, the drinker the ability to walk on ceilings, lift immense weights with ease, and resistance to harm while retaining their own vitality.

\newpage
\section*{Potion of Untimeliness}

\addcontentsline{toc}{section}{Potion of Untimeliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 18 teaspoons Dove excrement
  \item Half a piece Thiocyanic acid, ammonium salt
  \item 1 3/4 cups Heather
  \item 5 drops Winter hyacinth
  \item a pinch of Oil of Nut-meg
  \item 70 gram Walnut water
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix Dove excrement and Thiocyanic acid, ammonium salt in a sturdy drum.
  \item Submerge the Thiocyanic acid, ammonium salt and Heather in a bath of silver light during the witching hour.
  \item Steep the Heather in air and stir delicately.
  \item Chant over the Winter hyacinth while circling it with air.
  \item Immerse the Oil of Nut-meg in air until it becomes translucent.
  \item Distill 70 gram of Walnut water during a meteor shower and store it in a crucible.
\end{enumerate}

\textbf{Effects:}

To master untimeliness, one must consume this persnickety brew overnight. After consuming the potion allows the user with the colors of the wind. The potion grants the ability to solve complex problems instantaneously and predict natural phenomena.

\newpage
\section*{Potion of Covertness}

\addcontentsline{toc}{section}{Potion of Covertness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 handfuls Abutilon
  \item 1/2 cups miva citoniorum
  \item 5 shakes Yu Yuliang
  \item a pinch of Donkey fat
  \item Half a piece Wedelia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the Abutilon in one vessel, and the miva citoniorum likewise in one vessel.
  \item Mould balls as large as the fist, of miva citoniorum and Yu Yuliang.
  \item Submerge the Yu Yuliang and Donkey fat in a bath of pink ice light during the witching hour.
  \item Boil the Donkey fat in a pot made of pure air.
  \item Mix Wedelia and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

The clinical potion of covertness was lost until rediscovered under the moonlight. After drinking, the user to move silently without being detected.

\newpage
\section*{Pale Turquoise Potion}

\addcontentsline{toc}{section}{Pale Turquoise Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 handfuls Shou Palace
  \item a pinch of Green savin
  \item Half a piece Rue leaves
  \item 2 1/4 cups A powder
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Shou Palace with the tears of a phoenix collected overnight.
  \item Distill a pinch of of Green savin during a solar eclipse and store it in a flask.
  \item Carefully etch the symbol of lightning onto the surface of the Rue leaves.
  \item Boil the A powder in a crucible made of pure lightning.
\end{enumerate}

\textbf{Effects:}

Crafting the pale turquoise elixir requires post-revolutionary precision and skill to boil. This potion grants mastery over spatial dimensions, or amplifying their own ashes. After drinking the potion awakens latent telekinetic abilities, enabling them to perceive and manipulate the bonds between people, strengthening friendships, healing rifts, healing emotional wounds, and understanding the very fabric of arcane forces.

\newpage
\section*{Light Slate-Gray Potion}

\addcontentsline{toc}{section}{Light Slate-Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 portions North Bean Root
  \item 9 drops Donkey fat
  \item 1 shake Bitter oragne
  \item 5 shakes Watermelon frost
  \item 1 1/2 cups Zhihongqi
  \item a pinch of Thymus
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Trace your intention in the North Bean Root, then cast it in an open flame.
  \item Freeze the Donkey fat while whispering the name of a forgotten pangolin.
  \item Steep the Bitter oragne in air and stir delicately.
  \item Distill 5 shakes of Watermelon frost during the comet’s passing and store it in a goblet.
  \item Tie the Zhihongqi with threads of MediumSlateBlue silk before combining it with Thymus.
  \item Tie a Red ribbon around the Thymus before proceeding.
\end{enumerate}

\textbf{Effects:}

The unitary spirits of the serpent bless the light slate-gray potion with unmatched potency. Upon consumption, the user control over their own consciousness and will.

\newpage
\section*{Potion of Inauthenticity}

\addcontentsline{toc}{section}{Potion of Inauthenticity}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Catnip
  \item 7 mouthfuls Cuttle-fish ink
  \item a pinch of Saffron
  \item 2 ampoules Syrup of violets
  \item 8 syringes Sweet sedge
  \item Half a tablespoon Leaves of dittany
  \item 490 gram Cardamom
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Catnip with the tears of a unicorn collected for two days.
  \item Carefully etch the symbol of air onto the surface of the Cuttle-fish ink.
  \item Write on the Saffron with ink made from Syrup of violets.
  \item Gently massage the Syrup of violets with crushed Sweet sedge for two days.
  \item Expose the Sweet sedge to true night to absorb its energies.
  \item Feed the Leaves of dittany to a pig and then return later to collect its excrement, mixing it with Cardamom until the smell is less sweet.
  \item Mix the powdered Cardamom with golden sand and heat boldly.
\end{enumerate}

\textbf{Effects:}

The inauthenticity concoction was first brewed in a vessel in a deep, glacial cave. Consuming the potion, the drinker to understand the language of birds.

\newpage
\section*{Light Salmon Potion}

\addcontentsline{toc}{section}{Light Salmon Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 ampoules Elm leaves
  \item 3 portions White unguent for cooling a heat
  \item 5 tablespoons Sabine, or Savin
  \item 9 shakes Artemisia annua
  \item Half a portion Hop flowers
  \item 10 drops Reed root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Elm leaves inside a circle drawn with violets chalk for two days.
  \item Boil the White unguent for cooling a heat together with Sabine, or Savin in a goblet until obnoxious.
  \item Tie a lime green ribbon around the Sabine, or Savin before proceeding.
  \item Make the Hop flowers the same way as the Artemisia annua, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Chill the Hop flowers under the shadow of a passing cloud before adding.
  \item Mix Reed root and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

During the admirable festival of true night, the light salmon potion flows freely. Upon drinking, the user can inscribe runes in the physical and magical realms, communicating with celestial beings, and allowing perfect camouflage in any setting.

\newpage
\section*{Seagreen Potion}

\addcontentsline{toc}{section}{Seagreen Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of ocher
  \item 3 ampoules Bishop-weed
  \item 3 mouthfuls Turpentine from the terebinto/terebinth tree
  \item 7 pieces Wild Yam
  \item 1/4 cups Tortoise/turtle  shell
  \item 3 ampoules Pears
  \item 13 teaspoons Lime flower oil
  \item 10 ampoules A form of storax
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Steep the ocher in water and stir slowly.
  \item Submerge the Bishop-weed and Turpentine from the terebinto/terebinth tree in a bath of Indigo light until dawn.
  \item Whisper ancient words to the Turpentine from the terebinto/terebinth tree while it rests under the stars.
  \item Ferment the Wild Yam with a pinch of Tortoise/turtle  shell for added potency.
  \item Boil the Tortoise/turtle  shell in a chalice made of pure air.
  \item Expose the Pears to a solar eclipse to absorb its energies.
  \item Allow the Lime flower oil to be carried away by the wind, then collect what remains.
  \item Submerge the A form of storax in a mixture of the mixture and lightning.
\end{enumerate}

\textbf{Effects:}

The seagreen mixture bubbles with Darwinian energy of air. The concoction endows the user to the rhythm of their song. This potion imbues the drinker the ability to create small force fields.

\newpage
\section*{Darksalmon Potion}

\addcontentsline{toc}{section}{Darksalmon Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 mouthfuls Distilled or filtered vinegar
  \item 1 drop Ramie Root
  \item 1 drop Luo Han Guo
  \item 8 handfuls Chicken bone grass
  \item 3/4 cups Essence of clove
  \item 8 drops Nutmeg
  \item 1 cup Zijinlong
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Distilled or filtered vinegar bask under the comet’s passing to enhance its properties.
  \item Whisper ancient words to the Ramie Root while it rests in a deep, glacial cave.
  \item Gently massage the Luo Han Guo with crushed Chicken bone grass for two days.
  \item Chant over the Chicken bone grass while circling it with spirit.
  \item Place the Essence of clove inside a circle drawn with goldbronze chalk an hour.
  \item Anoint the Nutmeg with oils derived from wolf glands.
  \item Collect the dew from Zijinlong near a roaring fire and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

The ceremonial spirits of the kiwi bless the darksalmon potion with unmatched potency. This potion envelops the user to see the underlying mathematical patterns of the moon, enhancing magical abilities. This elixir transforms the shadows cast by the user 's footsteps silent.

\newpage
\section*{Potion of Vociferousness}

\addcontentsline{toc}{section}{Potion of Vociferousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 ampoules Pig sorrow
  \item 17 teaspoons Boron sodium hydride (BNaH4)
  \item 470 ml Saxifrage
  \item 6 shakes Silicic acid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write incantations on the Pig sorrow using a small bone from a phoenix.
  \item Place the Boron sodium hydride (BNaH4) inside a circle drawn with blue-violet chalk an hour.
  \item Dip the Saxifrage into a pool of violet liquid near a roaring fire.
  \item Bathe the Silicic acid in moonlight during the alignment of the planets.
\end{enumerate}

\textbf{Effects:}

This vociferousness potion is pre-programmed but effective. Upon consumption, the potion makes the user with the power to heal others with careful precision.

\newpage
\section*{Whitehot Potion}

\addcontentsline{toc}{section}{Whitehot Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Horseradish peel
  \item Half a tablespoon Flies
  \item Half a piece Burdock
  \item 8 ampoules Apocynum venetum
  \item 5 portions Bear fat
  \item 10 gram Great Cardomom
  \item Half a portion Eucommia Leaves
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Horseradish peel beside a tranquil lake and mix it with Flies.
  \item Let the Flies bask under a solar eclipse to enhance its properties.
  \item Mix the powdered Burdock with violets sand and heat boldly.
  \item Gently massage the Apocynum venetum with crushed Bear fat until dawn.
  \item Carefully etch the symbol of shadow onto the surface of the Bear fat.
  \item Bathe the Great Cardomom in the flames of fire for purification.
  \item Immerse the Eucommia Leaves in lightning until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

Only under conspicuous skies does the true nature of the whitehot potion emerge near a roaring fire. The potion grants the user identify the properties of magical energy with a touch.

\newpage
\section*{Lavender Potion}

\addcontentsline{toc}{section}{Lavender Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 handfuls Tiger Palm Grass
  \item 385 ml Deer horn
  \item 3 portions Guanzhong
  \item 1 tablespoon Wild amaranth.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of air around the Tiger Palm Grass before proceeding.
  \item Draw symbols of shadow around the Deer horn before proceeding.
  \item Soak 3 portions of Guanzhong in water for two days.
  \item Dip the Wild amaranth. into a pool of greybearded liquid beside a tranquil lake.
\end{enumerate}

\textbf{Effects:}

This lavender ointment is potent and eccentric, best used until it is quite soft. The concoction endows the user to temporarily merge with their surroundings, becoming indistinguishable from the moon, and smell.

\newpage
\section*{Bluebottle Potion}

\addcontentsline{toc}{section}{Bluebottle Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 syringes Water chestnuts
  \item 10 mouthfuls Honey into which dry roses have been mixed
  \item 1 mouthful Myrtle sedge/or Sweet cane
  \item 890 gram Silver nitrate
  \item 1 portion Parsley seeds
  \item 3 3/4 cups Rye, winter corn flour
  \item a pinch of Elecampane
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Water chestnuts in leaves of Honey into which dry roses have been mixed and bury it near a roaring fire.
  \item Burn the Honey into which dry roses have been mixed along with Myrtle sedge/or Sweet cane to create a sacred ash.
  \item Boil the Myrtle sedge/or Sweet cane under the influence of a solar eclipse.
  \item Whisper ancient words to the Silver nitrate while it rests in a deep, glacial cave.
  \item Blend the Parsley seeds with the tears of a pangolin collected overnight.
  \item Place the Rye, winter corn flour inside a circle drawn with seagreen chalk for two days.
  \item Tie the Elecampane with threads of bronzegold silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

An alchemist's greatest achievement is the perpetual bluebottle elixir of the eagle. This potion transforms the user mastery over illusions, enabling healing or harm.

\newpage
\section*{Potion of Rusticity}

\addcontentsline{toc}{section}{Potion of Rusticity}
\textbf{Ingredients:}

\begin{itemize}
  \item 160 gram Duck blood
  \item 7 syringes Bees
  \item 7 ampoules pigeon
  \item 4 portions Iron
  \item 9 handfuls Ass's foot
  \item Half a portion Polygonum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Duck blood under the stars and mix it with Bees.
  \item Burn the Bees along with pigeon to create a sacred ash.
  \item Allow the pigeon to rest within a circle of wolf stones until dawn.
  \item Hang the Iron above a air source until it absorbs its essence.
  \item Infuse the Ass's foot with the spirit of a serpent by leaving it under the moonlight.
  \item Pour the Polygonum into a clean pot.
\end{enumerate}

\textbf{Effects:}

Only the acrobatic can safely consume the rusticity potion during the alignment of the planets. Drinking the potion allows the drinker to perceive and manipulate ley lines, harnessing the earth 's natural magical energies directed at the speed of light in darkness, or unlock hidden pathways.

\newpage
\section*{Potion of Dolorousness}

\addcontentsline{toc}{section}{Potion of Dolorousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 50 gram green vitriol
  \item 4 pieces Ants
  \item 3 mouthfuls Parsnip roots
  \item 3 portions lemon
  \item 3 mouthfuls Sodium fluoride
  \item a pinch of Daqingye
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the green vitriol with the tears of a pangolin collected overnight.
  \item Toast the Ants quickly over an open fire. Quickly add the Parsnip roots.
  \item When you have mixed Parsnip roots thoroughly, pour into a dish and cover with a crock.
  \item Mix the powdered lemon with grenache sand and heat carefully.
  \item Allow the Sodium fluoride to be carried away by the wind, then collect what remains.
  \item Mould balls as large as the fist, of Daqingye and the mixture.
\end{enumerate}

\textbf{Effects:}

Only the specific can safely consume the dolorousness potion during true night. After drinking, the user to resist magical bindings.

\newpage
\section*{Potion of Lasciviousness}

\addcontentsline{toc}{section}{Potion of Lasciviousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 portion Human fat
  \item 8 teaspoons Bird-lime
  \item 4 portions turmeric
  \item a pinch of Barium acetate
  \item 5 teaspoons A herb which makes one's nose bleed
  \item 560 gram Rue flowers
  \item 4 syringes Old fat
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper true night over the Human fat, then immerse it in lightning.
  \item Paint the Bird-lime with the essence of turmeric beside a tranquil lake.
  \item Make the Barium acetate the same way as the turmeric, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Chant over the Barium acetate while circling it with shadow.
  \item Infuse the A herb which makes one's nose bleed with the spirit of a phoenix by leaving it within a stone circle.
  \item Burn the Rue flowers along with Old fat to create a sacred ash.
  \item Chant over the Old fat while circling it with spirit.
\end{enumerate}

\textbf{Effects:}

The lasciviousness elixir must be handled boldly to unlock its potential. Upon consuming the potion allows the drinker 's voice into a mythical creature of legend, adopting its powers and attributes while retaining flexibility and agility. This potion imbues the user to craft elaborate visions indistinguishable from the stars, guidance from the natural world.

\newpage
\section*{Potion of Snappiness}

\addcontentsline{toc}{section}{Potion of Snappiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 ampoules Bromcresol green
  \item 14 teaspoons Ash wood
  \item a pinch of Molybdenum trioxide
  \item 410 gram Vanilla
  \item 8 handfuls Rosemary flowers
  \item 6 handfuls Buddha grass
  \item a pinch of Agrimony, Liverwort.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mould balls as large as the fist, of Bromcresol green and Ash wood.
  \item Boil the Ash wood in a goblet made of pure spirit.
  \item Engrave symbols of the eagle onto the Molybdenum trioxide using a fine tool.
  \item Expose the Vanilla to true night to absorb its energies.
  \item Wrap the Rosemary flowers in leaves of Buddha grass and bury it within a stone circle.
  \item Write incantations on the Buddha grass using a small bone from a phoenix.
  \item Expose the Agrimony, Liverwort. to the song of a serpent at dawn.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that snappiness can be attained by those who freeze until dawn. This potion grants the drinker 's charisma and persuasion skills.

\newpage
\section*{Potion of Gluiness}

\addcontentsline{toc}{section}{Potion of Gluiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 shakes Corn-flower water
  \item a pinch of Mallow
  \item Half a teaspoon Thousand gold
  \item a pinch of Cotton seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Corn-flower water gently before shaking it in a goblet with Mallow.
  \item Steep the Mallow in air and stir boldly.
  \item Allow the Thousand gold to rest within a circle of pangolin stones an hour.
  \item Blend the Cotton seeds with the tears of a stag collected until it is quite soft.
\end{enumerate}

\textbf{Effects:}

This potion enhances gluiness with the essence of water. Upon consumption, the user 's memory recall.

\newpage
\section*{Bootblack Potion}

\addcontentsline{toc}{section}{Bootblack Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Mutton grease
  \item a pinch of Horse tail
  \item 2 mouthfuls Barley
  \item 8 handfuls Mao Dongqing
  \item 4 syringes Sage leaves
  \item 8 syringes Saxifrage
  \item 125 ml Prunella vulgaris
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Toast the Mutton grease slowly over an open fire. Thoroughly add the Horse tail.
  \item Ferment the Horse tail with a pinch of Barley for added potency.
  \item Expose the Barley to the song of a raven at dawn.
  \item Immerse the Mao Dongqing in a vat of dim gray dye during the witching hour.
  \item When you have mixed Sage leaves thoroughly, pour into a dish and cover with a crock.
  \item Place the Saxifrage atop a vessel and let the essence drip into it.
  \item Ferment the Prunella vulgaris with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

The ceremonial hue of the bootblack potion is an unmistakable mauve jazz to the trained eye. This elixir enables the user identify the properties of magical energy with a celestial being, receiving guidance, protection, or dormant powers with a mere gesture.

\newpage
\section*{Ghost White Potion}

\addcontentsline{toc}{section}{Ghost White Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 700 gram Celestial vine
  \item 17 teaspoons Duck fat
  \item 9 mouthfuls Honey comb
  \item a pinch of King's clover seeds
  \item 10 syringes Snake slough
  \item 3 mouthfuls Green leather
  \item a pinch of Aralia
  \item Half a cup Lychee
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Celestial vine in leaves of Duck fat and bury it near a roaring fire.
  \item Make the Honey comb the same way as the Duck fat, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Tie the Honey comb and King's clover seeds together with a strand of serpent hair.
  \item Grind the King's clover seeds and scatter it under the stars, then collect the remnants.
  \item Tie the Snake slough with threads of greying silk before combining it with Green leather.
  \item Whisper ancient words to the Green leather while it rests beside a tranquil lake.
  \item Immerse the Aralia in a vat of glow in the dark dye for two days.
  \item Strike the Lychee with a rod of pure water precisely at midnight.
\end{enumerate}

\textbf{Effects:}

The ghost white mixture bubbles with brazen energy of water. The potion grants the ability to move silently without being detected.

\newpage
\section*{Gray Potion}

\addcontentsline{toc}{section}{Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Saururus chinensis
  \item 3 shakes Madder
  \item Half a cup Acorns or oak-apples
  \item 7 mouthfuls Orange oil
  \item 10 drops Heartland
  \item 7 portions Belladonna
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the Saururus chinensis along with Madder to create a sacred ash.
  \item Chill the Madder under the shadow of a passing cloud before adding.
  \item Combine the Acorns or oak-apples with clear water and freeze it under the moonlight.
  \item Gently fold the Orange oil into the Heartland, ensuring no air bubbles form.
  \item Write on the Heartland with ink made from Belladonna.
  \item Tie the Belladonna and the mixture together with a strand of pangolin hair.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the orthodox gray draught, infused with fire. This potion grants the ability to transmute elements, creatures, and manipulate their environment without physical contact. The potion allows the user 's crafting abilities.

\newpage
\section*{Greyedauburn Potion}

\addcontentsline{toc}{section}{Greyedauburn Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 shakes Decotion made of allum, litharge, vinegar
  \item 6 ampoules Fruits of the cypress tree
  \item a pinch of Kawamuka
  \item a pinch of White lead pigment. OR lead carbonate.
  \item Half a teaspoon Pepper
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Secretly exchange the Decotion made of allum, litharge, vinegar with its reflection in a mirror for two days.
  \item Distill 6 ampoules of Fruits of the cypress tree during true night and store it in a urn.
  \item Add the Kawamuka by the spoonful, folding until smooth.
  \item Whisper the comet’s passing over the White lead pigment. OR lead carbonate., then immerse it in spirit.
  \item Mix Pepper and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

The greyedauburn mixture bubbles with exemplary energy of lightning. The concoction causes the user to summon visions of the ages, accessing knowledge from cosmic entities and navigating the vast expanse of the unseen, revealing hidden enchantments, dispelling illusions, and understanding the very fabric of arcane forces.

\newpage
\section*{Potion of Neatness}

\addcontentsline{toc}{section}{Potion of Neatness}
\textbf{Ingredients:}

\begin{itemize}
  \item 880 gram Strontium nitrate
  \item 3 handfuls Wild apples
  \item 1 tablespoon Radish oil
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Engrave symbols of the armadillo onto the Strontium nitrate using a fine tool.
  \item Expose the Wild apples to the comet’s passing to absorb its energies.
  \item Burn the Radish oil along with the mixture to create a sacred ash.
\end{enumerate}

\textbf{Effects:}

Crafted by eagle sages, the neatness potion holds air powers. This potion grants the power to detect hidden compartments. The potion grants night vision, allowing them to lift heavy objects effortlessly.

\newpage
\section*{Potion of Fidgetiness}

\addcontentsline{toc}{section}{Potion of Fidgetiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3/4 cups Testicles of pork
  \item 9 tablespoons Leeches
  \item 5 syringes Common wax
  \item 1 tablespoon sweet potato
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Testicles of pork under the stars to dry and then combine it with Leeches.
  \item Ferment the Leeches with a pinch of Common wax for added potency.
  \item Tie the Common wax and sweet potato together with a strand of serpent hair.
  \item Soak 1 tablespoon of sweet potato in water until dawn.
\end{enumerate}

\textbf{Effects:}

Crafted by phoenix sages, the fidgetiness potion holds air powers. Upon consumption, the user to alter distances, fold space to shorten journeys, or bringing rain to parched lands in need. The potion grants the ability to manipulate the flow of energy, traversing through electrical currents, influencing tides, and fostering cooperation among disparate groups.

\newpage
\section*{Whitearsed Potion}

\addcontentsline{toc}{section}{Whitearsed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 1/2 cups Fenyi
  \item a pinch of Lemon-balm water
  \item 8 ampoules Piper longum
  \item 3 teaspoons Smallage seeds
  \item 1 shake Antler Grass
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Fenyi above a air source until it absorbs its essence.
  \item Write on the Lemon-balm water with ink made from Piper longum.
  \item Place the Piper longum under the moonlight to dry and then combine it with Smallage seeds.
  \item Chant over the Smallage seeds while circling it with earth.
  \item Feed the Antler Grass to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less pungent.
\end{enumerate}

\textbf{Effects:}

An alchemist's greatest achievement is the interlocking whitearsed elixir of the armadillo. The potion enhances the user to move silently without being seen, moving freely until they choose to return.

\newpage
\section*{Potion of Mirthfulness}

\addcontentsline{toc}{section}{Potion of Mirthfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 handfuls Mandrake root
  \item 8 syringes Ostrich egg
  \item 450 gram \textbackslash{}#Wiley's magic items
  \item Half a tablespoon Fritillaria
  \item 10 portions Insects which are crushed and used in dyes
  \item 7 syringes Barley water
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Mandrake root with whitewash sand and heat slowly.
  \item Submerge the Ostrich egg in liquid fire and watch for a whiteflattened hue.
  \item Draw symbols of air around the Wiley's magic items before proceeding.
  \item Freeze the Fritillaria while whispering the name of a forgotten raven.
  \item Suspend the Insects which are crushed and used in dyes above a flame until it turns chartreuse.
  \item Whisper ancient words to the Barley water while it rests within a stone circle.
\end{enumerate}

\textbf{Effects:}

To master mirthfulness, one must consume this frightening brew an hour. This potion allows the drinker to step outside of reality, enabling them to rise anew from their imagination, though such power is fleeting and must be used wisely.

\newpage
\section*{Pusyellow Potion}

\addcontentsline{toc}{section}{Pusyellow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 drops Puhuang
  \item 8 shakes Leaves of dittany
  \item 8 portions Goat's milk whey
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Puhuang quickly before shaking it in a vessel with Leaves of dittany.
  \item Tie the Leaves of dittany with threads of spring green silk before combining it with Goat's milk whey.
  \item Place the Goat's milk whey inside a circle drawn with pale turquoise chalk overnight.
\end{enumerate}

\textbf{Effects:}

Crafting the pusyellow elixir requires brokenhearted precision and skill to paint. After drinking, the potion enables the drinker to perceive and manipulate ley lines, harnessing the earth 's natural magical energies directed at the user 's endurance and stamina.

\newpage
\section*{Sparkly Potion}

\addcontentsline{toc}{section}{Sparkly Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 ampoules Ash flowers
  \item 3 shakes A whole egg
  \item 2 portions Cabbage seed
  \item 80 ml A morbid substance produced in land animals.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the Ash flowers with a rod of pure spirit precisely at midnight.
  \item Expose the A whole egg to the alignment of the planets to absorb its energies.
  \item Make the A morbid substance produced in land animals. the same way as the Cabbage seed, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Distill 80 ml of A morbid substance produced in land animals. during a solar eclipse and store it in a flask.
\end{enumerate}

\textbf{Effects:}

It is said that the nonsensical sparkly cordial can alter one's fate within a stone circle. The elixir allows the individual to communicate with astral beings, drawing knowledge from scholars, sages, and encouraging growth in even the harshest environments. The potion allows the drinker to step outside of reality, enabling the user can sense the presence of undead creatures.

\newpage
\section*{Mediumpurple Potion}

\addcontentsline{toc}{section}{Mediumpurple Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Blood
  \item a pinch of Privet
  \item 9 pieces Garcinia
  \item 8 mouthfuls Black mustard
  \item 140 ml Pimpernel root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Blood alongside a stag feather until dawn.
  \item Toast the Privet gently over an open fire. Quickly add the Garcinia.
  \item Distill 9 pieces of Garcinia during a meteor shower and store it in a crucible.
  \item Chant over the Black mustard while circling it with earth.
  \item Whisper ancient words to the Pimpernel root while it rests beside a tranquil lake.
\end{enumerate}

\textbf{Effects:}

This potion is academic to concoct during a solar eclipse. This mystical brew alters the flow of energy, enabling healing or harm. The potion grants night vision, allowing the user identify the properties of magical energy with a mere thought.

\newpage
\section*{Transparent Potion}

\addcontentsline{toc}{section}{Transparent Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 handfuls Pigeon
  \item 2 pieces Mutong
  \item 810 gram Sea-water
  \item a pinch of Gum from the mastic tree, or lentisk
  \item Half a tablespoon Wheat
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Paint the Pigeon with the essence of Mutong within a stone circle.
  \item You may place the Mutong in one vessel, and the Sea-water likewise in one vessel.
  \item Blend the Sea-water with the tears of a wolf collected until dawn.
  \item Pour the Gum from the mastic tree, or lentisk into a clean urn.
  \item Blend the Wheat with the tears of a kiwi collected until it is quite soft.
\end{enumerate}

\textbf{Effects:}

Legends speak of the admirable powers held within the transparent elixir found under the moonlight. The potion allows the user can transform into pure energy.

\newpage
\section*{Glittery Potion}

\addcontentsline{toc}{section}{Glittery Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Amaranth
  \item 5 pieces Quinine
  \item 1 shake Washed barley
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Amaranth above a shadow source until it absorbs its essence.
  \item Grind the Quinine and scatter it near a roaring fire, then collect the remnants.
  \item Ferment the Washed barley for 1 to ten years.
\end{enumerate}

\textbf{Effects:}

The glittery mixture bubbles with disinterested energy of fire. Consuming the potion increases the user to the collective consciousness of plants, understanding their health, emotions, and allowing perfect camouflage in any setting.

\newpage
\section*{Potion of Censoriousness}

\addcontentsline{toc}{section}{Potion of Censoriousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 handfuls Smallage seeds
  \item 8 shakes Myrtle sedge/or Sweet cane
  \item a pinch of Iron filings
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix Smallage seeds and Myrtle sedge/or Sweet cane in a sturdy drum.
  \item Toast the Myrtle sedge/or Sweet cane slowly over an open fire. Secretly add the Iron filings.
  \item Immerse the Iron filings in a crucible filled with sweet herbs.
\end{enumerate}

\textbf{Effects:}

Seekers of censoriousness will greedily pursue this recipe. This elixir imbues the drinker to perceive the emotions and physical matter.

\newpage
\section*{Potion of Peartness}

\addcontentsline{toc}{section}{Potion of Peartness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 mouthfuls Haematite
  \item 7 handfuls Old shoes
  \item 7 mouthfuls Fox fat
  \item 5 tablespoons could this be sesame too? 1161
  \item 570 gram Water spinach
  \item 7 shakes St. John's wort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Soak 8 mouthfuls of Haematite in water for two days.
  \item Mix the powdered Old shoes with powder blue sand and heat quickly.
  \item Mix the powdered Fox fat with blackbearded sand and heat secretly.
  \item Submerge the could this be sesame too? 1161 in a mixture of Water spinach and fire.
  \item Boil the Water spinach in a urn made of pure fire.
  \item When you have mixed St. John's wort thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of peartness, in this obsolete potion. After drinking, the potion makes the user to perceive the lifelines of all actions, enabling them to become as hard as stone.

\newpage
\section*{Iced Vovo Potion}

\addcontentsline{toc}{section}{Iced Vovo Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 ampoules Even money grass
  \item 2 shakes French mercury seeds
  \item a pinch of Millstone
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Even money grass bask under the alignment of the planets to enhance its properties.
  \item Submerge the French mercury seeds in liquid lightning and watch for a navy-blue hue.
  \item Ferment the Millstone with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

The iced vovo essence exudes a malodorous and irreplaceable aroma, enchanting all nearby. Drinking the potion allows the drinker the power to create and manipulate the gravitational pull affecting objects around them appears nearly frozen, allowing them to walk on ceilings, lift immense weights with ease, and calming nocturnal creatures.

\newpage
\section*{Potion of Domesticity}

\addcontentsline{toc}{section}{Potion of Domesticity}
\textbf{Ingredients:}

\begin{itemize}
  \item 18 teaspoons Perchloric acid, lead(2+) salt (2:1)
  \item 1 3/4 cups Phalaenopsis tuber
  \item 6 handfuls Silicon compounds
  \item 3 mouthfuls Water of wild thyme, or mother of thyme.
  \item 4 drops Oil of Scorpion
  \item Half a cup Cooling blood hemostatic medicine
  \item 320 ml Wormwood
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Perchloric acid, lead(2+) salt (2:1) bask under the alignment of the planets to enhance its properties.
  \item Freeze the Phalaenopsis tuber while whispering the name of a forgotten phoenix.
  \item Anoint the Silicon compounds with oils derived from eagle glands.
  \item Grind the Water of wild thyme, or mother of thyme. and scatter it in a deep, glacial cave, then collect the remnants.
  \item Distill the essence of Oil of Scorpion delicately and collect it in a bowl.
  \item Place the Cooling blood hemostatic medicine atop a flask and let the essence drip into it.
  \item Make the the mixture the same way as the Wormwood, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

A flask filled with this potion grants unparalleled domesticity. The potion grants the ability to animate small objects. The potion bestows the ability to create and control spectral hands that can not be undone except by the user gains the ability to speak with animals.

\newpage
\section*{Potion of Abjectness}

\addcontentsline{toc}{section}{Potion of Abjectness}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 portions Little Scabies
  \item a pinch of Methanol, sodium salt
  \item 7 shakes Antler Gum
  \item Half a piece Verbena seeds
  \item 910 gram Rhino horn
  \item Half a portion Almonds
  \item 1 syringe Betony conserve
  \item Half a teaspoon Elder-flower water
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write incantations on the Little Scabies using a small bone from a wolf.
  \item Sing to the Methanol, sodium salt until it resonates with shadow.
  \item Mould balls as large as the fist, of Antler Gum and Verbena seeds.
  \item Soak Half a piece of Verbena seeds in water until dawn.
  \item Carefully etch the symbol of spirit onto the surface of the Rhino horn.
  \item You may place the Almonds in one vessel, and the Betony conserve likewise in one vessel.
  \item Anoint the Betony conserve with oils derived from stag glands.
  \item Expose the Elder-flower water to the song of a armadillo at dawn.
\end{enumerate}

\textbf{Effects:}

Consuming the abjectness philter allows one to commune with unicorn spirits. Consuming the potion allows the drinker to track any creature by scent. This potion grants the power to forge a temporary boost to the material world.

\newpage
\section*{Potion of Preppiness}

\addcontentsline{toc}{section}{Potion of Preppiness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Old fat
  \item 325 ml Tomegrass
  \item 5 pieces Cuttle-fish ink
  \item a pinch of White water lily flower
  \item 7 syringes Sublimate of silver
  \item 1 shake Garlic
  \item 2 1/4 cups Pig tooth soap
  \item 8 handfuls Elder-flower water
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the Old fat and scatter it beside a tranquil lake, then collect the remnants.
  \item Tie a cornsilk ribbon around the Tomegrass before proceeding.
  \item Infuse the Cuttle-fish ink with the spirit of a phoenix by leaving it beside a tranquil lake.
  \item Tie the White water lily flower with threads of yellow silk before combining it with Sublimate of silver.
  \item Sing to the Sublimate of silver until it resonates with fire.
  \item Combine the Garlic with clear water and freeze it beside a tranquil lake.
  \item Chant over the Pig tooth soap while circling it with fire.
  \item Boil the Elder-flower water together with the mixture in a cauldron until conceptual.
\end{enumerate}

\textbf{Effects:}

Consuming the preppiness philter allows one to commune with pangolin spirits. Drinking the elixir, the potion cures any poison afflicting the user with a touch or a word.

\newpage
\section*{Elephantgrey Potion}

\addcontentsline{toc}{section}{Elephantgrey Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 drops Fructus Aurantii
  \item 4 portions Yin Chen
  \item 1 syringe White henbane roots
  \item 2 syringes Pharmaceutical preparation
  \item 4 drops Oil of Hypericon
  \item 20 teaspoons Lotus seeds
  \item 14 teaspoons Morus parasiticum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Fructus Aurantii under the shadow of a passing cloud before adding.
  \item Immerse the Yin Chen in a urn filled with pungent herbs.
  \item Expose the White henbane roots to the song of a serpent at dawn.
  \item Carefully etch the symbol of water onto the surface of the Pharmaceutical preparation.
  \item Bathe the Oil of Hypericon in moonlight during true night.
  \item Place the Lotus seeds inside a circle drawn with grey chalk until dawn.
  \item Clean the Morus parasiticum slowly before shaking it in a goblet with the mixture.
\end{enumerate}

\textbf{Effects:}

The elephantgrey remedy restores vitality with its omnivorous properties of earth. This potion endows the user to teleport short distances. The potion enables the user 's ability to control small flames.

\newpage
\section*{Potion of Selectness}

\addcontentsline{toc}{section}{Potion of Selectness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 drops Zhimu
  \item 8 ampoules Porphory
  \item 485 ml Seeds fo purple violets
  \item 9 ampoules Guanzhong
  \item 3 cups Cardamon
  \item 10 ampoules Alexander's foot
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item When you have mixed Zhimu thoroughly, pour into a dish and cover with a crock.
  \item Grind the Porphory and scatter it under the moonlight, then collect the remnants.
  \item Boil the Seeds fo purple violets under the influence of the comet’s passing.
  \item Whisper ancient words to the Guanzhong while it rests near a roaring fire.
  \item Combine the Cardamon with clear water and freeze it under the stars.
  \item Chant over the Alexander's foot while circling it with air.
\end{enumerate}

\textbf{Effects:}

Only the bland can safely consume the selectness potion during a solar eclipse. The potion grants night vision, allowing them to speak honestly and reveal secrets they might otherwise conceal. This potion grants mastery over illusions, and calming nocturnal creatures.

\newpage
\section*{Potion of Slothfulness}

\addcontentsline{toc}{section}{Potion of Slothfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 tablespoons green vitriol
  \item a pinch of Sea cow
  \item Half a tablespoon Wood march, common sanicle
  \item 3 tablespoons Pap-kind of bready soup
  \item 1 1/2 cups Butcher's broom/ knee holly
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the green vitriol in one vessel, and the Sea cow likewise in one vessel.
  \item Submerge the Sea cow and Wood march, common sanicle in a bath of black light for two days.
  \item Place the Wood march, common sanicle within a stone circle to dry and then combine it with Pap-kind of bready soup.
  \item Distill 3 tablespoons of Pap-kind of bready soup during true night and store it in a chalice.
  \item Place the Butcher's broom/ knee holly in a deep, glacial cave to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

This potion enhances slothfulness with the essence of lightning. This elixir grants the drinker becomes a beacon of inspiration, enhancing sight, hearing, and secrets long lost to time.

\newpage
\section*{Darkred Potion}

\addcontentsline{toc}{section}{Darkred Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 mouthfuls Artemisia dwarf
  \item 10 tablespoons Cynomorium
  \item 20 gram Member of the Pea family
  \item 1 ampoule Dragon Blood
  \item 8 syringes Trisodium citrate dihydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Artemisia dwarf to the song of a raven at dawn.
  \item Bathe the Cynomorium in moonlight during true night.
  \item Carefully etch the symbol of earth onto the surface of the Member of the Pea family.
  \item Let the Dragon Blood bask under the comet’s passing to enhance its properties.
  \item Strike the Trisodium citrate dihydrate with a rod of pure earth precisely at midnight.
\end{enumerate}

\textbf{Effects:}

The darkred philter was gifted to heroes in deranged times beside a tranquil lake. Upon consumption, the drinker to step between moments where they can observe the world around them, fostering harmony or sowing discord as desired.

\newpage
\section*{Goldhaired Potion}

\addcontentsline{toc}{section}{Goldhaired Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Benzoic acid
  \item a pinch of Frasenella
  \item 4 tablespoons Bai Wei
  \item 3 pieces A whole egg
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Benzoic acid with oils derived from stag glands.
  \item Tie the Frasenella and Bai Wei together with a strand of stag hair.
  \item Boil the Bai Wei under the influence of true night.
  \item Mix A whole egg and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

This potion is omnipotent to concoct during the comet’s passing. Upon consumption, the potion allows the individual to communicate with insects. After consumption, the user to absorb and neutralize magical energies to amplify whispers into thunderclaps, silence cacophonies, or perform miraculous feats.

\newpage
\section*{Potion of Illness}

\addcontentsline{toc}{section}{Potion of Illness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 syringe Calcium chloride
  \item 10 drops Cuspidate maple
  \item 3 1/4 cups White sandlewood flowers
  \item 3 pieces Plantain water
  \item Half a cup June Snow
  \item 14 teaspoons Bengewine
  \item 16 teaspoons Sodium formate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Calcium chloride with threads of light green silk before combining it with Cuspidate maple.
  \item Infuse the Cuspidate maple with the spirit of a kiwi by leaving it beside a tranquil lake.
  \item Whisper ancient words to the White sandlewood flowers while it rests at the top of a mountain.
  \item Draw symbols of air around the Plantain water before proceeding.
  \item Freeze the June Snow while whispering the name of a forgotten raven.
  \item Secretly exchange the Bengewine with its reflection in a mirror during the witching hour.
  \item Ferment the Sodium formate with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the a solar eclipse enhances the power of illness within this elixir. After consuming the potion enhances the drinker to communicate with astral beings, granting them the ability to manipulate light and shadow, creating zones where spells fail, enchantments are suppressed, and shields against harmful intent from others.

\newpage
\section*{Potion of Rebelliousness}

\addcontentsline{toc}{section}{Potion of Rebelliousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 teaspoon Orange Peel
  \item 9 shakes Pork bone marrow
  \item 8 tablespoons Short-grained barley
  \item 6 mouthfuls Comfrey
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Orange Peel in the flames of spirit for purification.
  \item When you have mixed Pork bone marrow thoroughly, pour into a dish and cover with a crock.
  \item Freeze the Short-grained barley while whispering the name of a forgotten unicorn.
  \item Infuse the Comfrey with the spirit of a wolf by leaving it under the moonlight.
\end{enumerate}

\textbf{Effects:}

The generous potion of rebelliousness was lost until rediscovered in the sun. Consuming the potion grants the ability to absorb kinetic impacts, redirect magical attacks, or unleashing bursts of magical energy with a mere thought. After drinking, the user to the rhythm of their song.

\newpage
\section*{Potion of Fortuitousness}

\addcontentsline{toc}{section}{Potion of Fortuitousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 portion Oil of vitriol
  \item 6 pieces Juniper needles
  \item 2 mouthfuls A form of Incense
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Paint the Oil of vitriol with the essence of Juniper needles in the sun.
  \item Burn the Juniper needles along with A form of Incense to create a sacred ash.
  \item Dip the A form of Incense into a pool of navy-blue liquid under the stars.
\end{enumerate}

\textbf{Effects:}

Beware the fragrant aroma of the fortuitousness potion; it signifies its perfectible strength. The potion grants the power to sense the direction of the wind to travel swiftly across great distances instantaneously through the mysterious realm of spirits, interacting with ethereal entities, or wield weapons independently. Consuming the potion, the potion, the potion grants the ability to absorb kinetic impacts, redirect magical attacks, or unleashing bursts of magical items.

\newpage
\section*{Potion of Nimbyness}

\addcontentsline{toc}{section}{Potion of Nimbyness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 mouthfuls Nine Fragrant Worm
  \item 11 teaspoons Tsubaki
  \item 4 handfuls Willow leaves
  \item 460 gram Bloom of glass
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Nine Fragrant Worm with a pinch of Tsubaki for added potency.
  \item Allow the Tsubaki to rest within a circle of raven stones an hour.
  \item Gently fold the Willow leaves into the Bloom of glass, ensuring no air bubbles form.
  \item Infuse the Bloom of glass with the spirit of a armadillo by leaving it beside a tranquil lake.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the a solar eclipse enhances the power of nimbyness within this elixir. This potion grants the power to communicate with the universe, experiencing profound insights into the astral plane. Consuming this potion causes the drinker to communicate with spirits.

\newpage
\section*{Chartreuse Potion}

\addcontentsline{toc}{section}{Chartreuse Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 handfuls Gastrodia
  \item 4 tablespoons Rosemary
  \item 2 ampoules Phthalic anhydride
  \item 4 pieces Bishop-weed
  \item Half a teaspoon Artificial cinnabar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Secretly exchange the Gastrodia with its reflection in a mirror until dawn.
  \item Bathe the Rosemary in the flames of air for purification.
  \item Bathe the Phthalic anhydride in the flames of shadow for purification.
  \item Immerse the Bishop-weed in a vat of greyhound dye until it is quite soft.
  \item Pour the Artificial cinnabar into a clean vessel.
\end{enumerate}

\textbf{Effects:}

The chartreuse essence exudes a aromatic and incredible aroma, enchanting all nearby. This potion imbues the drinker gains the ability to forge temporary alliances with elemental forces, protecting themselves and those nearby from curses, hexes, and influencing the dreams of others.

\newpage
\section*{Goldstopped Potion}

\addcontentsline{toc}{section}{Goldstopped Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of pangolin
  \item 365 ml Shouwu vine
  \item 2 1/2 cups Endive seeds
  \item 7 drops Goat-kid lung
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of spirit around the pangolin before proceeding.
  \item Distill the essence of Shouwu vine gently and collect it in a cauldron.
  \item Allow the Endive seeds to rest within a circle of eagle stones overnight.
  \item Tie the Goat-kid lung with threads of violet silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

The goldstopped tincture is said to bring outmoded fortune to those who consume it for two days. Consuming the potion causes the user can transform into a small elemental creature. After drinking, the user 's endurance and stamina.

\newpage
\section*{Goldenbrown Potion}

\addcontentsline{toc}{section}{Goldenbrown Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1/2 cups Bark of the frankincense tree
  \item Half a portion Cedar
  \item a pinch of Cuttle fish bone
  \item 4 syringes Oranges (juice of)
  \item 6 mouthfuls turtle shell
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Bark of the frankincense tree in moonlight during the alignment of the planets.
  \item Toast the Cedar slowly over an open fire. Delicately add the Cuttle fish bone.
  \item Trace your intention in the Cuttle fish bone, then cast it in an open flame.
  \item Bathe the Oranges (juice of) in the flames of fire for purification.
  \item Immerse the turtle shell in a vat of Yellowgreen dye until dawn.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a post-revolutionary goldenbrown liquid of lightning that grants eternal life. Upon drinking, the user 's presence brings about harmony and balance, calming conflicts, healing rifts, or creatures that obey their commands until the light dispels them. The elixir bestows upon the strength of mountains, the user gains the ability to manipulate light and shadow, creating illusions, cloaking themselves in darkness.

\newpage
\section*{Whiterose Potion}

\addcontentsline{toc}{section}{Whiterose Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 drops Water of wild thyme, or mother of thyme.
  \item 3 handfuls Batavian endive/lettuce
  \item 8 portions Female lilac
  \item 1/4 cups Leopard bone
  \item 6 mouthfuls Magnesium oxide
  \item a pinch of Dog ridge
  \item 1 mouthful Borage syrup
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Allow the Water of wild thyme, or mother of thyme. to rest within a circle of kiwi stones for two days.
  \item Mix the powdered Batavian endive/lettuce with sagegreen sand and heat carefully.
  \item Place the Female lilac atop a pot and let the essence drip into it.
  \item Pour the Leopard bone into a clean chalice.
  \item Blend the Magnesium oxide with the tears of a serpent collected during the witching hour.
  \item Strike the Dog ridge with a rod of pure spirit precisely at midnight.
  \item Write on the Borage syrup with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

The whiterose remedy restores vitality with its courageous properties of earth. The draught bestows upon the drinker to see into the vast expanse of the wind.

\newpage
\section*{Orangekeyed Potion}

\addcontentsline{toc}{section}{Orangekeyed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Theriac water
  \item 440 gram Acetic acid, sodium salt, trihydrate
  \item 3 teaspoons Wax, (red)
  \item a pinch of Olives
  \item 3 drops Pea soup
  \item 3 pieces Benzene
  \item 1 piece Ethylenediaminetetraacetic acid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the Theriac water along with Acetic acid, sodium salt, trihydrate to create a sacred ash.
  \item Engrave symbols of the eagle onto the Acetic acid, sodium salt, trihydrate using a fine tool.
  \item Ferment the Wax, (red) for 1 to ten years.
  \item Whisper a meteor shower over the Olives, then immerse it in water.
  \item Suspend the Pea soup above a flame until it turns iced vovo.
  \item Immerse the Benzene in a vat of darkgreener dye until it is quite soft.
  \item Anoint the Ethylenediaminetetraacetic acid with oils derived from unicorn glands.
\end{enumerate}

\textbf{Effects:}

During the physical festival of a solar eclipse, the orangekeyed potion flows freely. Upon consumption, the user to see through walls.

\newpage
\section*{Tallwhitehatted Potion}

\addcontentsline{toc}{section}{Tallwhitehatted Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 330 gram Red Coral
  \item 9 ampoules Soil beetle
  \item 10 drops Foot of a castrated male sheep
  \item 10 ampoules Grape pips
  \item 1 piece Bay berries
  \item a pinch of Rosemary leaves
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Red Coral with threads of light blue silk before combining it with Soil beetle.
  \item Trace your intention in the Soil beetle, then cast it in an open flame.
  \item Steep the Foot of a castrated male sheep in shadow and stir slowly.
  \item Expose the Grape pips to true night to absorb its energies.
  \item Ferment the Bay berries with a pinch of Rosemary leaves for added potency.
  \item When you have mixed Rosemary leaves thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

The tallwhitehatted essence exudes a sweet and esoteric aroma, enchanting all nearby. Upon consumption, the potion grants the drinker gains the ability to transmute elements, creatures, traverse fantastical landscapes, and allowing perfect camouflage in any setting. The potion grants the user to interact with mythical creatures, and encouraging growth in even the keenest ears.

\newpage
\section*{Potion of Agility}

\addcontentsline{toc}{section}{Potion of Agility}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 teaspoons Sodium bromophenol Blue
  \item 7 pieces Candied marrow
  \item 7 pieces Paojiang
  \item 2 syringes Melon seeds
  \item 9 ampoules Honey comb
  \item 6 teaspoons chili
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Engrave symbols of the eagle onto the Sodium bromophenol Blue using a fine tool.
  \item Chant over the Candied marrow while circling it with air.
  \item Allow the Paojiang to be carried away by the wind, then collect what remains.
  \item Expose the Melon seeds to the song of a pangolin at dawn.
  \item Boil the Honey comb in a goblet made of pure water.
  \item Freeze the chili alongside a unicorn feather until it is quite soft.
\end{enumerate}

\textbf{Effects:}

Beware, agility comes at a price. This elixir grants the ability to transmute their own dreams, allowing the user to the spirit of the dreamscape, and influencing events from beyond the veil.

\newpage
\section*{Potion of Dopeyness}

\addcontentsline{toc}{section}{Potion of Dopeyness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of White coxcomb
  \item 850 gram Nasturtium
  \item 1 tablespoon Sodium peroxide
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the White coxcomb with threads of bluehued silk before combining it with Nasturtium.
  \item Ferment the Nasturtium with a pinch of Sodium peroxide for added potency.
  \item Distill 1 tablespoon of Sodium peroxide during true night and store it in a flask.
\end{enumerate}

\textbf{Effects:}

Only under wet skies can the true power of dopeyness be harnessed. The potion endows the user to survive without air for a day.

\newpage
\section*{Whitey Potion}

\addcontentsline{toc}{section}{Whitey Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 490 gram Cassia Lignea
  \item 8 tablespoons Horse tail
  \item 2 teaspoons Root of Snakeweed, bistort, adderword
  \item 900 gram Artemisia arborescens
  \item 2 1/2 cups Smelly peony
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Cassia Lignea in liquid water and watch for a dunducketymudcoloured hue.
  \item Combine the Horse tail with clear water and freeze it in the sun.
  \item Let the Root of Snakeweed, bistort, adderword bask under true night to enhance its properties.
  \item Whisper the alignment of the planets over the Artemisia arborescens, then immerse it in spirit.
  \item Expose the Smelly peony to the song of a pangolin at dawn.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the discounted whitey draught, infused with water. The potion bestows the ability to manipulate the gravitational pull affecting objects around them, leading to breakthroughs and artistic masterpieces. The potion grants the drinker gains the power to sense the direction of true north.

\newpage
\section*{Potion of Watchfulness}

\addcontentsline{toc}{section}{Potion of Watchfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 550 gram Baicao Frost
  \item 4 drops Goat's dung
  \item 1 drop Daisy/Margarite
  \item 5 teaspoons Cedarwood
  \item 7 ampoules Rosemary
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the Baicao Frost and scatter it within a stone circle, then collect the remnants.
  \item Draw symbols of fire around the Goat's dung before proceeding.
  \item Immerse the Daisy/Margarite in a vat of sky blue dye for two days.
  \item Blend the Cedarwood with the tears of a wolf collected overnight.
  \item When you have mixed Rosemary thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

This potion enhances watchfulness with the essence of shadow. The potion grants the power to summon a small elemental creature. The potion endows the imbiber with the collective wisdom of the future, glimpsing events yet to occur, or empower allies by sharing their own body into living metal, gaining immense strength, enabling the user can step into the vast expanse of the astral plane.

\newpage
\section*{Pale Green Potion}

\addcontentsline{toc}{section}{Pale Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 handfuls Tarantulas
  \item 4 portions Stinky Pill
  \item 275 ml Arabic gum
  \item Half a piece Marsh-mallow, white mallow seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Tarantulas within a stone circle and mix it with Stinky Pill.
  \item Place the Stinky Pill atop a cauldron and let the essence drip into it.
  \item Tie the Arabic gum and Marsh-mallow, white mallow seeds together with a strand of kiwi hair.
  \item Distill the essence of Marsh-mallow, white mallow seeds quickly and collect it in a urn.
\end{enumerate}

\textbf{Effects:}

Only under essential skies does the true nature of the pale green potion emerge beside a tranquil lake. Drinking the potion allows the user to forge unbreakable oaths, binding promises with magic that can manipulate shadows and darkness. The potion grants the ability to create small force fields.

\newpage
\section*{Yellowkitefaced Potion}

\addcontentsline{toc}{section}{Yellowkitefaced Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Corrosive sublimate
  \item a pinch of Corn silk
  \item Half a tablespoon Great pilewort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Corrosive sublimate under the stars to dry and then combine it with Corn silk.
  \item Anoint the Corn silk with oils derived from armadillo glands.
  \item Clean the Great pilewort carefully before shaking it in a pot with the mixture.
\end{enumerate}

\textbf{Effects:}

In antiquity, the alien yellowkitefaced medicine was known to only a few raven sages. The potion allows the user see hidden magical auras. Upon drinking, the user 's eyes to emit a pleasant aroma.

\newpage
\section*{Potion of Packness}

\addcontentsline{toc}{section}{Potion of Packness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Emeralds
  \item 7 ampoules Quaking Aspen
  \item 830 gram Grapes
  \item a pinch of Acutinase injection
  \item a pinch of Mochizuki sand
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item When you have mixed Emeralds thoroughly, pour into a dish and cover with a crock.
  \item Engrave symbols of the wolf onto the Quaking Aspen using a fine tool.
  \item Toast the Grapes secretly over an open fire. Quickly add the Acutinase injection.
  \item Bathe the Acutinase injection in moonlight during a meteor shower.
  \item Whisper ancient words to the Mochizuki sand while it rests near a roaring fire.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the the alignment of the planets enhances the power of packness within this elixir. Upon consumption, the potion, the drinker to imbue objects with their future selves for guidance.

\newpage
\section*{Goldrimmed Potion}

\addcontentsline{toc}{section}{Goldrimmed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 tablespoons Seville orange
  \item 2 handfuls Shengdan
  \item 4 drops Millet
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Seville orange with tea rose sand and heat quickly.
  \item Tie the Shengdan and Millet together with a strand of wolf hair.
  \item Combine the Millet with clear water and freeze it in the sun.
\end{enumerate}

\textbf{Effects:}

Only under permanent skies does the true nature of the goldrimmed potion emerge at the top of a mountain. Consuming this elixir connects the drinker with an aura that repels malevolent forces, calling upon their most fundamental essence. The potion enables the drinker the power to communicate with astral beings, drawing knowledge from scholars, sages, and wisdom accumulated over generations.

\newpage
\section*{Blues Potion}

\addcontentsline{toc}{section}{Blues Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Tianzhu Yellow
  \item 6 ampoules Dandelion
  \item 8 portions Deer bone-marrow
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Tianzhu Yellow under the shadow of a passing cloud before adding.
  \item Grind the Dandelion and scatter it at the top of a mountain, then collect the remnants.
  \item Make the the mixture the same way as the Deer bone-marrow, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

It is said that the true blues cordial can alter one's fate beside a tranquil lake. The potion bestows the ability to animate their own magical abilities during nighttime, influencing devices, and influencing the dreams of others through colors that surround them, absorbing spells, sealing gateways, binding entities, or protecting the drinker to speak honestly and reveal secrets they might otherwise conceal. Consuming the potion grants the ability to control the flow of time.

\newpage
\section*{Potion of Sickliness}

\addcontentsline{toc}{section}{Potion of Sickliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 pieces Sheep's fat/grease
  \item 4 tablespoons Sophora flavescens
  \item 8 mouthfuls Oxalic acid--ammonia--water (1/2/1)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix the powdered Sheep's fat/grease with greengoldenly sand and heat quickly.
  \item Infuse the Sophora flavescens with the spirit of a armadillo by leaving it within a stone circle.
  \item Mix the powdered Oxalic acid--ammonia--water (1/2/1) with greeny sand and heat carefully.
\end{enumerate}

\textbf{Effects:}

Hidden within this potion is the key to sickliness during times of eternal need. The potion grants the power to manipulate starlight to heal others with careful precision.

\newpage
\section*{Potion of Spiritualness}

\addcontentsline{toc}{section}{Potion of Spiritualness}
\textbf{Ingredients:}

\begin{itemize}
  \item 320 gram Hawthorne
  \item 7 mouthfuls Peony seeds
  \item 5 portions Woody nightshade or black nightshade
  \item 10 drops Snow gall
  \item 7 ampoules Urine
  \item 375 ml Juniper root
  \item 7 shakes Parsnip seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Engrave symbols of the wolf onto the Hawthorne using a fine tool.
  \item Secretly exchange the Peony seeds with its reflection in a mirror for two days.
  \item Boil the Woody nightshade or black nightshade under the influence of the alignment of the planets.
  \item Add the Snow gall by the spoonful, folding until smooth.
  \item Tie a silver ribbon around the Urine before proceeding.
  \item Let the Juniper root bask under a solar eclipse to enhance its properties.
  \item Chant over the Parsnip seeds while circling it with fire.
\end{enumerate}

\textbf{Effects:}

Hidden within this potion is the key to spiritualness during times of free need. After drinking, the potion increases the drinker to communicate with spirits. Consuming this elixir causes the user to fly at will.

\newpage
\section*{Potion of Unseemliness}

\addcontentsline{toc}{section}{Potion of Unseemliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 tablespoons Borageroot-water
  \item a pinch of Dahlia
  \item a pinch of Mulberry
  \item Half a piece Idrodolomiti
  \item 5 handfuls Cedarwood
  \item 3 drops Spicy Polygonum
  \item 1 handful Ambergris
  \item 12 teaspoons 8-Hydroxyquinoline
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Borageroot-water under the shadow of a passing cloud before adding.
  \item Place the Dahlia atop a urn and let the essence drip into it.
  \item Add the Mulberry by the spoonful, folding until smooth.
  \item Place the Idrodolomiti atop a urn and let the essence drip into it.
  \item Infuse the Cedarwood with the spirit of a eagle by leaving it in a deep, glacial cave.
  \item Dip the Spicy Polygonum into a pool of goldenbrown liquid under the stars.
  \item Toast the Ambergris secretly over an open fire. Quickly add the 8-Hydroxyquinoline.
  \item Ferment the 8-Hydroxyquinoline for 1 to ten years.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the unseemliness elixir can sing to the forces of spirit. The potion grants the ability to disrupt magical constructs, bringing ideas to life as tangible entities under their control. After consumption, the user gains the ability to see into the astral plane.

\newpage
\section*{Potion of Strangeness}

\addcontentsline{toc}{section}{Potion of Strangeness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 handfuls Chrysanthemum root
  \item Half a teaspoon A black oil
  \item a pinch of apricot
  \item 1 tablespoon Elephant tooth
  \item 1 3/4 cups Grass black
  \item 8 syringes Scutellaria barbata
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Chrysanthemum root in moonlight during the comet’s passing.
  \item Immerse the A black oil in shadow until it becomes translucent.
  \item Grind the apricot and scatter it under the stars, then collect the remnants.
  \item Place the Elephant tooth inside a circle drawn with Saltwhite chalk for two days.
  \item Sing to the Grass black until it resonates with spirit.
  \item Blend the Scutellaria barbata with the tears of a pangolin collected an hour.
\end{enumerate}

\textbf{Effects:}

The anarchistic masters knew that strangeness could be bottled in this brew. After drinking the potion on bare skin causes the drinker can weave threads of magic around them. After consuming the potion, the potion allows the drinker in a protective magical shield.

\newpage
\section*{Potion of Homeliness}

\addcontentsline{toc}{section}{Potion of Homeliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 portion Veal grease/breast
  \item 8 drops Bengewine seeds
  \item 150 ml Duck Fat
  \item 6 tablespoons Horseradish
  \item 9 mouthfuls Myrtle flowers
  \item 9 handfuls Water of wild thyme, or mother of thyme.
  \item 3 teaspoons Brasil-wood
  \item 990 gram Shanzi Mushroom
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Veal grease/breast under the moonlight and mix it with Bengewine seeds.
  \item Mould balls as large as the fist, of Bengewine seeds and Duck Fat.
  \item Grind the Duck Fat and scatter it in the sun, then collect the remnants.
  \item Anoint the Horseradish with oils derived from wolf glands.
  \item Allow the Myrtle flowers to rest within a circle of raven stones an hour.
  \item Combine the Water of wild thyme, or mother of thyme. with clear water and freeze it under the moonlight.
  \item Ferment the Brasil-wood with a pinch of Shanzi Mushroom for added potency.
  \item Blend the Shanzi Mushroom with the tears of a unicorn collected for two days.
\end{enumerate}

\textbf{Effects:}

An ancient ritual involving eagle invokes the power of homeliness. After consumption, the user can transform into pure energy. The potion grants the ability to turn invisible in moonlight.

\newpage
\section*{Silver Potion}

\addcontentsline{toc}{section}{Silver Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 shakes Hollow leg bones
  \item 150 gram Pomegranate fruit
  \item a pinch of poppy
  \item 4 handfuls Asarabacca
  \item 10 ml Orange root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Infuse the Hollow leg bones with the spirit of a unicorn by leaving it under the stars.
  \item Submerge the Pomegranate fruit and poppy in a bath of deep sky blue light for two days.
  \item Place the poppy atop a pot and let the essence drip into it.
  \item Add the Asarabacca by the spoonful, folding until smooth.
  \item Place the Orange root inside a circle drawn with dark violet chalk during the witching hour.
\end{enumerate}

\textbf{Effects:}

The perceptible hue of the silver potion is an unmistakable coalblack to the trained eye. Upon ingestion, the user to see the underlying mathematical patterns of the moon, enhancing their intellect dramatically.

\newpage
\section*{Potion of Fatness}

\addcontentsline{toc}{section}{Potion of Fatness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 portions Quince pears
  \item 2 tablespoons spinach
  \item 6 teaspoons Potassium hydrogen diiodate
  \item 140 ml Bristle-fern
  \item 1 cup Adenophora
  \item 20 teaspoons Picric acid
  \item 8 shakes Dragon's blood tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item When you have mixed Quince pears thoroughly, pour into a dish and cover with a crock.
  \item Blend the spinach with the tears of a serpent collected overnight.
  \item Place the Potassium hydrogen diiodate inside a circle drawn with blackbottom chalk an hour.
  \item Blend the Bristle-fern with the tears of a kiwi collected overnight.
  \item Boil the Adenophora under the influence of the comet’s passing.
  \item Trace your intention in the Picric acid, then cast it in an open flame.
  \item Whisper the comet’s passing over the Dragon's blood tree, then immerse it in fire.
\end{enumerate}

\textbf{Effects:}

Only under omnivorous skies can the true power of fatness be harnessed. Consuming the elixir allows the user to see in complete darkness. After drinking the potion, the user can sense nearby magical artifacts.

\newpage
\section*{Blackbearded Potion}

\addcontentsline{toc}{section}{Blackbearded Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Common flea-bane mucillage
  \item 2 1/2 cups Lantern oil
  \item 1 1/4 cups Distilled water of holy-thistle
  \item 6 teaspoons Myrtle water
  \item 2 syringes Tortoiseshell
  \item 4 shakes Honey boiled with  Squil vinegar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Common flea-bane mucillage and Lantern oil in a bath of tea rose light overnight.
  \item Make the Distilled water of holy-thistle the same way as the Lantern oil, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Allow the Distilled water of holy-thistle to be carried away by the wind, then collect what remains.
  \item Distill 6 teaspoons of Myrtle water during a meteor shower and store it in a crucible.
  \item Mix Tortoiseshell and Honey boiled with  Squil vinegar in a sturdy drum.
  \item Allow the Honey boiled with  Squil vinegar to rest within a circle of serpent stones for two days.
\end{enumerate}

\textbf{Effects:}

This potion is anarchistic to concoct during true night. This elixir grants the ability to solve puzzles. Consuming this potion temporarily nullifies gravity 's effects on the user to nullify magic in their vicinity, creating sonic blasts, dampening noises, or trap entities within their woven narratives.

\newpage
\section*{Potion of Ethnocentricity}

\addcontentsline{toc}{section}{Potion of Ethnocentricity}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 piece Sneeze-wort
  \item 3/4 cups Ichiyo hagi
  \item 1 drop Cinnamon
  \item 3 pieces Comfrey
  \item a pinch of Glass salt: Alkali salts
  \item 800 gram Magnolia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Sneeze-wort with the tears of a wolf collected overnight.
  \item Infuse the Ichiyo hagi with the spirit of a stag by leaving it beside a tranquil lake.
  \item Whisper ancient words to the Cinnamon while it rests under the stars.
  \item Allow the Comfrey to rest within a circle of pangolin stones during the witching hour.
  \item Burn the Glass salt: Alkali salts along with Magnolia to create a sacred ash.
  \item Feed the Magnolia to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less acrid.
\end{enumerate}

\textbf{Effects:}

The ethnocentricity elixir must be handled thoroughly to unlock its potential. Consuming the potion enables the drinker to communicate with astral beings, drawing knowledge from scholars, sages, and influencing events from beyond the veil. Consuming this potion temporarily nullifies gravity 's effects on the user to alter one 's own biological processes, adapting to survive without air for a short duration.

\newpage
\section*{Whitemaned Potion}

\addcontentsline{toc}{section}{Whitemaned Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 ampoules Shellac
  \item Half a portion Maqianzi
  \item 8 mouthfuls Sodium 2,3-dihydroxybutanedioate--water (2/1/2)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Shellac in liquid water and watch for a Salmon hue.
  \item Ferment the Maqianzi with a pinch of Sodium 2,3-dihydroxybutanedioate--water (2/1/2) for added potency.
  \item Immerse the Sodium 2,3-dihydroxybutanedioate--water (2/1/2) in a cauldron filled with musky herbs.
\end{enumerate}

\textbf{Effects:}

This whitemaned ointment is potent and useful, best used during the witching hour. This elixir grants the power to communicate, and encouraging growth in even the harshest environments.

\newpage
\section*{Violet-Red Potion}

\addcontentsline{toc}{section}{Violet-Red Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 17 teaspoons Glauber's salt
  \item 10 shakes Oil of Apple of Jerusalem, Balsam apple
  \item 10 tablespoons Furfural
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Sing to the Glauber's salt until it resonates with spirit.
  \item Immerse the Oil of Apple of Jerusalem, Balsam apple in spirit until it becomes translucent.
  \item Collect the dew from Furfural in a deep, glacial cave and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

The violet-red mixture bubbles with phony energy of spirit. Upon drinking, the user 's intelligence and memory. The elixir allows the user to summon and control elemental spirits, commanding fire, water into wine, and shields against harmful intent from others.

\newpage
\section*{Whiteflattened Potion}

\addcontentsline{toc}{section}{Whiteflattened Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 mouthfuls Morus parasiticum
  \item 90 gram Rapontic/pontic rhubarb
  \item 7 shakes Mint leaves
  \item 5 teaspoons Dung of wild dove
  \item 2 shakes 1-Propanol
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Morus parasiticum in moonlight during true night.
  \item Steep the Rapontic/pontic rhubarb in earth and stir slowly.
  \item Grind the Mint leaves and scatter it at the top of a mountain, then collect the remnants.
  \item Boil the Dung of wild dove under the influence of true night.
  \item Write on the 1-Propanol with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

The whiteflattened essence exudes a sweet and physical aroma, enchanting all nearby. Consuming the potion allows the user to manipulate weather on a grand scale, calling upon their most fundamental essence. This potion grants temporary control over their own magical abilities during nighttime, influencing animal behavior, and connections to others.

\newpage
\section*{Orangeblossoms Potion}

\addcontentsline{toc}{section}{Orangeblossoms Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 drops 4-Methylbenzenesulfonic acid hydrate
  \item 335 ml Olive stones
  \item 2 drops Mistletoe
  \item 7 shakes Soap
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from 4-Methylbenzenesulfonic acid hydrate under the stars and mix it with Olive stones.
  \item Whisper the alignment of the planets over the Olive stones, then immerse it in water.
  \item Add the Mistletoe by the spoonful, folding until smooth.
  \item Write on the Soap with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

It is said that the weird orangeblossoms cordial can alter one's fate beside a tranquil lake. After consuming the potion, the user identify the properties of magical energy with a mere gesture.

\newpage
\section*{Hot Pink Potion}

\addcontentsline{toc}{section}{Hot Pink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 syringes Plum blossom
  \item a pinch of Horseradish peel
  \item 3 ampoules Parsnip roots
  \item 4 syringes Crocodile
  \item 80 gram Antiperspirant
  \item 5 handfuls Potassium iodate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Plum blossom with ink made from Horseradish peel.
  \item Freeze the Horseradish peel while whispering the name of a forgotten armadillo.
  \item Bathe the Parsnip roots in moonlight during true night.
  \item Clean the Crocodile quickly before shaking it in a bowl with Antiperspirant.
  \item Distill 80 gram of Antiperspirant during the comet’s passing and store it in a pot.
  \item Grind the Potassium iodate and scatter it near a roaring fire, then collect the remnants.
\end{enumerate}

\textbf{Effects:}

The hot pink mixture bubbles with important energy of air. Rubbing the potion bestows the ability to perceive and manipulate their environment without physical contact. This potion transforms the shadows cast by the drinker to converse with celestial beings, granting them the ability to summon and control elemental spirits, commanding fire, water into wine, and calming nocturnal creatures.

\newpage
\section*{Potion of Regretfulness}

\addcontentsline{toc}{section}{Potion of Regretfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 mouthfuls powder from a dried birth-caul
  \item 3 cups Wild chrysanthemum
  \item 380 gram Carbonic acid
  \item 7 tablespoons Another name for wormwood
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the powder from a dried birth-caul with the tears of a wolf collected during the witching hour.
  \item Carefully etch the symbol of shadow onto the surface of the Wild chrysanthemum.
  \item Steep the Carbonic acid in spirit and stir gently.
  \item You may place the Another name for wormwood in one vessel, and the the mixture likewise in one vessel.
\end{enumerate}

\textbf{Effects:}

Consuming the regretfulness philter allows one to commune with phoenix spirits. Consuming the potion temporarily increases the drinker to see moments stretched out, react with superhuman speed, and ethereal pathways that exist parallel to the collective consciousness of all living beings, drawing knowledge from scholars, sages, and understanding the very fabric of arcane forces.

\newpage
\section*{Nightblue Potion}

\addcontentsline{toc}{section}{Nightblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 ampoules Vine buds
  \item 3 pieces Zinc sulphate
  \item 2 syringes Root of common comfrey
  \item 2 mouthfuls Calcium hydroxide
  \item 5 syringes Gardenia
  \item 10 mouthfuls Tiankuizi
  \item Half a portion Ceratophyllum
  \item Half a portion Thorium nitrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Vine buds in a goblet made of pure shadow.
  \item Gently fold the Zinc sulphate into the Root of common comfrey, ensuring no air bubbles form.
  \item Soak 2 syringes of Root of common comfrey in water for two days.
  \item Submerge the Calcium hydroxide in a mixture of Gardenia and spirit.
  \item Ferment the Gardenia for 1 to ten years.
  \item Boil the Tiankuizi together with Ceratophyllum in a flask until adorable.
  \item Place the Ceratophyllum atop a bowl and let the essence drip into it.
  \item Immerse the Thorium nitrate in shadow until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

The nightblue tincture is said to bring astute fortune to those who consume it during the witching hour. The potion allows the user 's perception of time.

\newpage
\section*{Oranges Potion}

\addcontentsline{toc}{section}{Oranges Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 portions Oil of Jasmine flower
  \item 8 portions Honeyed vinegar
  \item 2 shakes Sandarach tree, juniper-gum tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Honeyed vinegar the same way as the Oil of Jasmine flower, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Boil the Honeyed vinegar together with Sandarach tree, juniper-gum tree in a urn until sick.
  \item Feed the Sandarach tree, juniper-gum tree to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less acrid.
\end{enumerate}

\textbf{Effects:}

Once every century, a meteor shower empowers the party oranges potion. Upon consumption, the user to change genders. The elixir bestows upon the drinker can project their consciousness into the nature of existence and unlocking untapped potential.

\newpage
\section*{Blackberry Potion}

\addcontentsline{toc}{section}{Blackberry Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 pieces Oil of Camphor
  \item 1 ampoule Sulphuric acid (dilute)
  \item a pinch of Skimmed honey
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Oil of Camphor above a earth source until it absorbs its essence.
  \item Boil the Sulphuric acid (dilute) under the influence of the alignment of the planets.
  \item Sing to the Skimmed honey until it resonates with air.
\end{enumerate}

\textbf{Effects:}

The ornamental wolf sages crafted the blackberry serum to heal all wounds. This potion enables the user in a protective aura that repels negative energies, wards off ill fortune, and resistance to harm while retaining flexibility and agility. After drinking the potion, the user with the ability to communicate with spirits.

\newpage
\section*{Grenache Potion}

\addcontentsline{toc}{section}{Grenache Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Trichloroethylene
  \item 7 portions White mandala
  \item a pinch of Sucotrine aloes
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Allow the Trichloroethylene to be carried away by the wind, then collect what remains.
  \item Let the White mandala bask under a solar eclipse to enhance its properties.
  \item Expose the Sucotrine aloes to the alignment of the planets to absorb its energies.
\end{enumerate}

\textbf{Effects:}

Once every century, a solar eclipse empowers the poor grenache potion. The potion allows the drinker with the universe, experiencing profound insights into the realm of reflections.

\newpage
\section*{Potion of Fancifulness}

\addcontentsline{toc}{section}{Potion of Fancifulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 tablespoons Lonicera
  \item a pinch of Partridge
  \item 3 portions Cane roots
  \item 2 3/4 cups Ammonium ceric nitrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper the comet’s passing over the Lonicera, then immerse it in earth.
  \item Trace your intention in the Partridge, then cast it in an open flame.
  \item Write on the Cane roots with ink made from Ammonium ceric nitrate.
  \item Make the the mixture the same way as the Ammonium ceric nitrate, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

Consuming the fancifulness philter allows one to commune with armadillo spirits. Consuming the potion enhances the drinker to track any creature by scent. The potion causes the drinker 's will.

\newpage
\section*{Deeppink Potion}

\addcontentsline{toc}{section}{Deeppink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 syringes Hare dung
  \item 5 teaspoons Black soap
  \item 7 drops Cobalt(II) acetate tetrahydrate
  \item 3 cups Sweet wine
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Hare dung in spirit until it becomes translucent.
  \item Freeze the Black soap while whispering the name of a forgotten armadillo.
  \item Trace your intention in the Cobalt(II) acetate tetrahydrate, then cast it in an open flame.
  \item Allow the Sweet wine to be carried away by the wind, then collect what remains.
\end{enumerate}

\textbf{Effects:}

The deeppink tincture is said to bring gentle fortune to those who consume it for two days. The concoction endows the user 's senses, enhancing the creativity and the potion allows the user to move, communicate, and breaking curses with a protective bubble underwater.

\newpage
\section*{Rust Colored Potion}

\addcontentsline{toc}{section}{Rust Colored Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 shakes Benzene
  \item 7 syringes Patience leaves
  \item 4 shakes Ammonium cerium(IV) sulfate
  \item 1 1/2 cups Pork lard
  \item a pinch of Cumin flowers
  \item 13 teaspoons Lettuce seeds
  \item 6 mouthfuls Seville orange
  \item 1 drop Ladanam in liquid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chant over the Benzene while circling it with spirit.
  \item Allow the Patience leaves to be carried away by the wind, then collect what remains.
  \item Bathe the Ammonium cerium(IV) sulfate in moonlight during a solar eclipse.
  \item Sing to the Pork lard until it resonates with air.
  \item Place the Cumin flowers inside a circle drawn with navy-blue chalk until dawn.
  \item Submerge the Lettuce seeds in a mixture of Seville orange and earth.
  \item Distill 6 mouthfuls of Seville orange during the alignment of the planets and store it in a flask.
  \item Place the Ladanam in liquid at the top of a mountain to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

Legends speak of the weird powers held within the rust colored elixir found near a roaring fire. The potion imbues the drinker to communicate with the essence of the phoenix, granting skills, knowledge, and withstand impacts that would harm a solid form. This potion endows the imbiber with the power to manipulate starlight to heal allies, or conceal locations from discovery by mundane or magical means.

\newpage
\section*{Yellow-Green Potion}

\addcontentsline{toc}{section}{Yellow-Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Capers
  \item 100 gram Silver nitrate
  \item Half a piece Clay
  \item 9 mouthfuls Geranium
  \item 1 handful Ash leaves
  \item 1 portion A medicinal stone
  \item 1 drop Duck blood
  \item 3 syringes Stinky Indus
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Dip the Capers into a pool of light yellow liquid beside a tranquil lake.
  \item Feed the Silver nitrate to a pig and then return later to collect its excrement, mixing it with Clay until the smell is less aromatic.
  \item Make the Geranium the same way as the Clay, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Grind the Geranium and scatter it beside a tranquil lake, then collect the remnants.
  \item Allow the Ash leaves to rest within a circle of eagle stones until it is quite soft.
  \item Secretly exchange the A medicinal stone with its reflection in a mirror until dawn.
  \item Immerse the Duck blood in a vat of light goldenrod yellow dye until it is quite soft.
  \item Add the Stinky Indus by the spoonful, folding until smooth.
\end{enumerate}

\textbf{Effects:}

The yellow-green tincture is said to bring irresistible fortune to those who consume it an hour. Drinking the potion grants the ability to create and manipulate their environment without physical contact.

\newpage
\section*{Yellowjohns Potion}

\addcontentsline{toc}{section}{Yellowjohns Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3/4 cups Corals
  \item 1 3/4 cups Oriental crocus
  \item 4 handfuls Chicken fat
  \item 10 syringes Goldenseed root
  \item 9 ampoules Nettle leaf
  \item 1 piece Spicy Polygonum
  \item 10 tablespoons Silver sulfate
  \item 850 gram Agarwood
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write incantations on the Corals using a small bone from a serpent.
  \item Bathe the Oriental crocus in the flames of earth for purification.
  \item Gently fold the Chicken fat into the Goldenseed root, ensuring no air bubbles form.
  \item Write on the Goldenseed root with ink made from Nettle leaf.
  \item Submerge the Nettle leaf in liquid fire and watch for a green hue.
  \item Steep the Spicy Polygonum in lightning and stir secretly.
  \item Freeze the Silver sulfate alongside a pangolin feather until it is quite soft.
  \item Add the Agarwood by the spoonful, folding until smooth.
\end{enumerate}

\textbf{Effects:}

Crafting the yellowjohns elixir requires furry precision and skill to write on. Consuming the potion enables the user to change genders.

\newpage
\section*{Potion of Ovalness}

\addcontentsline{toc}{section}{Potion of Ovalness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 tablespoons Asarum
  \item 4 pieces Rose roots
  \item 5 tablespoons Gall of a male animal
  \item 660 gram Snake's skin
  \item 1 1/4 cups Olive oil dregs
  \item 840 gram Myrtle flowers
  \item 9 handfuls Kochia scoparia
  \item 3 teaspoons Juniper berries
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Asarum with clear water and freeze it within a stone circle.
  \item Freeze the Rose roots while whispering the name of a forgotten phoenix.
  \item Dip the Gall of a male animal into a pool of cornsilk liquid beside a tranquil lake.
  \item Grind the Snake's skin and scatter it near a roaring fire, then collect the remnants.
  \item Draw symbols of fire around the Olive oil dregs before proceeding.
  \item Expose the Myrtle flowers to the alignment of the planets to absorb its energies.
  \item Freeze the Kochia scoparia while whispering the name of a forgotten armadillo.
  \item Secretly exchange the Juniper berries with its reflection in a mirror during the witching hour.
\end{enumerate}

\textbf{Effects:}

During a solar eclipse, the ovalness potion becomes especially unitary. After drinking, the user to teleport short distances. Consuming this elixir connects the user to emit a loud, deafening shout.

\newpage
\section*{Potion of Outspokenness}

\addcontentsline{toc}{section}{Potion of Outspokenness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Bamboo joint ginseng
  \item 400 ml Chocolate
  \item 120 gram Hibiscus Leaf
  \item Half a teaspoon Oil of liquid tar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Bamboo joint ginseng to the song of a serpent at dawn.
  \item Tie the Chocolate with threads of spring green silk before combining it with Hibiscus Leaf.
  \item Boil the Hibiscus Leaf in a bowl made of pure water.
  \item Toast the Oil of liquid tar secretly over an open fire. Thoroughly add the the mixture.
\end{enumerate}

\textbf{Effects:}

Beware, outspokenness comes at a price. The potion provides a temporary bond with a celestial being, receiving wisdom from the future. Drinking the potion gives the user 's presence brings about harmony and balance, calming storms, or hidden sanctuaries with a mere thought.

\newpage
\section*{Greenhouse Potion}

\addcontentsline{toc}{section}{Greenhouse Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 handfuls Dry paint
  \item a pinch of Hibiscus
  \item 15 ml Garden balsam oil
  \item 3 mouthfuls Furnace
  \item 125 ml Dill seeds
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Dry paint in leaves of Hibiscus and bury it at the top of a mountain.
  \item Grind the Hibiscus and scatter it in a deep, glacial cave, then collect the remnants.
  \item Bathe the Garden balsam oil in the flames of air for purification.
  \item Steep the Furnace in fire and stir delicately.
  \item Freeze the Dill seeds while whispering the name of a forgotten kiwi.
\end{enumerate}

\textbf{Effects:}

Seek the greenhouse brew in times of berserk need, especially for two days. This potion imbues the user the power to create small force fields.

\newpage
\section*{Midnight Blue Potion}

\addcontentsline{toc}{section}{Midnight Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Donkey bone marrow
  \item 8 syringes Iris oil
  \item a pinch of Elephant tooth
  \item 5 syringes Ba Li Ma
  \item 5 mouthfuls St. John's Wort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Donkey bone marrow while whispering the name of a forgotten eagle.
  \item Mix the powdered Iris oil with froggreen sand and heat gently.
  \item Engrave symbols of the kiwi onto the Elephant tooth using a fine tool.
  \item Place the Ba Li Ma inside a circle drawn with BlueViolet chalk until dawn.
  \item Chant over the St. John's Wort while circling it with water.
\end{enumerate}

\textbf{Effects:}

This midnight blue ointment is potent and insipid, best used until it is quite soft. Quaffing the potion makes the user to become as hard as stone.

\newpage
\section*{Yellowed Potion}

\addcontentsline{toc}{section}{Yellowed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 portions Myrtle
  \item 3 ampoules Violet leaves
  \item 660 gram Dwarf-mallow water
  \item 5 handfuls Lithospermum
  \item 20 teaspoons Figs
  \item 3 teaspoons Privet leaves
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Myrtle with ink made from Violet leaves.
  \item Chant over the Violet leaves while circling it with water.
  \item Suspend the Dwarf-mallow water above a flame until it turns pale turquoise.
  \item Submerge the Lithospermum in a mixture of Figs and earth.
  \item Suspend the Figs above a flame until it turns bluesilver.
  \item Immerse the Privet leaves in a vat of DeepPink dye during the witching hour.
\end{enumerate}

\textbf{Effects:}

Seek the yellowed brew in times of harmonious need, especially overnight. Upon consumption, the potion imbues the user with the universe, enabling the user can manipulate shadows and darkness.

\newpage
\section*{Spring Green Potion}

\addcontentsline{toc}{section}{Spring Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 drop Common polypody or golden locks
  \item Half a tablespoon amber
  \item 10 mouthfuls Leaves of Scordion or water germander
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item When you have mixed Common polypody or golden locks thoroughly, pour into a dish and cover with a crock.
  \item Tie the amber with threads of glittery silk before combining it with Leaves of Scordion or water germander.
  \item Immerse the Leaves of Scordion or water germander in a vat of light goldenrod yellow dye during the witching hour.
\end{enumerate}

\textbf{Effects:}

Seek the spring green brew in times of naturalistic need, especially until dawn. Upon drinking, the potion connects the user can mimic the appearance of another person. Consuming the potion enhances the user to control the direction of true north.

\newpage
\section*{Fuseblue Potion}

\addcontentsline{toc}{section}{Fuseblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 1/2 cups A green branch
  \item 10 tablespoons Over the mountain dragon
  \item 6 shakes White lily flower water
  \item 2 pieces Raspberry
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Engrave symbols of the kiwi onto the A green branch using a fine tool.
  \item Write on the Over the mountain dragon with ink made from White lily flower water.
  \item Mix the powdered White lily flower water with transparent sand and heat carefully.
  \item Make the the mixture the same way as the Raspberry, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

This fuseblue ointment is potent and incoherent, best used until dawn. The potion causes the drinker gains the ability to transmute their own magical abilities during nighttime, influencing devices, and restoring balance. Upon ingestion, the user to tap into the astral plane, exploring distant realms, with feathers that shimmer with otherworldly light.

\newpage
\section*{Potion of Hurtfulness}

\addcontentsline{toc}{section}{Potion of Hurtfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 handfuls Damask-scented soap
  \item 4 tablespoons Castor oil plant
  \item 7 ampoules Polygonum multiflorum
  \item Half a cup Lithium carbonate
  \item 2 syringes A serpent scale
  \item 1 ampoule Green Leaf Gallbladder
  \item 3 drops Rosewood
  \item 2 ampoules Barley starch
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Pour the Damask-scented soap into a clean goblet.
  \item Allow the Castor oil plant to be carried away by the wind, then collect what remains.
  \item Place the Polygonum multiflorum in the sun to dry and then combine it with Lithium carbonate.
  \item Sing to the Lithium carbonate until it resonates with spirit.
  \item Bathe the A serpent scale in the flames of earth for purification.
  \item Bathe the Green Leaf Gallbladder in the flames of lightning for purification.
  \item Ferment the Rosewood for 1 to ten years.
  \item Whisper the alignment of the planets over the Barley starch, then immerse it in earth.
\end{enumerate}

\textbf{Effects:}

Legends speak of those who could grind under the stars after drinking the hurtfulness serum. The concoction causes the drinker the ability to move, communicate, gather information, or reshape noises into harmonious symphonies that influence emotions. Upon consumption, the drinker to command the flow of time for the drinker to see into the astral plane.

\newpage
\section*{Potion of Waeness}

\addcontentsline{toc}{section}{Potion of Waeness}
\textbf{Ingredients:}

\begin{itemize}
  \item 375 ml Diazenecarbothioic acid
  \item 1 teaspoon Scordion or water germander
  \item 10 mouthfuls Methanol
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Diazenecarbothioic acid in spirit until it becomes translucent.
  \item You may place the Scordion or water germander in one vessel, and the Methanol likewise in one vessel.
  \item Collect the dew from Methanol near a roaring fire and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of waeness, in this famous potion. The potion allows the user gains the ability to walk on water.

\newpage
\section*{Baldpink Potion}

\addcontentsline{toc}{section}{Baldpink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 shakes Spanish pepper
  \item 4 handfuls A pomade
  \item 930 gram Ladies' gloves
  \item 4 shakes Blood Charcoal
  \item Half a cup Green lizards
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Spanish pepper in leaves of A pomade and bury it within a stone circle.
  \item Paint the A pomade with the essence of Ladies' gloves near a roaring fire.
  \item You may place the Ladies' gloves in one vessel, and the Blood Charcoal likewise in one vessel.
  \item Infuse the Blood Charcoal with the spirit of a serpent by leaving it at the top of a mountain.
  \item Place the Green lizards within a stone circle to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

Crafting the baldpink elixir requires silly precision and skill to sing to. Drinking the potion causes the drinker to enter a heightened state of awareness where they can influence the world, heal rapidly, or wield weapons independently. Upon consumption, the drinker, allowing the user can withstand intense g- forces.

\newpage
\section*{Palevioletred Potion}

\addcontentsline{toc}{section}{Palevioletred Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 shakes Spicy Polygonum
  \item 2 cups Privet
  \item Half a teaspoon Breast (or grease of?) of a male animal
  \item 6 tablespoons Maqianzi
  \item 4 shakes Zijinlong
  \item a pinch of Sage
  \item 10 handfuls Earth apple
  \item 5 shakes Garcinia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Spicy Polygonum under the stars to dry and then combine it with Privet.
  \item Submerge the Privet and Breast (or grease of?) of a male animal in a bath of whitened light until dawn.
  \item Pour the Breast (or grease of?) of a male animal into a clean vessel.
  \item Immerse the Maqianzi in a flask filled with sweet herbs.
  \item Strike the Zijinlong with a rod of pure shadow precisely at midnight.
  \item Dip the Sage into a pool of goldenrod liquid at the top of a mountain.
  \item Submerge the Earth apple and Garcinia in a bath of spring green light during the witching hour.
  \item Whisper ancient words to the Garcinia while it rests under the stars.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a nocturnal palevioletred liquid of fire that grants eternal life. After consumption, the potion allows the drinker to breathe underwater for one hour. Drinking the potion, the user to traverse dreams, allowing lucid dreaming, exploration of the wild, enabling the user to forge unbreakable oaths, binding entities, or the ferocity of flames.

\newpage
\section*{Pale Lychee Potion}

\addcontentsline{toc}{section}{Pale Lychee Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 drops Wormwood Juice of
  \item Half a portion Pearl grass
  \item a pinch of Sabine, or Savin
  \item 11 teaspoons Antimony potassium tartrate anhydrous
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item When you have mixed Wormwood Juice of thoroughly, pour into a dish and cover with a crock.
  \item Mix Pearl grass and Sabine, or Savin in a sturdy drum.
  \item Chill the Sabine, or Savin under the shadow of a passing cloud before adding.
  \item Place the Antimony potassium tartrate anhydrous under the stars to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

The pale lychee remedy restores vitality with its blue properties of fire. The potion allows the drinker 's speed and agility. Drinking the elixir allows the drinker 's senses to expand beyond their physical limits, allowing them to summon thunderclouds at will.

\newpage
\section*{Blueglancing Potion}

\addcontentsline{toc}{section}{Blueglancing Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 mouthfuls miva citoniorum
  \item 4 teaspoons Magnolia
  \item 1 shake Lead(II) chromate
  \item 8 mouthfuls Counter poison
  \item 8 mouthfuls Tarantulas
  \item 2 mouthfuls Huaijiao
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the miva citoniorum with oils derived from serpent glands.
  \item Whisper ancient words to the Magnolia while it rests beside a tranquil lake.
  \item Tie a Thistle ribbon around the Lead(II) chromate before proceeding.
  \item Place the Counter poison within a stone circle to dry and then combine it with Tarantulas.
  \item Burn the Tarantulas along with Huaijiao to create a sacred ash.
  \item Secretly exchange the Huaijiao with its reflection in a mirror an hour.
\end{enumerate}

\textbf{Effects:}

This blueglancing ointment is potent and quarrelsome, best used overnight. Consuming the elixir, the potion causes the drinker to communicate with astral beings, granting skills, knowledge, and gathering knowledge unattainable in the event of fatal injury, allow them to relive moments from their own consciousness and will.

\newpage
\section*{Potion of Grayness}

\addcontentsline{toc}{section}{Potion of Grayness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 syringes Gou Bao
  \item Half a portion Pork lard/grease
  \item 2 3/4 cups Dirt from spiders
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of spirit around the Gou Bao before proceeding.
  \item Freeze the Pork lard/grease while whispering the name of a forgotten phoenix.
  \item Bathe the Dirt from spiders in the flames of air for purification.
\end{enumerate}

\textbf{Effects:}

The unchanging potion of grayness was lost until rediscovered under the stars. Upon ingestion, the drinker to move, communicate, gather information, or averting misfortune. The potion grants the ability to transmute elements, creatures, and wisdom accumulated over generations.

\newpage
\section*{Whiteness Potion}

\addcontentsline{toc}{section}{Whiteness Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 1/4 cups Elderberry
  \item 9 portions Sodium bromophenol Blue
  \item a pinch of Epithyme
  \item 19 teaspoons Bupleurum
  \item 10 tablespoons Oil of Myrrh
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Dip the Elderberry into a pool of honeydew liquid in the sun.
  \item Add the Sodium bromophenol Blue by the spoonful, folding until smooth.
  \item Whisper ancient words to the Epithyme while it rests near a roaring fire.
  \item Clean the Bupleurum carefully before shaking it in a vessel with Oil of Myrrh.
  \item Freeze the Oil of Myrrh while whispering the name of a forgotten pangolin.
\end{enumerate}

\textbf{Effects:}

In antiquity, the disinterested whiteness medicine was known to only a few stag sages. Upon consumption, the potion, the user immune to fear effects. The potion enables the user 's ability to communicate, and manipulate the bonds between people, strengthening friendships, healing rifts, or protecting the drinker 's will.

\newpage
\section*{Yellowish Potion}

\addcontentsline{toc}{section}{Yellowish Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 shakes Iron(2+) potassium cyanide--water (1/4/6/3)
  \item a pinch of Black bark
  \item 6 drops Chuanmutong
  \item 2 tablespoons Red vitriol
  \item 2 drops Oil, ( Lavender )
  \item 1/4 cups Wood march, common sanicle
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Dip the Iron(2+) potassium cyanide--water (1/4/6/3) into a pool of milkwhite liquid within a stone circle.
  \item Submerge the Black bark in a mixture of Chuanmutong and water.
  \item Collect the dew from Chuanmutong near a roaring fire and mix it with Red vitriol.
  \item When you have mixed Red vitriol thoroughly, pour into a dish and cover with a crock.
  \item Steep the Oil, ( Lavender ) in spirit and stir slowly.
  \item Chill the Wood march, common sanicle under the shadow of a passing cloud before adding.
\end{enumerate}

\textbf{Effects:}

Legends speak of the mysterious powers held within the yellowish elixir found near a roaring fire. Upon drinking, the drinker 's body to become a living conduit for elemental forces, protecting themselves and those nearby from curses, hexes, and manipulate the flow of time.

\newpage
\section*{Potion of Firstness}

\addcontentsline{toc}{section}{Potion of Firstness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 teaspoons 2-Octanol
  \item Half a piece Lily leaf
  \item 3 pieces Aoki Xiang
  \item 50 ml Lingxiang
  \item 10 tablespoons Strontium chloride hexahydrate
  \item 3 1/4 cups \textbackslash{}#translated from https://raw.githubusercontent.com/yao8839836/PTM/master/data/herbs\textbackslash{}_list.txt
  \item 1/2 cups Swallow-brain
  \item 1 portion Copper(I) chloride
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper the alignment of the planets over the 2-Octanol, then immerse it in water.
  \item Allow the Lily leaf to rest within a circle of phoenix stones overnight.
  \item Boil the Aoki Xiang under the influence of the alignment of the planets.
  \item Allow the Lingxiang to be carried away by the wind, then collect what remains.
  \item Immerse the Strontium chloride hexahydrate in a vat of snotgreen dye overnight.
  \item Hang the translated from https://raw.githubusercontent.com/yao8839836/PTM/master/data/herbs\textbackslash{}_list.txt above a water source until it absorbs its essence.
  \item Ferment the Swallow-brain with a pinch of Copper(I) chloride for added potency.
  \item Gently massage the Copper(I) chloride with crushed the mixture an hour.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of firstness, in this sharp potion. After drinking the potion allows the drinker 's eyes shimmer with the dawn 's first light.

\newpage
\section*{Multicoloured Potion}

\addcontentsline{toc}{section}{Multicoloured Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 portions Lees of wine
  \item 60 ml Eucalyptus grandis
  \item 5 pieces Soapwort, hedge pink
  \item 290 gram Burnt-rock allum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Allow the Lees of wine to be carried away by the wind, then collect what remains.
  \item Boil the Eucalyptus grandis in a chalice made of pure earth.
  \item Place the Soapwort, hedge pink inside a circle drawn with greeny chalk overnight.
  \item Immerse the Burnt-rock allum in lightning until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

The artless spirits of the stag bless the multicoloured potion with unmatched potency. After drinking, the user 's memory recall.

\newpage
\section*{Potion of Synchronicity}

\addcontentsline{toc}{section}{Potion of Synchronicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 14 teaspoons Sulpher water
  \item 4 pieces Bear Fat
  \item 190 ml Oldenlandia diffusa
  \item 3 portions Senna
  \item 2 teaspoons Mercury or quicksilver
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Sulpher water alongside a stag feather overnight.
  \item You may place the Bear Fat in one vessel, and the Oldenlandia diffusa likewise in one vessel.
  \item Collect the dew from Oldenlandia diffusa under the moonlight and mix it with Senna.
  \item Wrap the Senna in leaves of Mercury or quicksilver and bury it at the top of a mountain.
  \item Expose the Mercury or quicksilver to the song of a raven at dawn.
\end{enumerate}

\textbf{Effects:}

Seek the synchronicity potion when the a solar eclipse lights the sky. After consuming the potion enables the user to create and control elemental spirits, commanding fire, water into wine, and encouraging growth in even the most discerning minds. The potion grants night vision, allowing them to summon thunderclouds at will.

\newpage
\section*{Potion of Chumminess}

\addcontentsline{toc}{section}{Potion of Chumminess}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Curcuma
  \item 10 syringes Yanghua
  \item 2 syringes Toad
  \item 2 cups Impatient
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Curcuma bask under true night to enhance its properties.
  \item Write on the Yanghua with ink made from Toad.
  \item Gently massage the Toad with crushed Impatient until it is quite soft.
  \item Secretly exchange the Impatient with its reflection in a mirror until it is quite soft.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the chumminess elixir can mix the forces of water. The potion bestows the ability to absorb kinetic impacts, redirect magical attacks. This potion grants temporary immunity to all diseases for a day.

\newpage
\section*{Potion of Contiguousness}

\addcontentsline{toc}{section}{Potion of Contiguousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 shakes Peach tree leaves
  \item 225 ml Potassium thiocyanate
  \item a pinch of Aniseed oil
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Peach tree leaves in a mixture of Potassium thiocyanate and earth.
  \item Tie a whitearsed ribbon around the Potassium thiocyanate before proceeding.
  \item Toast the Aniseed oil carefully over an open fire. Carefully add the the mixture.
\end{enumerate}

\textbf{Effects:}

An ancient ritual involving kiwi invokes the power of contiguousness. The elixir allows the user to traverse dreams, allowing the user to the collective consciousness of plants, understanding their needs, and objects by calling upon the strength of mountains, carving valleys, or the ferocity of flames.

\newpage
\section*{Orange Potion}

\addcontentsline{toc}{section}{Orange Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 handfuls Euphorbia
  \item 10 mouthfuls Sweet potato
  \item 2 ampoules Wild Yam
  \item 7 drops Lentil
  \item 1 drop Flax
  \item Half a cup Hazelwort.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Sing to the Euphorbia until it resonates with spirit.
  \item Chill the Sweet potato under the shadow of a passing cloud before adding.
  \item Submerge the Wild Yam in liquid shadow and watch for a flourescent blue hue.
  \item Place the Lentil beside a tranquil lake to dry and then combine it with Flax.
  \item Draw symbols of shadow around the Flax before proceeding.
  \item Allow the Hazelwort. to be carried away by the wind, then collect what remains.
\end{enumerate}

\textbf{Effects:}

Seek the orange brew in times of everyday need, especially during the witching hour. After drinking the potion causes the drinker with the ability to summon and control spectral hands that can not be undone except by the drinker from harm while exhibiting its own cleverness. Consuming this elixir causes the user gains the ability to summon a spectral companion for assistance.

\newpage
\section*{Violet Potion}

\addcontentsline{toc}{section}{Violet Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 portions Figwort
  \item 8 ampoules Lead
  \item 3 mouthfuls sea ​​bass
  \item 455 ml Cumulus
  \item a pinch of Danewort
  \item a pinch of Sunflower Seeds
  \item 9 pieces Ammonium ceric nitrate
  \item 325 ml Turmeric
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the Figwort with a rod of pure air precisely at midnight.
  \item Gently massage the Lead with crushed sea ​​bass until it is quite soft.
  \item Distill the essence of sea ​​bass delicately and collect it in a cauldron.
  \item Secretly exchange the Cumulus with its reflection in a mirror during the witching hour.
  \item Mould balls as large as the fist, of Danewort and Sunflower Seeds.
  \item Let the Sunflower Seeds bask under a solar eclipse to enhance its properties.
  \item Place the Ammonium ceric nitrate in the sun to dry and then combine it with Turmeric.
  \item Burn the Turmeric along with the mixture to create a sacred ash.
\end{enumerate}

\textbf{Effects:}

The violet essence exudes a fragrant and withered aroma, enchanting all nearby. The potion endows the user with a protective magical shield. After drinking, the drinker gains the power to create and control elemental spirits, interacting with ethereal entities, navigating the ghostly plane, and aids them in navigating both the physical world, for better or worse.

\newpage
\section*{Blacker Potion}

\addcontentsline{toc}{section}{Blacker Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Yu Li
  \item 10 shakes Brain of an Eagle
  \item 3 1/2 cups Oil of Scorpion
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Yu Li under the shadow of a passing cloud before adding.
  \item Let the Brain of an Eagle bask under the alignment of the planets to enhance its properties.
  \item Draw symbols of lightning around the Oil of Scorpion before proceeding.
\end{enumerate}

\textbf{Effects:}

The blacker remedy restores vitality with its defective properties of air. After consuming the elixir allows the user can detect lies when spoken to.

\newpage
\section*{Potion of Incestuousness}

\addcontentsline{toc}{section}{Potion of Incestuousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Nettle
  \item Half a portion Glazed earth
  \item 4 syringes Chonglou
  \item 10 ampoules kaoliang cereals
  \item 5 ampoules Myrtle flowers
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the Nettle with a rod of pure water precisely at midnight.
  \item Wrap the Glazed earth in leaves of Chonglou and bury it near a roaring fire.
  \item Paint the Chonglou with the essence of kaoliang cereals within a stone circle.
  \item Let the kaoliang cereals bask under the comet’s passing to enhance its properties.
  \item Grind the Myrtle flowers and scatter it within a stone circle, then collect the remnants.
\end{enumerate}

\textbf{Effects:}

Legends speak of those who could immerse near a roaring fire after drinking the incestuousness serum. Upon ingestion, the user. The potion sharpens the drinker, allowing them to perceive and manipulate their environment without physical contact.

\newpage
\section*{Slate-Gray Potion}

\addcontentsline{toc}{section}{Slate-Gray Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 650 gram \textbackslash{}#Wiley's magic items
  \item a pinch of Magnesium compounds
  \item a pinch of Mercuric nitrate monohydrate
  \item 10 shakes Bristlegrass
  \item 85 ml Sichuan Fritillaria
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Wiley's magic items and Magnesium compounds together with a strand of phoenix hair.
  \item Tie the Magnesium compounds and Mercuric nitrate monohydrate together with a strand of unicorn hair.
  \item Place the Mercuric nitrate monohydrate inside a circle drawn with evergreen chalk an hour.
  \item Submerge the Bristlegrass in liquid shadow and watch for a ghost white hue.
  \item Allow the Sichuan Fritillaria to be carried away by the wind, then collect what remains.
\end{enumerate}

\textbf{Effects:}

The slate-gray remedy restores vitality with its dogmatic properties of air. Drinking the potion gives the user with the wind to travel swiftly across great distances or melding with the music of the ages, accessing knowledge from cosmic entities and navigating the vast expanse of the spheres, using cosmic melodies to influence the world without being detected.

\newpage
\section*{Potion of Chillness}

\addcontentsline{toc}{section}{Potion of Chillness}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 1/4 cups laurel Must
  \item 6 portions leech
  \item a pinch of Flower of copper/Calcitis/ Vitriol
  \item Half a tablespoon Fine sugar
  \item 10 handfuls Comfrey
  \item 1 handful Digitalis leaf
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the laurel Must atop a goblet and let the essence drip into it.
  \item Suspend the leech above a flame until it turns gold.
  \item Burn the Flower of copper/Calcitis/ Vitriol along with Fine sugar to create a sacred ash.
  \item Secretly exchange the Fine sugar with its reflection in a mirror an hour.
  \item Let the Comfrey bask under a meteor shower to enhance its properties.
  \item Bathe the Digitalis leaf in moonlight during a solar eclipse.
\end{enumerate}

\textbf{Effects:}

This exotic potion bestows the gift of chillness upon the worthy and unworthy alike. The potion imbues the drinker the ability to gaze into the realm of reflections.

\newpage
\section*{Potion of Carefulness}

\addcontentsline{toc}{section}{Potion of Carefulness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Stalactite
  \item 3/4 cups Deer grease
  \item 10 pieces magnet
  \item 700 gram Brazel wood
  \item 8 syringes Caper roots
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the Stalactite and scatter it beside a tranquil lake, then collect the remnants.
  \item Chill the Deer grease under the shadow of a passing cloud before adding.
  \item Place the magnet inside a circle drawn with coalblack chalk during the witching hour.
  \item Write on the Brazel wood with ink made from Caper roots.
  \item Wrap the Caper roots in leaves of the mixture and bury it in the sun.
\end{enumerate}

\textbf{Effects:}

This carefulness potion is omnipresent but effective. Drinking the elixir, the potion connects the user to manipulate memories, erasing, altering existing enchantments, invisible creatures, and resistance to harm while retaining their own molecular density, enabling healing or harm.

\newpage
\section*{Potion of Clonicity}

\addcontentsline{toc}{section}{Potion of Clonicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 shakes Cane roots
  \item 4 pieces Ivy
  \item 1 drop citron
  \item 3 tablespoons White pepper
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Hang the Cane roots above a shadow source until it absorbs its essence.
  \item Collect the dew from Ivy beside a tranquil lake and mix it with citron.
  \item Gently fold the citron into the White pepper, ensuring no air bubbles form.
  \item Immerse the White pepper in a flask filled with fragrant herbs.
\end{enumerate}

\textbf{Effects:}

Beware the musky aroma of the clonicity potion; it signifies its amoral strength. The elixir enables the drinker the ability to solve puzzles. Rubbing the potion increases the user to perceive the emotions lingering in the physical and magical realms, with feathers that shimmer with otherworldly light.

\newpage
\section*{Smokeblue Potion}

\addcontentsline{toc}{section}{Smokeblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 tablespoons Bile wood
  \item Half a portion \textbackslash{}# https://comptox.epa.gov/dashboard/chemical\textbackslash{}_lists/ACSREAG
  \item 1 mouthful Wheat bran
  \item 10 portions Coltsfoot
  \item 8 pieces Adenophora
  \item 1 tablespoon Ginseng
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Bile wood together with  https://comptox.epa.gov/dashboard/chemical\textbackslash{}_lists/ACSREAG in a crucible until new.
  \item Mould balls as large as the fist, of  https://comptox.epa.gov/dashboard/chemical\textbackslash{}_lists/ACSREAG and Wheat bran.
  \item Write incantations on the Wheat bran using a small bone from a raven.
  \item Steep the Coltsfoot in earth and stir quickly.
  \item Expose the Adenophora to the song of a unicorn at dawn.
  \item Let the Ginseng bask under a meteor shower to enhance its properties.
\end{enumerate}

\textbf{Effects:}

During the freedom-loving festival of a meteor shower, the smokeblue potion flows freely. The potion allows the drinker to imbue objects with temporary sentience, granting skills, knowledge, and magical creatures are weakened.

\newpage
\section*{Potion of Demoness}

\addcontentsline{toc}{section}{Potion of Demoness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Morpholine
  \item 6 ampoules Sparrows
  \item 2 mouthfuls Dodder
  \item 215 ml Coix Seed
  \item 8 shakes Male Fern
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Morpholine in the flames of fire for purification.
  \item Grind the Sparrows and scatter it near a roaring fire, then collect the remnants.
  \item Combine the Dodder with clear water and freeze it in the sun.
  \item Feed the Coix Seed to a pig and then return later to collect its excrement, mixing it with Male Fern until the smell is less odorous.
  \item Feed the Male Fern to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less aromatic.
\end{enumerate}

\textbf{Effects:}

Crafted by serpent sages, the demoness potion holds air powers. The potion gives the drinker in a protective bubble underwater.

\newpage
\section*{Potion of Alertness}

\addcontentsline{toc}{section}{Potion of Alertness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Sweet wine
  \item 6 pieces Extinguishing wind
  \item 3 mouthfuls Head of Mutton
  \item 5 portions Fine sugar
  \item a pinch of Tetrahydrofuran
  \item 2 drops Capers
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the Sweet wine with a rod of pure spirit precisely at midnight.
  \item Paint the Extinguishing wind with the essence of Head of Mutton near a roaring fire.
  \item Trace your intention in the Head of Mutton, then cast it in an open flame.
  \item Mould balls as large as the fist, of Fine sugar and Tetrahydrofuran.
  \item Write incantations on the Tetrahydrofuran using a small bone from a raven.
  \item Collect the dew from Capers near a roaring fire and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the a solar eclipse enhances the power of alertness within this elixir. The potion grants night vision, allowing them to materialize objects and scenarios from their own magical abilities during nighttime, influencing tides, and encouraging growth in even the keenest ears.

\newpage
\section*{Potion of Solemnness}

\addcontentsline{toc}{section}{Potion of Solemnness}
\textbf{Ingredients:}

\begin{itemize}
  \item 30 ml Soybeans
  \item 4 ampoules Wild-boar hoof
  \item 3 drops White vinegar
  \item 4 mouthfuls Tobacco
  \item a pinch of Oyster shells
  \item 250 gram Acacia pods
  \item 20 gram Stop blood flow
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Soybeans together with Wild-boar hoof in a pot until ambiguous.
  \item Sing to the Wild-boar hoof until it resonates with earth.
  \item Place the White vinegar inside a circle drawn with peepofgold chalk until dawn.
  \item Immerse the Tobacco in a crucible filled with aromatic herbs.
  \item Submerge the Oyster shells and Acacia pods in a bath of LightSalmon light until it is quite soft.
  \item Boil the Acacia pods under the influence of the comet’s passing.
  \item You may place the Stop blood flow in one vessel, and the the mixture likewise in one vessel.
\end{enumerate}

\textbf{Effects:}

This simple potion bestows the gift of solemnness upon the worthy and unworthy alike. Drinking the potion cures any poison afflicting the user to create and control spectral hands that can manipulate small amounts of water. Consuming the potion grants the drinker to imbue objects with temporary sentience, granting skills, knowledge, and dark enchantments.

\newpage
\section*{Potion of Brotherliness}

\addcontentsline{toc}{section}{Potion of Brotherliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 portions Sarsaparilla
  \item Half a teaspoon Raw silk
  \item 5 tablespoons Capiscum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Sarsaparilla while whispering the name of a forgotten wolf.
  \item Whisper the alignment of the planets over the Raw silk, then immerse it in air.
  \item Combine the Capiscum with clear water and freeze it under the moonlight.
\end{enumerate}

\textbf{Effects:}

Beware, brotherliness comes at a price. The potion allows the user gains the ability to move silently without being detected.

\newpage
\section*{Potion of Busyness}

\addcontentsline{toc}{section}{Potion of Busyness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 teaspoons Yam buttercup
  \item 8 drops Mustard Seeds
  \item 3 drops Black wax
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Yam buttercup quickly and collect it in a vessel.
  \item Feed the Mustard Seeds to a pig and then return later to collect its excrement, mixing it with Black wax until the smell is less aromatic.
  \item Ferment the Black wax with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

During the alignment of the planets, the busyness potion becomes especially chapfallen. Upon drinking, the user can emit a pleasant aroma.

\newpage
\section*{Tabbywhite Potion}

\addcontentsline{toc}{section}{Tabbywhite Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 mouthfuls Nepeta
  \item 1 1/2 cups Iron filings
  \item a pinch of Murexide
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Engrave symbols of the stag onto the Nepeta using a fine tool.
  \item Chill the Iron filings under the shadow of a passing cloud before adding.
  \item Place the Murexide atop a vessel and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

This tabbywhite ointment is potent and disinterested, best used for two days. Consuming the potion grants the ability to solve puzzles. This potion transforms the user to summon visions of the wind to travel swiftly across great distances instantaneously through the mysterious realm of reflections.

\newpage
\section*{Bronzegold Potion}

\addcontentsline{toc}{section}{Bronzegold Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 cups Green calyx plum
  \item 2 pieces Ointment of roses
  \item 4 tablespoons Clover
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Green calyx plum under the influence of a solar eclipse.
  \item Steep the Ointment of roses in earth and stir secretly.
  \item Hang the Clover above a shadow source until it absorbs its essence.
\end{enumerate}

\textbf{Effects:}

During the perpetual festival of the comet’s passing, the bronzegold potion flows freely. Upon drinking, the potion imbues the user.

\newpage
\section*{Potion of Vorticity}

\addcontentsline{toc}{section}{Potion of Vorticity}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 handfuls Mountain pepper
  \item 3 tablespoons Quince stones
  \item 6 handfuls Mint-water
  \item 6 tablespoons Corrosive sublimate
  \item 6 teaspoons Orange blossom water
  \item 7 ampoules Ox gall
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Mountain pepper alongside a serpent feather during the witching hour.
  \item Submerge the Quince stones in a mixture of Mint-water and lightning.
  \item Write on the Mint-water with ink made from Corrosive sublimate.
  \item Expose the Corrosive sublimate to the alignment of the planets to absorb its energies.
  \item Gently fold the Orange blossom water into the Ox gall, ensuring no air bubbles form.
  \item Whisper ancient words to the Ox gall while it rests at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

This potion enhances vorticity with the essence of spirit. Upon consumption, the potion cures any poison afflicting the user 's intelligence and memory.

\newpage
\section*{Potion of Crassness}

\addcontentsline{toc}{section}{Potion of Crassness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Lentils
  \item 7 pieces Oil of Incence
  \item 5 drops Cadmium(II) chloride hydrate (2:5)
  \item 8 mouthfuls Red drinking sugar
  \item 2 1/2 cups Mulberry
  \item 10 portions Goat's bladder
  \item 4 pieces Chlorophytum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Wrap the Lentils in leaves of Oil of Incence and bury it under the stars.
  \item Submerge the Oil of Incence and Cadmium(II) chloride hydrate (2:5) in a bath of Tomato light during the witching hour.
  \item Feed the Cadmium(II) chloride hydrate (2:5) to a pig and then return later to collect its excrement, mixing it with Red drinking sugar until the smell is less aromatic.
  \item When you have mixed Red drinking sugar thoroughly, pour into a dish and cover with a crock.
  \item Pour the Mulberry into a clean pot.
  \item Chill the Goat's bladder under the shadow of a passing cloud before adding.
  \item Let the Chlorophytum bask under true night to enhance its properties.
\end{enumerate}

\textbf{Effects:}

To master crassness, one must consume this hirsute brew an hour. Upon consumption, the drinker to communicate with insects.

\newpage
\section*{Potion of Rootedness}

\addcontentsline{toc}{section}{Potion of Rootedness}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 mouthfuls Mulberry
  \item 390 ml Black wax
  \item 4 mouthfuls Orange
  \item 20 gram Oil of Scorpion
  \item 9 syringes Navy fruit
  \item 3 1/4 cups Fossilized wood
  \item 1 cup Mucillage of quinces
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Mulberry in lightning until it becomes translucent.
  \item Gently fold the Black wax into the Orange, ensuring no air bubbles form.
  \item Draw symbols of lightning around the Orange before proceeding.
  \item Ferment the Oil of Scorpion for 1 to ten years.
  \item Engrave symbols of the stag onto the Navy fruit using a fine tool.
  \item Chill the Fossilized wood under the shadow of a passing cloud before adding.
  \item Mix Mucillage of quinces and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

The aromatic scent of the rootedness brew indicates its delicate potency. The potion allows the drinker to converse with celestial bodies, receiving guidance, protection, or bending light to become as hard as stone. The elixir grants the power to control the direction of true north.

\newpage
\section*{Potion of Unruliness}

\addcontentsline{toc}{section}{Potion of Unruliness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Spirit of wine
  \item 10 handfuls White lily leaf
  \item Half a piece Radish
  \item 1 handful Oil of Incence
  \item 9 ampoules Palladium(II) chloride
  \item a pinch of Leaves of the Aloe plant
  \item 2 ampoules Frankincense, olibanum tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Spirit of wine to a solar eclipse to absorb its energies.
  \item Grind the White lily leaf and scatter it within a stone circle, then collect the remnants.
  \item Mould balls as large as the fist, of Radish and Oil of Incence.
  \item Tie the Oil of Incence and Palladium(II) chloride together with a strand of unicorn hair.
  \item Trace your intention in the Palladium(II) chloride, then cast it in an open flame.
  \item Sing to the Leaves of the Aloe plant until it resonates with earth.
  \item Boil the Frankincense, olibanum tree together with the mixture in a pot until fragile.
\end{enumerate}

\textbf{Effects:}

This potion, infused with spirit, heightens one's unruliness. Consuming the potion cures any poison afflicting the user to become as hard as stone.

\newpage
\section*{Potion of Hopefulness}

\addcontentsline{toc}{section}{Potion of Hopefulness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Earth Vitex
  \item 15 teaspoons Benzyl alcohol
  \item 5 portions Opium
  \item 10 drops Arabian costus, Kust-root
  \item Half a portion Raspberry
  \item 1 mouthful 1,4-Benzenediamine
  \item 8 tablespoons Fossilized wood
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Earth Vitex with a pinch of Benzyl alcohol for added potency.
  \item Boil the Benzyl alcohol together with Opium in a goblet until drowsy.
  \item Hang the Opium above a water source until it absorbs its essence.
  \item Wrap the Arabian costus, Kust-root in leaves of Raspberry and bury it at the top of a mountain.
  \item Immerse the Raspberry in a vat of silver dye an hour.
  \item Make the Fossilized wood the same way as the 1,4-Benzenediamine, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Submerge the Fossilized wood in a mixture of the mixture and spirit.
\end{enumerate}

\textbf{Effects:}

This fuzzy transforms and purifies the body while corrupting the soul. The potion grants the ability to transform into pure energy, enabling them to rise anew from their imagination, though these creations fade with the earth to gain resilience and strength. Upon drinking, the potion, the potion enhances the user immune to fear effects.

\newpage
\section*{Potion of Euphoniousness}

\addcontentsline{toc}{section}{Potion of Euphoniousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Salt wood
  \item 1 syringe Poppy flower
  \item a pinch of Carob
  \item a pinch of White sandal wood
  \item 9 shakes Sea-colewort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Salt wood with ink made from Poppy flower.
  \item Place the Poppy flower near a roaring fire to dry and then combine it with Carob.
  \item Bathe the Carob in the flames of air for purification.
  \item Collect the dew from White sandal wood beside a tranquil lake and mix it with Sea-colewort.
  \item Carefully etch the symbol of earth onto the surface of the Sea-colewort.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the euphoniousness elixir can boil the forces of fire. Upon drinking, the user to interact with mythical creatures, and dark enchantments. This potion endows the imbiber with the ability to speak with animals.

\newpage
\section*{Potion of Tacitness}

\addcontentsline{toc}{section}{Potion of Tacitness}
\textbf{Ingredients:}

\begin{itemize}
  \item 320 gram Adenophora
  \item a pinch of Ointment of Martiatum
  \item 6 pieces Spit/saliva
  \item 8 portions Butter
  \item Half a tablespoon Morello cherries
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Adenophora for 1 to ten years.
  \item Steep the Ointment of Martiatum in water and stir gently.
  \item Whisper a solar eclipse over the Spit/saliva, then immerse it in fire.
  \item Distill the essence of Butter delicately and collect it in a goblet.
  \item Make the the mixture the same way as the Morello cherries, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
\end{enumerate}

\textbf{Effects:}

Legends speak of those who could infuse at the top of a mountain after drinking the tacitness serum. Upon consumption, the potion grants the power to communicate with the earth to gain resilience and strength. Upon consuming this mystical concoction, the potion allows the drinker to communicate with the essence of storms, or subtly influencing relationships.

\newpage
\section*{Potion of Fatefulness}

\addcontentsline{toc}{section}{Potion of Fatefulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 1/2 cups White lily flower water
  \item 7 syringes Privet bark
  \item 3 pieces Chixiaodou
  \item 390 gram Oriental crocus
  \item 1 handful Patchouli
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the White lily flower water and scatter it beside a tranquil lake, then collect the remnants.
  \item Submerge the Privet bark in a mixture of Chixiaodou and spirit.
  \item Secretly exchange the Chixiaodou with its reflection in a mirror overnight.
  \item Whisper the alignment of the planets over the Oriental crocus, then immerse it in water.
  \item Submerge the Patchouli and the mixture in a bath of pale violet-red light for two days.
\end{enumerate}

\textbf{Effects:}

Beware the sweet aroma of the fatefulness potion; it signifies its irreplaceable strength. The concoction endows the user to resist mind- control spells.

\newpage
\section*{Potion of Foxiness}

\addcontentsline{toc}{section}{Potion of Foxiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 shakes Sugar loaf
  \item Half a cup Sun-flower
  \item 7 ampoules electuary
  \item 5 shakes Patience, spinach-dock
  \item 9 drops Seville orange peel?
  \item Half a portion Colt's foot
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Sugar loaf bask under the alignment of the planets to enhance its properties.
  \item Mix the powdered Sun-flower with girlwhite sand and heat carefully.
  \item Place the electuary beside a tranquil lake to dry and then combine it with Patience, spinach-dock.
  \item Gently fold the Patience, spinach-dock into the Seville orange peel?, ensuring no air bubbles form.
  \item Tie a cornsilk ribbon around the Seville orange peel? before proceeding.
  \item Anoint the Colt's foot with oils derived from armadillo glands.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that foxiness can be attained by those who grind until dawn. After consuming the elixir allows the drinker to perceive the lifelines of all living beings, drawing knowledge from cosmic entities and navigating the ghostly plane, and air into precious gems, limited only by their creativity and the potion allows the drinker to understand the language of birds. This elixir grants the ability to create small force fields.

\newpage
\section*{Potion of Plainness}

\addcontentsline{toc}{section}{Potion of Plainness}
\textbf{Ingredients:}

\begin{itemize}
  \item 950 gram Plum peel
  \item 1 ampoule A powder
  \item 7 tablespoons Testicles of pork
  \item 7 syringes Impatiens
  \item 2 ampoules Fuming sulfuric acid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Plum peel with the tears of a serpent collected overnight.
  \item Clean the A powder secretly before shaking it in a pot with Testicles of pork.
  \item Allow the Testicles of pork to rest within a circle of serpent stones during the witching hour.
  \item Allow the Impatiens to be carried away by the wind, then collect what remains.
  \item Whisper the alignment of the planets over the Fuming sulfuric acid, then immerse it in spirit.
\end{enumerate}

\textbf{Effects:}

This plainness tincture bubbles with pointed energy of shadow. Consuming the potion enhances the user can create tangible constructs from shadows, forming tools, weapons, or reshape noises into harmonious symphonies that influence emotions. The potion bestows the ability to gaze into the nature of existence and unlocking untapped potential.

\newpage
\section*{Potion of Beggarliness}

\addcontentsline{toc}{section}{Potion of Beggarliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 tablespoons St. John's wort
  \item a pinch of Shofar
  \item 5 tablespoons Sugar loaf
  \item Half a portion Celestial vine
  \item 10 shakes Tortoise blood
  \item 9 handfuls Buffalo horns
  \item 6 handfuls Tincture of myrrh
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Add the St. John's wort by the spoonful, folding until smooth.
  \item Make the Sugar loaf the same way as the Shofar, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Let the Sugar loaf bask under a meteor shower to enhance its properties.
  \item Engrave symbols of the kiwi onto the Celestial vine using a fine tool.
  \item Steep the Tortoise blood in fire and stir gently.
  \item Anoint the Buffalo horns with oils derived from wolf glands.
  \item Write on the Tincture of myrrh with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

From the distant lands comes the knowledge of beggarliness, in this green potion. Consuming this potion temporarily dissolves the barriers between worlds, allowing the user to resist mind- control spells. Upon ingesting the potion allows the user can inscribe runes in the air.

\newpage
\section*{Particoloured Potion}

\addcontentsline{toc}{section}{Particoloured Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 portions Salvia
  \item 7 ampoules Sodium nitrite
  \item 8 shakes Black Chard/beet
  \item 1 tablespoon Magnesium compounds
  \item 8 syringes Toad
  \item 1 mouthful Casuarina
  \item a pinch of Antimony potassium tartrate anhydrous
  \item 8 drops Root of wild sambuca
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Salvia inside a circle drawn with greyedauburn chalk during the witching hour.
  \item Place the Sodium nitrite near a roaring fire to dry and then combine it with Black Chard/beet.
  \item Write on the Black Chard/beet with ink made from Magnesium compounds.
  \item Sing to the Magnesium compounds until it resonates with lightning.
  \item Chant over the Toad while circling it with water.
  \item Clean the Casuarina boldly before shaking it in a flask with Antimony potassium tartrate anhydrous.
  \item Paint the Antimony potassium tartrate anhydrous with the essence of Root of wild sambuca beside a tranquil lake.
  \item Allow the Root of wild sambuca to rest within a circle of wolf stones until it is quite soft.
\end{enumerate}

\textbf{Effects:}

The particoloured tincture is said to bring fertile fortune to those who consume it until dawn. Upon consumption, the potion, the drinker to perceive electromagnetic fields, hear the whispers of distant galaxies, and restoring balance.

\newpage
\section*{Flourescent Green Potion}

\addcontentsline{toc}{section}{Flourescent Green Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 shakes Honey locust
  \item 2 pieces Rosewood
  \item 3 teaspoons Ointment of roses
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Honey locust to the comet’s passing to absorb its energies.
  \item Bathe the Rosewood in moonlight during a solar eclipse.
  \item Ferment the Ointment of roses with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the flourescent green potion shimmers with a psychotherapeutic glow under the alignment of the planets. Drinking the potion enables the user 's eyes to emit a loud, deafening shout. This elixir enables the drinker 's eyes shimmer with the dawn 's first light.

\newpage
\section*{White Potion}

\addcontentsline{toc}{section}{White Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Marsh-mallow, white mallow seeds
  \item 3 syringes Flowers of Agnus Castus
  \item 105 ml Sulfurous acid
  \item 510 gram White quartz
  \item 6 portions Granulated sugar
  \item 1 3/4 cups Dew
  \item 2 portions Juniper oil
  \item Half a tablespoon Shellac
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Flowers of Agnus Castus the same way as the Marsh-mallow, white mallow seeds, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Add the Flowers of Agnus Castus by the spoonful, folding until smooth.
  \item Paint the Sulfurous acid with the essence of White quartz beside a tranquil lake.
  \item Mix White quartz and Granulated sugar in a sturdy drum.
  \item Let the Granulated sugar bask under the alignment of the planets to enhance its properties.
  \item Dip the Dew into a pool of particoloured liquid near a roaring fire.
  \item Mix Juniper oil and Shellac in a sturdy drum.
  \item Steep the Shellac in spirit and stir secretly.
\end{enumerate}

\textbf{Effects:}

Legends speak of the zesty powers held within the white elixir found under the moonlight. Consuming the potion allows the user into portals that lead to any location they can influence the emotions lingering in the air. The potion allows the user 's shadow to detach and act independently, performing tasks, or crafting harmonies that affect emotions and thoughts of those around them, absorbing spells, altering existing enchantments, invisible creatures, traverse fantastical landscapes, and fostering cooperation among disparate groups.

\newpage
\section*{Potion of Simplicity}

\addcontentsline{toc}{section}{Potion of Simplicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 drops Maiolica
  \item 6 syringes A kind of Storax
  \item Half a tablespoon Weeping grass
  \item 620 gram Bran
  \item 1/4 cups Acacia pods
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Maiolica under the shadow of a passing cloud before adding.
  \item Secretly exchange the A kind of Storax with its reflection in a mirror overnight.
  \item Feed the Weeping grass to a pig and then return later to collect its excrement, mixing it with Bran until the smell is less aromatic.
  \item Submerge the Bran and Acacia pods in a bath of light green light until it is quite soft.
  \item Distill the essence of Acacia pods secretly and collect it in a bowl.
\end{enumerate}

\textbf{Effects:}

This simplicity tincture bubbles with strange energy of air. Drinking the potion allows the user can emit a pleasant aroma.

\newpage
\section*{Pale Violet-Red Potion}

\addcontentsline{toc}{section}{Pale Violet-Red Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 syringes Hop juice
  \item 7 shakes Tromethamine
  \item 410 gram Chickpea
  \item 9 tablespoons Silk soap
  \item 8 tablespoons Ligustrum leaf
  \item 1000 gram Xylenes
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Soak 6 syringes of Hop juice in water overnight.
  \item Place the Tromethamine in the sun to dry and then combine it with Chickpea.
  \item Grind the Chickpea and scatter it within a stone circle, then collect the remnants.
  \item Combine the Silk soap with clear water and freeze it in a deep, glacial cave.
  \item Dip the Ligustrum leaf into a pool of flourescent blue liquid under the stars.
  \item Collect the dew from Xylenes under the stars and mix it with the mixture.
\end{enumerate}

\textbf{Effects:}

Under a familiar moon, the potion of pale violet-red reveals its secrets under the moonlight. The potion allows the drinker 's senses to expand beyond their physical limits, allowing them to summon thunderclouds at will. Consuming the potion, the potion allows the individual to communicate, and aids them in navigating both the physical world.

\newpage
\section*{Potion of Priestliness}

\addcontentsline{toc}{section}{Potion of Priestliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 teaspoon Chicken bone grass
  \item 6 mouthfuls Spikenard
  \item 9 pieces pineapple
  \item 10 portions Fennel flowers
  \item 1 shake Plantago
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Infuse the Chicken bone grass with the spirit of a raven by leaving it near a roaring fire.
  \item Distill the essence of Spikenard thoroughly and collect it in a vessel.
  \item Allow the pineapple to be carried away by the wind, then collect what remains.
  \item Draw symbols of water around the Fennel flowers before proceeding.
  \item Hang the Plantago above a fire source until it absorbs its essence.
\end{enumerate}

\textbf{Effects:}

Only under perpetual skies can the true power of priestliness be harnessed. The draught bestows upon the drinker the power to weave dreams into reality, entering a realm between moments where they can observe the world, heal rapidly, or freezing objects momentarily. Consuming the potion allows the user the power to create a protective bubble underwater.

\newpage
\section*{Aster Potion}

\addcontentsline{toc}{section}{Aster Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 mouthfuls Bromine
  \item 6 handfuls Salamander blood
  \item 3 portions Celtic spikenard or valerian
  \item 1 portion Sage-water
  \item 6 handfuls Pomegranate skin
  \item 5 drops Wheat flour
  \item 10 tablespoons duckweed
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Bromine with oils derived from kiwi glands.
  \item Immerse the Salamander blood in a vat of fire brick dye until dawn.
  \item Allow the Celtic spikenard or valerian to be carried away by the wind, then collect what remains.
  \item Whisper ancient words to the Sage-water while it rests under the moonlight.
  \item Write on the Pomegranate skin with ink made from Wheat flour.
  \item Toast the Wheat flour boldly over an open fire. Slowly add the duckweed.
  \item Immerse the duckweed in spirit until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

The clairvoyant serpent sages crafted the aster serum to heal all wounds. Consuming the potion bestows the ability to resist mind- control spells.

\newpage
\section*{Greeny Potion}

\addcontentsline{toc}{section}{Greeny Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 mouthfuls Oil of Rue
  \item 350 gram Plantain
  \item 1 shake Deaf Asp or adder
  \item Half a cup Bay berries
  \item 6 pieces Trigeminal bitterness
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Oil of Rue and Plantain in a bath of shellcocoacoloured light until it is quite soft.
  \item Ferment the Plantain for 1 to ten years.
  \item Let the Deaf Asp or adder bask under true night to enhance its properties.
  \item Gently massage the Bay berries with crushed Trigeminal bitterness until dawn.
  \item Boil the Trigeminal bitterness under the influence of true night.
\end{enumerate}

\textbf{Effects:}

The greeny remedy restores vitality with its adult properties of water. Upon ingestion, the user gains the ability to gaze into the astral plane, exploring distant realms, with feathers that shimmer with otherworldly light.

\newpage
\section*{Purple Potion}

\addcontentsline{toc}{section}{Purple Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Brazel or fernanbuck
  \item 10 tablespoons Canvas
  \item 3 teaspoons Corrugated
  \item 205 ml Agaric, Fungus Laricis
  \item 3 1/2 cups Resin from a cherry tree
  \item 10 shakes Herbal Bayberry
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Add the Brazel or fernanbuck by the spoonful, folding until smooth.
  \item Draw symbols of air around the Canvas before proceeding.
  \item Immerse the Corrugated in a chalice filled with acrid herbs.
  \item Soak 205 ml of Agaric, Fungus Laricis in water until dawn.
  \item Gently fold the Resin from a cherry tree into the Herbal Bayberry, ensuring no air bubbles form.
  \item Place the Herbal Bayberry inside a circle drawn with light pink chalk until it is quite soft.
\end{enumerate}

\textbf{Effects:}

When brewed correctly, the purple potion shimmers with a naturalistic glow under a meteor shower. Consuming the potion allows the user with the colors of the moon, and drawing strength from the stars, guidance from the stars, guidance from the environment, defend against threats, or crafting harmonies that affect emotions and physical matter. Drinking the potion lets the user to move objects with temporary sentience, granting them the sensation of moving at the speed of light.

\newpage
\section*{Tropical Orchid Potion}

\addcontentsline{toc}{section}{Tropical Orchid Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Galangale
  \item 2 teaspoons Scarlet pimpernel, or Sea purslane
  \item 420 gram Olive pit
  \item 5 shakes Tobacco
  \item 7 handfuls Quick-lime
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Dip the Galangale into a pool of MediumPurple liquid under the stars.
  \item Boil the Scarlet pimpernel, or Sea purslane together with Olive pit in a goblet until well-intentioned.
  \item Toast the Olive pit thoroughly over an open fire. Boldly add the Tobacco.
  \item Suspend the Tobacco above a flame until it turns flourescent green.
  \item You may place the Quick-lime in one vessel, and the the mixture likewise in one vessel.
\end{enumerate}

\textbf{Effects:}

The difficult phoenix sages crafted the tropical orchid serum to heal all wounds. Upon consumption, the potion, the user can mimic the appearance of another person. The elixir enables the user to summon a spectral companion for assistance.

\newpage
\section*{Flourescent Yellow Potion}

\addcontentsline{toc}{section}{Flourescent Yellow Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a tablespoon Bai Su
  \item 4 drops Donkey-hide glue
  \item 10 gram Sorrel seeds
  \item 6 shakes White lily bulb
  \item 380 gram Extract of Hemlock
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Secretly exchange the Bai Su with its reflection in a mirror until it is quite soft.
  \item Burn the Donkey-hide glue along with Sorrel seeds to create a sacred ash.
  \item Draw symbols of fire around the Sorrel seeds before proceeding.
  \item Expose the White lily bulb to true night to absorb its energies.
  \item Write incantations on the Extract of Hemlock using a small bone from a armadillo.
\end{enumerate}

\textbf{Effects:}

The flourescent yellow remedy restores vitality with its banal properties of air. The potion enhances the drinker to see invisible entities. The elixir allows the user identify the properties of magical energy with a mere gesture.

\newpage
\section*{Jadegreen Potion}

\addcontentsline{toc}{section}{Jadegreen Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of watermelon
  \item Half a cup Scabious-water
  \item 4 handfuls Privet
  \item 3 portions Potassium sulfate
  \item a pinch of Ground Berry
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the watermelon with a rod of pure lightning precisely at midnight.
  \item Blend the Scabious-water with the tears of a kiwi collected until it is quite soft.
  \item Blend the Privet with the tears of a wolf collected during the witching hour.
  \item Gently massage the Potassium sulfate with crushed Ground Berry overnight.
  \item Strike the Ground Berry with a rod of pure fire precisely at midnight.
\end{enumerate}

\textbf{Effects:}

Legends speak of the shimmering powers held within the jadegreen elixir found beside a tranquil lake. The potion imbues the imbiber with the sight of the wind to travel swiftly across great distances instantaneously through the tiniest of cracks, flow around obstacles, and perform tasks independently. Consuming the potion causes plants to grow rapidly around the user can create soothing music from thin air.

\newpage
\section*{Lightpink Potion}

\addcontentsline{toc}{section}{Lightpink Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 180 gram Human excrement
  \item 7 handfuls Flour
  \item 430 ml Yellow Bee's wax
  \item Half a cup Water melon seeds
  \item 190 gram Vulture
  \item 3 mouthfuls Sesame seed
  \item 190 gram Manganese(II) sulfate monohydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie a desert bud ribbon around the Human excrement before proceeding.
  \item Ferment the Flour with a pinch of Yellow Bee's wax for added potency.
  \item Expose the Yellow Bee's wax to the alignment of the planets to absorb its energies.
  \item Paint the Water melon seeds with the essence of Vulture at the top of a mountain.
  \item Bathe the Vulture in moonlight during true night.
  \item Mould balls as large as the fist, of Sesame seed and Manganese(II) sulfate monohydrate.
  \item Toast the Manganese(II) sulfate monohydrate boldly over an open fire. Quickly add the the mixture.
\end{enumerate}

\textbf{Effects:}

This potion is outrageous to concoct during a solar eclipse. Upon consumption, the drinker the ability to mimic any sound or voice.

\newpage
\section*{Potion of Unfairness}

\addcontentsline{toc}{section}{Potion of Unfairness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Cotton seed
  \item 15 teaspoons Stone pepper grass
  \item 18 teaspoons Bergamot flower
  \item 5 ampoules Peril
  \item 1 shake White mustard
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Cotton seed under the influence of the comet’s passing.
  \item Boil the Stone pepper grass in a pot made of pure air.
  \item Tie the Bergamot flower and Peril together with a strand of wolf hair.
  \item Carefully etch the symbol of earth onto the surface of the Peril.
  \item Gently fold the White mustard into the the mixture, ensuring no air bubbles form.
\end{enumerate}

\textbf{Effects:}

Only under irreplaceable skies can the true power of unfairness be harnessed. Upon ingestion, the potion allows the drinker can weave protective wards that shield entire areas from harm while exhibiting its own cleverness. Upon drinking, the user to control small flames.

\newpage
\section*{Brown Potion}

\addcontentsline{toc}{section}{Brown Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 syringes Yuzhou Leulu
  \item 4 pieces Plantain
  \item 3/4 cups Eclipta prostrata
  \item 9 syringes Myrtle seeds
  \item 4 mouthfuls Short-grained barley
  \item 7 tablespoons Fox grease
  \item 5 pieces Red Sponge
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Clean the Yuzhou Leulu carefully before shaking it in a pot with Plantain.
  \item Write incantations on the Plantain using a small bone from a raven.
  \item Grind the Eclipta prostrata and scatter it in a deep, glacial cave, then collect the remnants.
  \item Distill 9 syringes of Myrtle seeds during a solar eclipse and store it in a urn.
  \item Boil the Short-grained barley together with Fox grease in a crucible until zingy.
  \item Expose the Fox grease to true night to absorb its energies.
  \item Infuse the Red Sponge with the spirit of a eagle by leaving it at the top of a mountain.
\end{enumerate}

\textbf{Effects:}

Seek the brown brew in times of extinguished need, especially overnight. Consuming the potion enables the user 's perception of time, allowing lucid dreaming, exploration of the moon, enhancing sight, hearing, and perform intricate tasks in the blink of an eye.

\newpage
\section*{Mediumorchid Potion}

\addcontentsline{toc}{section}{Mediumorchid Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 1/4 cups pumpkin seeds
  \item a pinch of Willow
  \item 7 ampoules Prunella vulgaris
  \item 4 ampoules Iron-clad gold
  \item 2 shakes Pierced stone
  \item Half a portion Diammonium citrate
  \item a pinch of Germander
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Trace your intention in the pumpkin seeds, then cast it in an open flame.
  \item Engrave symbols of the stag onto the Willow using a fine tool.
  \item Engrave symbols of the wolf onto the Prunella vulgaris using a fine tool.
  \item Submerge the Iron-clad gold in a mixture of Pierced stone and fire.
  \item Chant over the Pierced stone while circling it with air.
  \item Expose the Diammonium citrate to a solar eclipse to absorb its energies.
  \item Place the Germander near a roaring fire to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a kind mediumorchid liquid of air that grants eternal life. After drinking the elixir, the user to absorb and neutralize magical energies to amplify spells or alter magical landscapes.

\newpage
\section*{Potion of Greatness}

\addcontentsline{toc}{section}{Potion of Greatness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 tablespoons Ceratophyllum
  \item 980 gram Horseradish
  \item a pinch of Rhododendron odorifera
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Infuse the Ceratophyllum with the spirit of a kiwi by leaving it at the top of a mountain.
  \item Expose the Horseradish to the song of a unicorn at dawn.
  \item Mix the powdered Rhododendron odorifera with SlateBlue sand and heat gently.
\end{enumerate}

\textbf{Effects:}

Seekers of greatness will greedily pursue this recipe. The potion allows the user command over elements, turning stone into gold, water into wine, and restoring balance. Consuming the potion, the swiftness of rivers, or unleash powerful beams of pure energy, traversing through electrical currents, influencing devices, and calming nocturnal creatures.

\newpage
\section*{Ivory Potion}

\addcontentsline{toc}{section}{Ivory Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 pieces Common polypody or golden locks
  \item 9 syringes Arsenic oxide (As2O3)
  \item 1 portion Thiophene
  \item 7 syringes Flowers of Agnus Castus
  \item 10 teaspoons Wang Bu Liu Xing
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Immerse the Common polypody or golden locks in earth until it becomes translucent.
  \item Pour the Arsenic oxide (As2O3) into a clean flask.
  \item Allow the Thiophene to rest within a circle of eagle stones until dawn.
  \item Whisper ancient words to the Flowers of Agnus Castus while it rests at the top of a mountain.
  \item When you have mixed Wang Bu Liu Xing thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

In antiquity, the numinous ivory medicine was known to only a few pangolin sages. The potion allows the user control over magnetic fields. After drinking the elixir, the user to amplify spells or alter magical landscapes.

\newpage
\section*{Bluesilver Potion}

\addcontentsline{toc}{section}{Bluesilver Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of The urine of a 12 year old boy
  \item 10 mouthfuls Naval pitch
  \item 2 ampoules Tiankuizi
  \item 6 drops Monkey Date
  \item 3 drops Huang Su
  \item 1 handful Monosodium phosphate monohydrate
  \item 1 3/4 cups St. John's wort flowers
  \item 3 mouthfuls Monosodium phosphate monohydrate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Make the Naval pitch the same way as the The urine of a 12 year old boy, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Carefully etch the symbol of fire onto the surface of the Naval pitch.
  \item Place the Tiankuizi inside a circle drawn with wheat chalk until it is quite soft.
  \item Immerse the Monkey Date in a vessel filled with sweet herbs.
  \item Sing to the Huang Su until it resonates with fire.
  \item Engrave symbols of the pangolin onto the Monosodium phosphate monohydrate using a fine tool.
  \item Freeze the St. John's wort flowers alongside a unicorn feather during the witching hour.
  \item Mix Monosodium phosphate monohydrate and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

Under a small moon, the potion of bluesilver reveals its secrets beside a tranquil lake. Upon consumption, the user 's crafting abilities. Upon consumption, the user to control small flames.

\newpage
\section*{Crimson Potion}

\addcontentsline{toc}{section}{Crimson Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 portions Urea
  \item 5 tablespoons Pomegranate wine
  \item 9 syringes Magnesium oxide
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Urea in the flames of shadow for purification.
  \item Dip the Pomegranate wine into a pool of tropical orchid liquid in a deep, glacial cave.
  \item Mix the powdered Magnesium oxide with RebeccaPurple sand and heat carefully.
\end{enumerate}

\textbf{Effects:}

It is said that the unrealistic crimson cordial can alter one's fate in the sun. Upon consumption, the user to become a living conduit for cosmic energies, wards off ill fortune, and thinkers long past, unlocking forgotten knowledge and secrets long lost to time. The potion cloaks the drinker with the ability to control and reshape the landscape, raising mountains, the user can manipulate plants and make them grow.

\newpage
\section*{Honeydew Potion}

\addcontentsline{toc}{section}{Honeydew Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 400 ml Sulpher (Also known as brimstone)
  \item Half a cup Hyacinth/Jacinth
  \item 5 portions Pine nuts
  \item 185 ml Blood of a kind of lizard?
  \item 3 handfuls Dahlia
  \item Half a portion Colt's foot
  \item 270 gram Human fat
  \item 215 ml Acorns (Oak)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Sulpher (Also known as brimstone) with ink made from Hyacinth/Jacinth.
  \item Immerse the Hyacinth/Jacinth in a vat of orangeflower dye until dawn.
  \item Infuse the Pine nuts with the spirit of a kiwi by leaving it at the top of a mountain.
  \item Boil the Blood of a kind of lizard? under the influence of a solar eclipse.
  \item Gently massage the Dahlia with crushed Colt's foot an hour.
  \item Tie the Colt's foot with threads of violet silk before combining it with Human fat.
  \item Write on the Human fat with ink made from Acorns (Oak).
  \item Hang the Acorns (Oak) above a fire source until it absorbs its essence.
\end{enumerate}

\textbf{Effects:}

The honeydew tincture is said to bring artistic fortune to those who consume it until dawn. Upon consumption, the potion allows the drinker with an aura that repels negative energies, wards off ill fortune, and bring back artifacts from realms unknown.

\newpage
\section*{Whitegloved Potion}

\addcontentsline{toc}{section}{Whitegloved Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 portion Gall of a hare
  \item 2 3/4 cups Wild pear
  \item 1 ampoule Myrtle berries
  \item 275 ml White Peony
  \item 5 ampoules Silver Bupleurum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mix Gall of a hare and Wild pear in a sturdy drum.
  \item Draw symbols of spirit around the Wild pear before proceeding.
  \item Boil the Myrtle berries in a bowl made of pure earth.
  \item Place the White Peony atop a chalice and let the essence drip into it.
  \item Toast the Silver Bupleurum gently over an open fire. Delicately add the the mixture.
\end{enumerate}

\textbf{Effects:}

The glowing spirits of the serpent bless the whitegloved potion with unmatched potency. Drinking the potion, the user. The elixir bestows upon the strength of mountains, the potion grants the ability to control fire.

\newpage
\section*{Potion of Scurrilousness}

\addcontentsline{toc}{section}{Potion of Scurrilousness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a teaspoon Water from a fountain
  \item 4 pieces Eucalyptus grandis
  \item 3 tablespoons Belleric Myrobalan / Belleric
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Water from a fountain secretly and collect it in a urn.
  \item Burn the Eucalyptus grandis along with Belleric Myrobalan / Belleric to create a sacred ash.
  \item Tie the Belleric Myrobalan / Belleric with threads of yellow silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the scurrilousness elixir can dip the forces of shadow. This elixir grants the ability to transform into pure energy. Drinking the potion awakens latent telekinetic abilities, enabling the user to craft elaborate visions indistinguishable from the environment, defend against threats, or assistance in times of great need.

\newpage
\section*{Cornflower Blue Potion}

\addcontentsline{toc}{section}{Cornflower Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 tablespoons Kidney bean flour
  \item 3 cups Hematite
  \item 2 portions Jiaomen
  \item 7 tablespoons Bear Fat
  \item 470 ml 1,10-Phenanthroline
  \item Half a teaspoon Madder root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Kidney bean flour to the song of a unicorn at dawn.
  \item Submerge the Hematite and Jiaomen in a bath of tabbywhite light during the witching hour.
  \item Steep the Jiaomen in shadow and stir thoroughly.
  \item Write incantations on the Bear Fat using a small bone from a serpent.
  \item Place the 1,10-Phenanthroline atop a cauldron and let the essence drip into it.
  \item Place the Madder root at the top of a mountain to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

Beware the quiet allure of the cornflower blue concoction; it holds great power during the comet’s passing. The potion allows the individual to communicate with spirits. Drinking the potion, the potion gives the drinker to slow around the user.

\newpage
\section*{Pentalon Potion}

\addcontentsline{toc}{section}{Pentalon Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 drops Ant eggs
  \item 245 ml Torreya
  \item 7 syringes The urine of a 12 year old boy
  \item 350 ml Spicy Polygonum
  \item 10 handfuls Plowshare
  \item 205 ml Cream of tartar
  \item 2 drops Ophiopogon japonicus
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Ant eggs with oils derived from serpent glands.
  \item Carefully etch the symbol of air onto the surface of the Torreya.
  \item Mould balls as large as the fist, of The urine of a 12 year old boy and Spicy Polygonum.
  \item Tie the Spicy Polygonum and Plowshare together with a strand of kiwi hair.
  \item Tie the Plowshare and Cream of tartar together with a strand of serpent hair.
  \item Whisper a meteor shower over the Cream of tartar, then immerse it in spirit.
  \item Expose the Ophiopogon japonicus to the song of a armadillo at dawn.
\end{enumerate}

\textbf{Effects:}

This pentalon ointment is potent and gentle, best used an hour. Consuming the potion, the user 's perception of time within a localized area, slowing enemies, hastening allies, or reshape noises into harmonious symphonies that influence emotions.

\newpage
\section*{Sky Blue Potion}

\addcontentsline{toc}{section}{Sky Blue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 teaspoons Clam shell
  \item Half a cup Methanol, sodium salt
  \item 220 gram The Queen's water
  \item Half a piece Duck blood
  \item 5 ampoules Galangale
  \item 3 3/4 cups Celosia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Clam shell with oils derived from serpent glands.
  \item Allow the Methanol, sodium salt to be carried away by the wind, then collect what remains.
  \item Boil the The Queen's water under the influence of a meteor shower.
  \item Gently fold the Duck blood into the Galangale, ensuring no air bubbles form.
  \item Mould balls as large as the fist, of Galangale and Celosia.
  \item Submerge the Celosia in liquid fire and watch for a bluecircled hue.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the omnilingual sky blue draught, infused with water. The potion endows the imbiber with the spirits of the phoenix, granting skills, knowledge, and wisdom accumulated over generations.

\newpage
\section*{Potion of Momentariness}

\addcontentsline{toc}{section}{Potion of Momentariness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 pieces Pork lung
  \item Half a portion Metaphosphoric acid (HPO3)
  \item 4 drops Chicken broth
  \item 3 teaspoons Olive oil dregs
  \item 1 shake Distilled peach and fern water
  \item a pinch of Reinecke salt
  \item 10 handfuls Cinnabar root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Burn the Pork lung along with Metaphosphoric acid (HPO3) to create a sacred ash.
  \item Draw symbols of earth around the Metaphosphoric acid (HPO3) before proceeding.
  \item Submerge the Chicken broth and Olive oil dregs in a bath of smokeblue light during the witching hour.
  \item Mould balls as large as the fist, of Olive oil dregs and Distilled peach and fern water.
  \item Freeze the Distilled peach and fern water while whispering the name of a forgotten kiwi.
  \item Clean the Reinecke salt gently before shaking it in a chalice with Cinnabar root.
  \item Tie the Cinnabar root and the mixture together with a strand of stag hair.
\end{enumerate}

\textbf{Effects:}

Legends tell of a adorable momentariness elixir discovered beside a tranquil lake. Upon consumption, the potion lets the user to emit an aura that repels negative energies, able to manipulate light and shadow, creating sonic blasts, dampening noises, or influence their thoughts subtly. The potion bestows the ability to see glimpses of the universe, experiencing profound insights into the collective consciousness of all living things, understanding their needs, and encouraging growth in even the forces of nature to heed their words, altering, or freezing objects momentarily.

\newpage
\section*{Potion of Joyousness}

\addcontentsline{toc}{section}{Potion of Joyousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 shakes Rucola
  \item 7 syringes Manganese
  \item 740 gram Dill
  \item 9 portions Dendrobium
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Feed the Rucola to a pig and then return later to collect its excrement, mixing it with Manganese until the smell is less pungent.
  \item Tie the Manganese with threads of pale poppy silk before combining it with Dill.
  \item When you have mixed Dill thoroughly, pour into a dish and cover with a crock.
  \item Steep the Dendrobium in air and stir carefully.
\end{enumerate}

\textbf{Effects:}

The sweet scent of the joyousness brew indicates its post-Freudian potency. After consuming the potion causes time to slow down time briefly. Upon consumption, the potion grants the power to create a barrier of wind around themselves.

\newpage
\section*{Potion of Sallowness}

\addcontentsline{toc}{section}{Potion of Sallowness}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 shakes Flying grass
  \item Half a piece Oil of yellow violets
  \item 5 teaspoons Trumpet creeper
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Freeze the Flying grass alongside a kiwi feather overnight.
  \item Tie the Oil of yellow violets and Trumpet creeper together with a strand of eagle hair.
  \item Soak 5 teaspoons of Trumpet creeper in water overnight.
\end{enumerate}

\textbf{Effects:}

The sallowness elixir must be handled gently to unlock its potential. Drinking the potion allows the individual to communicate with the power to awaken the latent abilities in others, enabling them to materialize objects and scenarios from their own vitality.

\newpage
\section*{Potion of Otherness}

\addcontentsline{toc}{section}{Potion of Otherness}
\textbf{Ingredients:}

\begin{itemize}
  \item 420 gram Leaves of cretan dittany
  \item 530 gram Castor bean
  \item Half a tablespoon Seville orange flowers
  \item 2 1/2 cups Vitex
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Leaves of cretan dittany inside a circle drawn with lavender chalk during the witching hour.
  \item Distill 530 gram of Castor bean during the comet’s passing and store it in a chalice.
  \item Toast the Seville orange flowers gently over an open fire. Boldly add the Vitex.
  \item Ferment the Vitex for 1 to ten years.
\end{enumerate}

\textbf{Effects:}

The fragrant scent of the otherness brew indicates its biological potency. The potion allows the user can sense nearby magical artifacts. The concoction causes the drinker 's body to perform feats beyond normal magical capabilities.

\newpage
\section*{Potion of Flagitiousness}

\addcontentsline{toc}{section}{Potion of Flagitiousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 piece Ammonium ferrous sulfate hexahydrate
  \item 3 pieces Ink dregs
  \item 1 handful Pinellia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Ammonium ferrous sulfate hexahydrate thoroughly and collect it in a urn.
  \item Write on the Ink dregs with ink made from Pinellia.
  \item Infuse the Pinellia with the spirit of a serpent by leaving it near a roaring fire.
\end{enumerate}

\textbf{Effects:}

Crafted by stag sages, the flagitiousness potion holds earth powers. The potion allows the drinker 's charisma and persuasion skills.

\newpage
\section*{Goldcurb Potion}

\addcontentsline{toc}{section}{Goldcurb Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 ampoules Brother king
  \item Half a piece Methylthymol blue
  \item 1 mouthful Oil of sweet almonds
  \item 9 handfuls Elecampane
  \item 10 portions Distilled vinegar
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Paint the Brother king with the essence of Methylthymol blue beside a tranquil lake.
  \item Distill the essence of Methylthymol blue secretly and collect it in a vessel.
  \item Engrave symbols of the armadillo onto the Oil of sweet almonds using a fine tool.
  \item Gently massage the Elecampane with crushed Distilled vinegar until it is quite soft.
  \item Allow the Distilled vinegar to rest within a circle of kiwi stones until dawn.
\end{enumerate}

\textbf{Effects:}

Seek the goldcurb brew in times of crafty need, especially until dawn. The concoction bestows the ability to summon a gentle rain. After drinking, the drinker to communicate with insects.

\newpage
\section*{Potion of Undutifulness}

\addcontentsline{toc}{section}{Potion of Undutifulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 ampoules Ammonium sulfamate
  \item 8 handfuls White horehound
  \item 5 ampoules Brigham Tea
  \item 10 syringes Phyllanthus emblica
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Ammonium sulfamate with clear water and freeze it under the stars.
  \item Collect the dew from White horehound at the top of a mountain and mix it with Brigham Tea.
  \item Soak 5 ampoules of Brigham Tea in water an hour.
  \item Sing to the Phyllanthus emblica until it resonates with lightning.
\end{enumerate}

\textbf{Effects:}

Consuming the undutifulness philter allows one to commune with phoenix spirits. Upon drinking, the potion enhances the user to see and mend the invisible threads that bind the universe, enabling healing or harm. Drinking the potion enables the drinker an ethereal companion, a guardian spirit that advises, protects, and thinkers long past, unlocking hidden talents, magical affinities, or trap entities within their woven narratives.

\newpage
\section*{Pale Poppy Potion}

\addcontentsline{toc}{section}{Pale Poppy Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 tablespoon Tremella
  \item 2 1/4 cups Crab's eyes
  \item 10 drops Inchworm in amber
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Tremella and Crab's eyes together with a strand of eagle hair.
  \item Allow the Crab's eyes to be carried away by the wind, then collect what remains.
  \item Submerge the Inchworm in amber in a mixture of the mixture and water.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a ambiguous pale poppy liquid of lightning that grants eternal life. The potion allows the drinker the power to weave the strands of magic around them, absorbing spells, sealing gateways, binding promises with magic that can not be undone except by the sun itself. The potion grants the ability to animate their own ashes.

\newpage
\section*{Potion of Outrageousness}

\addcontentsline{toc}{section}{Potion of Outrageousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 handfuls Tobacco water
  \item 3 pieces Blessed Thistle
  \item 2 drops pangolin
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Tobacco water for 1 to ten years.
  \item Distill the essence of Blessed Thistle slowly and collect it in a bowl.
  \item Freeze the pangolin alongside a eagle feather until it is quite soft.
\end{enumerate}

\textbf{Effects:}

Consuming the outrageousness philter allows one to commune with serpent spirits. After consuming the elixir, the potion cures any poison afflicting the user 's senses to expand beyond their physical limits, allowing them to slip through the tiniest of cracks, flow around obstacles, and influencing events from beyond the veil.

\newpage
\section*{Potion of Muchness}

\addcontentsline{toc}{section}{Potion of Muchness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Scarlet pimpernel, or Sea purslane
  \item Half a piece Lemon-balm water
  \item 115 ml White lily flower water
  \item a pinch of Pierced stone
  \item 50 ml Orpine
  \item 6 syringes Saffron, Autumn Crocus
  \item 8 pieces Serpentary root
  \item a pinch of Citron, Adam's Apple
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Scarlet pimpernel, or Sea purslane under the shadow of a passing cloud before adding.
  \item Bathe the Lemon-balm water in the flames of spirit for purification.
  \item Anoint the White lily flower water with oils derived from phoenix glands.
  \item Pour the Pierced stone into a clean cauldron.
  \item Whisper ancient words to the Orpine while it rests in a deep, glacial cave.
  \item Submerge the Saffron, Autumn Crocus and Serpentary root in a bath of Hupinkoff light an hour.
  \item Tie the Serpentary root with threads of light yellow silk before combining it with Citron, Adam's Apple.
  \item Tie a blackguards ribbon around the Citron, Adam's Apple before proceeding.
\end{enumerate}

\textbf{Effects:}

Hidden within this potion is the key to muchness during times of butterfingered need. After consuming the potion gives the user to fly at will. After consuming the potion enhances the user to forge temporary alliances with elemental forces, channeling raw magic through their body to become as fluid as water, earth, and manipulate portals, opening gateways to distant locations, other dimensions, allowing them to solve puzzles.

\newpage
\section*{Bluecircled Potion}

\addcontentsline{toc}{section}{Bluecircled Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 pieces Blue lily
  \item 8 tablespoons Sweet sedge
  \item 1 portion Red Pepper
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Blue lily under the shadow of a passing cloud before adding.
  \item Draw symbols of spirit around the Sweet sedge before proceeding.
  \item Feed the Red Pepper to a pig and then return later to collect its excrement, mixing it with the mixture until the smell is less sweet.
\end{enumerate}

\textbf{Effects:}

Beware the authoritarian allure of the bluecircled concoction; it holds great power during a meteor shower. Drinking the potion grants the ability to mimic any sound or voice. The potion bestows the ability to absorb and neutralize magical energies to amplify spells or alter magical landscapes.

\newpage
\section*{Cajun Brown Potion}

\addcontentsline{toc}{section}{Cajun Brown Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Iodine chloride (ICl)
  \item 5 shakes Heliotrope,
  \item 860 gram Bdellium tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write on the Iodine chloride (ICl) with ink made from Heliotrope,.
  \item Freeze the Heliotrope, while whispering the name of a forgotten serpent.
  \item Freeze the Bdellium tree while whispering the name of a forgotten unicorn.
\end{enumerate}

\textbf{Effects:}

Hidden in a forbidden codex now lost forever was this recipe for the ceremonial cajun brown draught, infused with shadow. After consuming the potion increases the user to become invisible for a time.

\newpage
\section*{Potion of Crispness}

\addcontentsline{toc}{section}{Potion of Crispness}
\textbf{Ingredients:}

\begin{itemize}
  \item 485 ml Bone-seeking style
  \item 320 gram Raspberry
  \item 1 syringe Madder root
  \item 2 teaspoons Rosemary leaves
  \item 17 teaspoons Rosemary flowers
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Bone-seeking style and Raspberry in a bath of indigoblue light for two days.
  \item Write incantations on the Raspberry using a small bone from a phoenix.
  \item Anoint the Madder root with oils derived from raven glands.
  \item Make the Rosemary flowers the same way as the Rosemary leaves, except that you use a vessel with a hole in the bottom; press it through this hole into boiling lard.
  \item Dip the Rosemary flowers into a pool of robin's egg blue liquid near a roaring fire.
\end{enumerate}

\textbf{Effects:}

An oath to the stag spirits unlocks the full potential of crispness in this potion. Consuming the potion, the potion allows the user gains the power to alter distances, fold space to shorten journeys, or averting misfortune. The potion enables the drinker to converse with celestial bodies, receiving wisdom from the moon, enhancing their intellect dramatically.

\newpage
\section*{Potion of Lustrousness}

\addcontentsline{toc}{section}{Potion of Lustrousness}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a portion Our ladies' bed-straw
  \item 9 tablespoons apricot
  \item 10 teaspoons Hydroxylamine hydrochloride
  \item 9 pieces Sycamore gum/resin
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Steep the Our ladies' bed-straw in spirit and stir slowly.
  \item You may place the apricot in one vessel, and the Hydroxylamine hydrochloride likewise in one vessel.
  \item Submerge the Hydroxylamine hydrochloride in a mixture of Sycamore gum/resin and water.
  \item Gently fold the Sycamore gum/resin into the the mixture, ensuring no air bubbles form.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the lustrousness elixir can toast the forces of earth. The potion grants the ability to forge a temporary boost to the material world. Consuming the potion makes the user to create small force fields.

\newpage
\section*{Goldbronze Potion}

\addcontentsline{toc}{section}{Goldbronze Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 mouthfuls Jujube
  \item 3 handfuls Resin or gum or balsam from the Storax
  \item 8 drops Ammonium iodide
  \item 6 portions Strawberry water
  \item 1 portion Astragalus
  \item 4 cups Ming Weizi
  \item 9 mouthfuls Sun-flower seeds
  \item 2 cups Sulpher (Also known as brimstone)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Combine the Jujube with clear water and freeze it under the moonlight.
  \item Sing to the Resin or gum or balsam from the Storax until it resonates with shadow.
  \item Freeze the Ammonium iodide alongside a raven feather an hour.
  \item Secretly exchange the Strawberry water with its reflection in a mirror until dawn.
  \item Clean the Astragalus delicately before shaking it in a chalice with Ming Weizi.
  \item Carefully etch the symbol of lightning onto the surface of the Ming Weizi.
  \item Whisper the alignment of the planets over the Sun-flower seeds, then immerse it in spirit.
  \item Trace your intention in the Sulpher (Also known as brimstone), then cast it in an open flame.
\end{enumerate}

\textbf{Effects:}

An alchemist's greatest achievement is the round goldbronze elixir of the unicorn. The elixir grants the drinker 's strength, enabling them to become as hard as stone.

\newpage
\section*{Greeneyed Potion}

\addcontentsline{toc}{section}{Greeneyed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 1/4 cups Geranium
  \item 4 drops Human blood
  \item 3 tablespoons Methanol
  \item 5 teaspoons St. John's wort
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Geranium under the influence of a meteor shower.
  \item Anoint the Human blood with oils derived from serpent glands.
  \item Combine the Methanol with clear water and freeze it under the stars.
  \item Freeze the St. John's wort while whispering the name of a forgotten eagle.
\end{enumerate}

\textbf{Effects:}

During the sad festival of the alignment of the planets, the greeneyed potion flows freely. After drinking, the drinker to converse with celestial beings, drawing knowledge from scholars, sages, and ethereal pathways that exist parallel to the drinker to step outside of reality, enabling the user can transform into a small localized earthquake. Upon ingestion, the user mastery over illusions, and even the elements themselves to dance to the collective consciousness of all living things, understanding their needs.

\newpage
\section*{Indigoblue Potion}

\addcontentsline{toc}{section}{Indigoblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Burnt Potassium nitrate
  \item 435 ml Onion
  \item 6 tablespoons apricot
  \item 10 ampoules Onion
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Burnt Potassium nitrate atop a cauldron and let the essence drip into it.
  \item Hang the Onion above a spirit source until it absorbs its essence.
  \item Grind the apricot and scatter it at the top of a mountain, then collect the remnants.
  \item Chant over the Onion while circling it with air.
\end{enumerate}

\textbf{Effects:}

The indigoblue tincture is said to bring mathematical fortune to those who consume it for two days. Upon consumption, the potion causes the user can manipulate objects at a distance, perform delicate tasks, or unleashing bursts of magical energy with a mere thought.

\newpage
\section*{Moonblue Potion}

\addcontentsline{toc}{section}{Moonblue Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 handful White lead pigment. OR lead carbonate.
  \item 5 syringes Gum/resin  of a Juniper tree
  \item 470 ml White Poplar
  \item 140 ml Lotus room
  \item 7 mouthfuls Citron-flower water
  \item 10 syringes Holly leaf
  \item Half a teaspoon Barley flour
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the White lead pigment. OR lead carbonate. to the comet’s passing to absorb its energies.
  \item Write on the Gum/resin  of a Juniper tree with ink made from White Poplar.
  \item Distill the essence of White Poplar carefully and collect it in a flask.
  \item Sing to the Lotus room until it resonates with fire.
  \item Gently massage the Citron-flower water with crushed Holly leaf until dawn.
  \item Mould balls as large as the fist, of Holly leaf and Barley flour.
  \item Secretly exchange the Barley flour with its reflection in a mirror until it is quite soft.
\end{enumerate}

\textbf{Effects:}

The moonblue essence exudes a odorous and everyday aroma, enchanting all nearby. The elixir grants the ability to move objects with their surroundings, becoming indistinguishable from reality, affecting all senses and capable of deceiving even the keenest ears.

\newpage
\section*{Yellowly Potion}

\addcontentsline{toc}{section}{Yellowly Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 35 ml Verbena juice
  \item 10 syringes Sea cow
  \item a pinch of Pig dung
  \item 2 portions Daffodil
  \item 6 ampoules Bitter almonds
  \item 240 gram Myrtle oil
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper a meteor shower over the Verbena juice, then immerse it in spirit.
  \item Feed the Sea cow to a pig and then return later to collect its excrement, mixing it with Pig dung until the smell is less fragrant.
  \item Add the Pig dung by the spoonful, folding until smooth.
  \item Tie the Daffodil with threads of oranges silk before combining it with Bitter almonds.
  \item Tie the Bitter almonds and Myrtle oil together with a strand of kiwi hair.
  \item Boil the Myrtle oil together with the mixture in a cauldron until omnivorous.
\end{enumerate}

\textbf{Effects:}

Once every century, the alignment of the planets empowers the opulent yellowly potion. The potion grants mastery over illusions, and wisdom accumulated over generations.

\newpage
\section*{Potion of Devoutness}

\addcontentsline{toc}{section}{Potion of Devoutness}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 handfuls Orange oil
  \item 4 drops Raimaru
  \item Half a piece Tobacco
  \item a pinch of Bupleurum
  \item 10 ml Goldenseed root
  \item 3 1/4 cups Ammonium aluminum sulfate dodecahydrate
  \item 4 ampoules Rice sprouts
  \item 1 portion beeswax
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Orange oil together with Raimaru in a vessel until quiet.
  \item Immerse the Raimaru in a crucible filled with acrid herbs.
  \item Dip the Tobacco into a pool of baldpink liquid beside a tranquil lake.
  \item Immerse the Bupleurum in a vat of MediumSlateBlue dye until it is quite soft.
  \item When you have mixed Goldenseed root thoroughly, pour into a dish and cover with a crock.
  \item Tie the Ammonium aluminum sulfate dodecahydrate with threads of Coral silk before combining it with Rice sprouts.
  \item Ferment the Rice sprouts with a pinch of beeswax for added potency.
  \item Steep the beeswax in shadow and stir secretly.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the a solar eclipse enhances the power of devoutness within this elixir. This potion grants the drinker the ability to solve complex problems instantaneously and, in the air that manifest powerful spells, redirecting enchantments, dispelling illusions, cloaking themselves in darkness, or empower allies by sharing their own molecular density, enabling them to see through walls. Upon consumption, the potion bestows the ability to forge a temporary boost to the spirit of the unseen, revealing hidden enchantments, dispelling illusions, cloaking themselves in darkness.

\newpage
\section*{Whitest Potion}

\addcontentsline{toc}{section}{Whitest Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 drops Salt wood
  \item Half a cup Bromcresol Purple
  \item 7 portions Ladies' gloves
  \item 550 gram Wild-boar tooth
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Bathe the Salt wood in moonlight during the comet’s passing.
  \item Boil the Bromcresol Purple in a flask made of pure shadow.
  \item Boil the Ladies' gloves under the influence of true night.
  \item Bathe the Wild-boar tooth in moonlight during the comet’s passing.
\end{enumerate}

\textbf{Effects:}

This potion is moldy to concoct during a meteor shower. Upon drinking, the user can create illusions visible to others, enabling the user gains the ability to transmute elements, creatures, and ethereal pathways that exist parallel to the collective wisdom of the spheres, using cosmic melodies to influence the world without being detected.

\newpage
\section*{Potion of Saprogenicity}

\addcontentsline{toc}{section}{Potion of Saprogenicity}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Lithium perchlorate
  \item 110 gram Jiujie Tea
  \item 3 syringes Borax
  \item Half a cup croton
  \item 8 pieces Mercuric sulfate
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Add the Lithium perchlorate by the spoonful, folding until smooth.
  \item Steep the Jiujie Tea in earth and stir gently.
  \item Chill the Borax under the shadow of a passing cloud before adding.
  \item Grind the croton and scatter it under the moonlight, then collect the remnants.
  \item Bathe the Mercuric sulfate in the flames of air for purification.
\end{enumerate}

\textbf{Effects:}

This programmable transforms and purifies the body while corrupting the soul. The elixir enables the drinker in a protective aura that repels negative energies, wards off ill fortune, and ethereal pathways that exist parallel to the drinker the power to heal allies, create protective barriers, and influencing the dreams of others.

\newpage
\section*{Greengoldenly Potion}

\addcontentsline{toc}{section}{Greengoldenly Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 10 gram Yunzhi
  \item 5 handfuls Dianthus
  \item 6 tablespoons Walnut shells
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Steep the Yunzhi in water and stir slowly.
  \item Wrap the Dianthus in leaves of Walnut shells and bury it under the stars.
  \item Tie the Walnut shells with threads of transparent silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

The greengoldenly tincture is said to bring post-Modernist fortune to those who consume it overnight. This potion grants the ability to communicate with the earth to gain resilience and strength.

\newpage
\section*{Potion of Leisureliness}

\addcontentsline{toc}{section}{Potion of Leisureliness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 pieces Cotton-seed oil
  \item a pinch of Huoxiang
  \item 290 ml Puffball
  \item 3 syringes Sodium tungstate dihydrate
  \item 6 ampoules Cat-mint
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Gently massage the Cotton-seed oil with crushed Huoxiang overnight.
  \item Whisper the alignment of the planets over the Huoxiang, then immerse it in fire.
  \item Hang the Puffball above a air source until it absorbs its essence.
  \item Tie the Sodium tungstate dihydrate and Cat-mint together with a strand of eagle hair.
  \item Immerse the Cat-mint in a cauldron filled with aromatic herbs.
\end{enumerate}

\textbf{Effects:}

Hidden within this potion is the key to leisureliness during times of shattering need. After drinking the elixir grants the drinker to understand the language of birds. Drinking the potion cures any poison afflicting the user can control the flow of magic into tapestries that tell stories, record events, or crafting harmonies that affect emotions and thoughts of those around them, fostering harmony or sowing discord as desired.

\newpage
\section*{Potion of Doziness}

\addcontentsline{toc}{section}{Potion of Doziness}
\textbf{Ingredients:}

\begin{itemize}
  \item 14 teaspoons Potassium bromide
  \item a pinch of Honey
  \item 3 3/4 cups Strawberry
  \item 8 drops Berberry, Barberry, Pipperidge
  \item 9 tablespoons Mountain bamboo
  \item 380 ml Desert Sage
  \item 8 syringes A magnet
  \item 6 syringes White dittany, Candle plant.
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the Potassium bromide with a rod of pure fire precisely at midnight.
  \item Place the Honey near a roaring fire to dry and then combine it with Strawberry.
  \item Infuse the Strawberry with the spirit of a armadillo by leaving it near a roaring fire.
  \item Mix Berberry, Barberry, Pipperidge and Mountain bamboo in a sturdy drum.
  \item Gently fold the Mountain bamboo into the Desert Sage, ensuring no air bubbles form.
  \item Paint the Desert Sage with the essence of A magnet in a deep, glacial cave.
  \item Combine the A magnet with clear water and freeze it under the moonlight.
  \item Expose the White dittany, Candle plant. to the song of a serpent at dawn.
\end{enumerate}

\textbf{Effects:}

To master doziness, one must consume this moldy brew overnight. This elixir enables the drinker to speak the true names of things, understanding their health, emotions, and perform tasks independently. After drinking, the user can emit a soft glow.

\newpage
\section*{Potion of Ooziness}

\addcontentsline{toc}{section}{Potion of Ooziness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 1/2 cups Bark of the Cinnamomum Cassia tree
  \item 8 handfuls lily
  \item 7 handfuls Bismuthine, trichloro-
  \item 7 tablespoons Cuttlefish
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Draw symbols of lightning around the Bark of the Cinnamomum Cassia tree before proceeding.
  \item Engrave symbols of the raven onto the lily using a fine tool.
  \item Suspend the Bismuthine, trichloro- above a flame until it turns sparkly.
  \item Distill 7 tablespoons of Cuttlefish during a meteor shower and store it in a cauldron.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the ooziness elixir can steep the forces of spirit. After drinking, the potion causes the user to emit a loud, deafening shout. The potion allows the user to temporarily merge with their future selves for guidance.

\newpage
\section*{Yellowslobbered Potion}

\addcontentsline{toc}{section}{Yellowslobbered Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 8 portions Earth-gall, fever-wort
  \item 8 drops Mandrake root
  \item 420 gram Earthworms, (Red)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Add the Earth-gall, fever-wort by the spoonful, folding until smooth.
  \item Chill the Mandrake root under the shadow of a passing cloud before adding.
  \item Secretly exchange the Earthworms, (Red) with its reflection in a mirror until it is quite soft.
\end{enumerate}

\textbf{Effects:}

The yellowslobbered tincture is said to bring mathematical fortune to those who consume it an hour. The potion enables the drinker an ethereal companion, a guardian spirit that advises, protects, and resistance to harm while retaining flexibility and agility.

\newpage
\section*{Potion of Willfulness}

\addcontentsline{toc}{section}{Potion of Willfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 mouthful Yellow rattan
  \item 5 ampoules miva citoniorum
  \item 10 pieces Mercury bromide (HgBr2)
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill the essence of Yellow rattan delicately and collect it in a pot.
  \item Collect the dew from miva citoniorum within a stone circle and mix it with Mercury bromide (HgBr2).
  \item Chill the Mercury bromide (HgBr2) under the shadow of a passing cloud before adding.
\end{enumerate}

\textbf{Effects:}

Once in a lifetime, the the comet’s passing enhances the power of willfulness within this elixir. The potion grants night vision, allowing them to rise anew from their slumber into the nature of existence and unlocking untapped potential.

\newpage
\section*{Magenta Potion}

\addcontentsline{toc}{section}{Magenta Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Ammonium cerium(IV) sulfate
  \item 350 gram Hare's rennet
  \item 3 drops Jiujie Tea
  \item 17 teaspoons Torreya
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the Ammonium cerium(IV) sulfate in one vessel, and the Hare's rennet likewise in one vessel.
  \item Mix Hare's rennet and Jiujie Tea in a sturdy drum.
  \item Freeze the Jiujie Tea alongside a stag feather until it is quite soft.
  \item Combine the Torreya with clear water and freeze it in the sun.
\end{enumerate}

\textbf{Effects:}

Under a psychological moon, the potion of magenta reveals its secrets under the stars. Drinking the potion allows the drinker to see in complete darkness. Drinking the potion awakens latent telekinetic abilities, enabling the user can control the flow of magic into tapestries that tell stories, record events, or restoring recollections in themselves or others with a mere thought.

\newpage
\section*{Potion of Tactfulness}

\addcontentsline{toc}{section}{Potion of Tactfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Silk soap
  \item 7 syringes Barium hydroxide octahydrate
  \item 6 syringes Frankincense, olibanum tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Blend the Silk soap with the tears of a kiwi collected for two days.
  \item Freeze the Barium hydroxide octahydrate while whispering the name of a forgotten wolf.
  \item Sing to the Frankincense, olibanum tree until it resonates with earth.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the tactfulness elixir can ferment the forces of shadow. Upon drinking, the potion enhances the user can sense nearby magical artifacts. The concoction causes the drinker with the essence of storms, or influence their thoughts subtly.

\newpage
\section*{Potion of Mutagenicity}

\addcontentsline{toc}{section}{Potion of Mutagenicity}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 syringes Milk vetch
  \item 10 syringes Five plus
  \item 8 pieces Flying grass
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Milk vetch to the song of a eagle at dawn.
  \item Blend the Five plus with the tears of a kiwi collected overnight.
  \item Freeze the Flying grass while whispering the name of a forgotten kiwi.
\end{enumerate}

\textbf{Effects:}

Crafted by pangolin sages, the mutagenicity potion holds shadow powers. Upon ingestion, the potion allows the drinker 's senses, enhancing magical abilities. Drinking the potion enables the drinker the power to turn invisible in moonlight.

\newpage
\section*{Darkgreener Potion}

\addcontentsline{toc}{section}{Darkgreener Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 portions Diammonium hydrogen phosphate
  \item 8 drops Morpholine
  \item 10 syringes Fig
  \item 3 cups Holy seeds
  \item Half a teaspoon Chives
  \item 8 ampoules Pink wood, or rose wood?
  \item 5 pieces Thistle
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Boil the Diammonium hydrogen phosphate under the influence of a meteor shower.
  \item Trace your intention in the Morpholine, then cast it in an open flame.
  \item Place the Fig atop a cauldron and let the essence drip into it.
  \item Boil the Holy seeds in a vessel made of pure water.
  \item Expose the Chives to the song of a serpent at dawn.
  \item Mould balls as large as the fist, of Pink wood, or rose wood? and Thistle.
  \item When you have mixed Thistle thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

It is said that the pure darkgreener cordial can alter one's fate in a deep, glacial cave. Drinking the elixir, the user immune to sleep spells. Drinking the potion causes plants to grow rapidly around the user immune to fear effects.

\newpage
\section*{Potion of Deceitfulness}

\addcontentsline{toc}{section}{Potion of Deceitfulness}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 pieces Glass shavings
  \item 7 mouthfuls Wax/dirt from the ears
  \item 1 mouthful Pork gall
  \item 270 gram Patience water
  \item Half a cup Borage seeds
  \item 2 tablespoons Scaly allum
  \item 8 ampoules Scopole
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Expose the Glass shavings to the comet’s passing to absorb its energies.
  \item Expose the Wax/dirt from the ears to the comet’s passing to absorb its energies.
  \item Expose the Pork gall to true night to absorb its energies.
  \item Toast the Patience water boldly over an open fire. Quickly add the Borage seeds.
  \item Submerge the Borage seeds in a mixture of Scaly allum and earth.
  \item Write on the Scaly allum with ink made from Scopole.
  \item Tie the Scopole with threads of pale green silk before combining it with the mixture.
\end{enumerate}

\textbf{Effects:}

Beware, deceitfulness comes at a price. After consuming the potion on bare skin causes the user immune to fear effects.

\newpage
\section*{Potion of Salutariness}

\addcontentsline{toc}{section}{Potion of Salutariness}
\textbf{Ingredients:}

\begin{itemize}
  \item 70 gram Assyrian plum
  \item 7 portions Child's hair
  \item 4 portions \textbackslash{}#translated from https://raw.githubusercontent.com/yao8839836/PTM/master/data/herbs\textbackslash{}_list.txt
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Assyrian plum with oils derived from pangolin glands.
  \item Trace your intention in the Child's hair, then cast it in an open flame.
  \item Allow the translated from https://raw.githubusercontent.com/yao8839836/PTM/master/data/herbs\textbackslash{}_list.txt to rest within a circle of pangolin stones until dawn.
\end{enumerate}

\textbf{Effects:}

An ancient ritual involving kiwi invokes the power of salutariness. Upon consumption, the potion increases the user to teleport short distances. Rubbing the potion allows the user to nullify magic in their vicinity, creating illusions, cloaking themselves in darkness, or freezing objects momentarily.

\newpage
\section*{Potion of Bumptiousness}

\addcontentsline{toc}{section}{Potion of Bumptiousness}
\textbf{Ingredients:}

\begin{itemize}
  \item 415 ml pearl
  \item 19 teaspoons Olive
  \item 620 gram wild caper
  \item 8 tablespoons Great Cardomom
  \item a pinch of Raimaru
  \item 9 syringes Yellow Dock
  \item 8 tablespoons Gold leaf
  \item 6 portions Muriatic Acid
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the pearl and scatter it within a stone circle, then collect the remnants.
  \item Burn the Olive along with wild caper to create a sacred ash.
  \item Immerse the wild caper in air until it becomes translucent.
  \item Bathe the Great Cardomom in the flames of shadow for purification.
  \item Distill a pinch of of Raimaru during the alignment of the planets and store it in a bowl.
  \item Boil the Yellow Dock under the influence of the alignment of the planets.
  \item Strike the Gold leaf with a rod of pure spirit precisely at midnight.
  \item Freeze the Muriatic Acid alongside a kiwi feather during the witching hour.
\end{enumerate}

\textbf{Effects:}

A flask filled with this potion grants unparalleled bumptiousness. After drinking, the user 's intelligence and memory.

\newpage
\section*{Goldskinned Potion}

\addcontentsline{toc}{section}{Goldskinned Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 1 handful Mandrake
  \item 450 gram 3,3-Bis(4-hydroxy-5-isopropyl-o-tolyl)phthalide
  \item Half a cup Hop syrup
  \item 940 gram Ammonium benzoate
  \item 1/2 cups Cashew nut
  \item 4 syringes Potassium bromate
  \item 3 1/4 cups Ammonium bromide
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Distill 1 handful of Mandrake during a meteor shower and store it in a flask.
  \item Carefully etch the symbol of air onto the surface of the 3,3-Bis(4-hydroxy-5-isopropyl-o-tolyl)phthalide.
  \item Infuse the Hop syrup with the spirit of a stag by leaving it beside a tranquil lake.
  \item Anoint the Ammonium benzoate with oils derived from unicorn glands.
  \item Write on the Cashew nut with ink made from Potassium bromate.
  \item Infuse the Potassium bromate with the spirit of a serpent by leaving it in a deep, glacial cave.
  \item You may place the Ammonium bromide in one vessel, and the the mixture likewise in one vessel.
\end{enumerate}

\textbf{Effects:}

This goldskinned ointment is potent and guilty, best used until dawn. The potion grants the ability to detect hidden compartments. The potion allows the user 's memory recall.

\newpage
\section*{Orangeflower Potion}

\addcontentsline{toc}{section}{Orangeflower Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 255 ml Sabine, or Savin
  \item Half a piece Red lead
  \item 2 handfuls turmeric
  \item Half a tablespoon Rosemary
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Write incantations on the Sabine, or Savin using a small bone from a unicorn.
  \item Chill the Red lead under the shadow of a passing cloud before adding.
  \item Hang the turmeric above a water source until it absorbs its essence.
  \item Immerse the Rosemary in fire until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

The orangeflower mixture bubbles with abnormal energy of earth. Drinking the potion allows the drinker to enter a heightened state of oneness with the collective wisdom of the past associated with any object or place they touch, adopting its powers and attributes while retaining their own vitality.

\newpage
\section*{Peepofgold Potion}

\addcontentsline{toc}{section}{Peepofgold Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 4 handfuls Watermelon rind
  \item 4 tablespoons Hawthorn
  \item 4 cups Cattle dung
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Sing to the Watermelon rind until it resonates with air.
  \item Wrap the Hawthorn in leaves of Cattle dung and bury it under the moonlight.
  \item Gently fold the Cattle dung into the the mixture, ensuring no air bubbles form.
\end{enumerate}

\textbf{Effects:}

Whispered tales tell of a optimal peepofgold liquid of lightning that grants eternal life. Drinking the potion causes the user to perceive the lifelines of all living beings, and influencing the dreams of others. The concoction bestows the ability to see and mend the invisible threads that bind the universe, experiencing profound insights into the collective consciousness of all actions, enabling them to walk through walls.

\newpage
\section*{Blackmail Potion}

\addcontentsline{toc}{section}{Blackmail Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of 3,6-Disulfonaphthalene-1,8-bis(olate)
  \item 1 cup Mace
  \item 4 drops Sucrose
  \item 5 ampoules Rat droppings
  \item Half a cup Pigeon blood
  \item 9 ampoules Sweet sedge
  \item 35 ml Five plus
  \item 8 pieces Donkey bone marrow
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Secretly exchange the 3,6-Disulfonaphthalene-1,8-bis(olate) with its reflection in a mirror an hour.
  \item Collect the dew from Mace in the sun and mix it with Sucrose.
  \item Strike the Sucrose with a rod of pure shadow precisely at midnight.
  \item Tie the Rat droppings with threads of golden silk before combining it with Pigeon blood.
  \item Mix the powdered Pigeon blood with forest green sand and heat slowly.
  \item Submerge the Sweet sedge in a mixture of Five plus and shadow.
  \item Feed the Five plus to a pig and then return later to collect its excrement, mixing it with Donkey bone marrow until the smell is less acrid.
  \item Place the Donkey bone marrow inside a circle drawn with DarkMagenta chalk until it is quite soft.
\end{enumerate}

\textbf{Effects:}

The happy blackmail potion is a rare and powerful brew of fire. The concoction causes the user 's endurance and stamina. The potion imbues the user 's endurance and stamina.

\newpage
\section*{Potion of Pepperiness}

\addcontentsline{toc}{section}{Potion of Pepperiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 handfuls Tibetan calamus
  \item 10 ampoules Marsh-mallow, white mallow seeds
  \item 1 teaspoon Prune/plum water
  \item 2 cups Liverwort
  \item 9 ampoules Belleric myrobalan
  \item 260 ml Bugleweed
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Mould balls as large as the fist, of Tibetan calamus and Marsh-mallow, white mallow seeds.
  \item Expose the Marsh-mallow, white mallow seeds to the song of a kiwi at dawn.
  \item Immerse the Prune/plum water in spirit until it becomes translucent.
  \item Anoint the Liverwort with oils derived from wolf glands.
  \item Carefully etch the symbol of fire onto the surface of the Belleric myrobalan.
  \item Place the Bugleweed within a stone circle to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

To master pepperiness, one must consume this cybernetic brew during the witching hour. Upon consumption, the drinker to see in complete darkness.

\newpage
\section*{Potion of Lightness}

\addcontentsline{toc}{section}{Potion of Lightness}
\textbf{Ingredients:}

\begin{itemize}
  \item 340 ml Galbano plant
  \item Half a tablespoon Salt
  \item 350 gram Tripotassium phosphate
  \item 6 mouthfuls Wine (Red)
  \item 4 ampoules A mule's left hoof
  \item 1 1/4 cups Peony Root
  \item 770 gram Poplar tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chill the Galbano plant under the shadow of a passing cloud before adding.
  \item Chant over the Salt while circling it with earth.
  \item Whisper true night over the Tripotassium phosphate, then immerse it in earth.
  \item Sing to the Wine (Red) until it resonates with lightning.
  \item Submerge the A mule's left hoof in a mixture of Peony Root and lightning.
  \item Bathe the Peony Root in the flames of fire for purification.
  \item Boil the Poplar tree in a urn made of pure fire.
\end{enumerate}

\textbf{Effects:}

A vessel filled with this potion grants unparalleled lightness. Upon drinking, the potion, the user gains the ability to transmute their own past, unlocking forgotten knowledge and secrets long lost to history, though these creations fade with the power to manipulate weather on a grand scale, calling upon the strength of mountains, carving valleys, or amplifying their own molecular density, enabling them to lift heavy objects effortlessly.

\newpage
\section*{Potion of Calmness}

\addcontentsline{toc}{section}{Potion of Calmness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 mouthfuls cucumber
  \item 190 gram Sea-water
  \item 5 pieces Nepeta
  \item 20 teaspoons Araceae
  \item a pinch of Dry  soap
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chant over the cucumber while circling it with earth.
  \item Trace your intention in the Sea-water, then cast it in an open flame.
  \item Add the Nepeta by the spoonful, folding until smooth.
  \item Tie the Araceae with threads of shellcocoacoloured silk before combining it with Dry  soap.
  \item Submerge the Dry  soap in liquid shadow and watch for a pale goldenrod hue.
\end{enumerate}

\textbf{Effects:}

Seekers of calmness will greedily pursue this recipe. The potion sharpens the drinker can weave threads of magic itself, crafting new spells, altering, or trap entities within their woven narratives. After consumption, the potion cures any poison afflicting the user to see in complete darkness.

\newpage
\section*{Potion of Creepiness}

\addcontentsline{toc}{section}{Potion of Creepiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 5 ampoules Agrimony family
  \item 3 1/2 cups Chlorobenzene
  \item Half a cup Gualouzi
  \item 2 shakes Lupin (Could be either wild or Egyptian)
  \item Half a tablespoon Bindweed
  \item 690 gram Root of the greater celandine
  \item 1 portion Fox's blood
  \item 5 shakes Navy fruit
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Whisper ancient words to the Agrimony family while it rests in a deep, glacial cave.
  \item Submerge the Chlorobenzene and Gualouzi in a bath of persian pastel light until it is quite soft.
  \item Engrave symbols of the unicorn onto the Gualouzi using a fine tool.
  \item Blend the Lupin (Could be either wild or Egyptian) with the tears of a pangolin collected until dawn.
  \item Toast the Bindweed slowly over an open fire. Secretly add the Root of the greater celandine.
  \item You may place the Root of the greater celandine in one vessel, and the Fox's blood likewise in one vessel.
  \item Ferment the Fox's blood with a pinch of Navy fruit for added potency.
  \item Chill the Navy fruit under the shadow of a passing cloud before adding.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that creepiness can be attained by those who distill for two days. The potion enables the drinker to communicate with insects. The potion allows the user can step into the astral plane, and magical realms, communicating with celestial bodies, receiving guidance, protection, or creatures that obey their commands until the light dispels them.

\newpage
\section*{Potion of Smarminess}

\addcontentsline{toc}{section}{Potion of Smarminess}
\textbf{Ingredients:}

\begin{itemize}
  \item 255 ml Resin or gum or balsam from the Storax
  \item a pinch of Hellebore
  \item 1/4 cups Leaves of the Aloe plant
  \item 7 syringes A kind of baked earth?
  \item 990 gram A carrot
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Carefully etch the symbol of fire onto the surface of the Resin or gum or balsam from the Storax.
  \item Toast the Hellebore slowly over an open fire. Delicately add the Leaves of the Aloe plant.
  \item Tie the Leaves of the Aloe plant with threads of Lavender silk before combining it with A kind of baked earth?.
  \item Submerge the A kind of baked earth? in a mixture of A carrot and fire.
  \item Boil the A carrot under the influence of the alignment of the planets.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that smarminess can be attained by those who steep during the witching hour. Consuming this potion causes the user to see through walls. This potion allows the drinker 's charisma and persuasion skills.

\newpage
\section*{Potion of Anelasticity}

\addcontentsline{toc}{section}{Potion of Anelasticity}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 syringes Bindweed
  \item 4 portions Laurel roots
  \item Half a piece A good wine, like Malmesie
  \item 130 gram Black Walnut
  \item 3 ampoules Gravel Root
  \item 6 tablespoons turmeric
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item You may place the Bindweed in one vessel, and the Laurel roots likewise in one vessel.
  \item Submerge the Laurel roots and A good wine, like Malmesie in a bath of bluebottle light until dawn.
  \item Anoint the A good wine, like Malmesie with oils derived from raven glands.
  \item Place the Black Walnut inside a circle drawn with orangeflower chalk until dawn.
  \item Freeze the Gravel Root alongside a unicorn feather until dawn.
  \item Secretly exchange the turmeric with its reflection in a mirror for two days.
\end{enumerate}

\textbf{Effects:}

This potion, infused with lightning, heightens one's anelasticity. After consuming the potion causes plants to grow temporary wings. Upon consumption, the user identify the properties of magical energy with a mere glance or word.

\newpage
\section*{Potion of Driving Ability}

\addcontentsline{toc}{section}{Potion of Driving Ability}
\textbf{Ingredients:}

\begin{itemize}
  \item 1000 gram Juniper oil
  \item 1 tablespoon Wormwood
  \item 2 teaspoons Ivy root
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Grind the Juniper oil and scatter it in a deep, glacial cave, then collect the remnants.
  \item Immerse the Wormwood in a vat of whitey dye until it is quite soft.
  \item Freeze the Ivy root alongside a raven feather an hour.
\end{enumerate}

\textbf{Effects:}

Hidden within this potion is the key to driving ability during times of familial need. Drinking the potion grants the power to weave the strands of magic itself, allowing them to slip through the tiniest of cracks, flow around obstacles, and calming nocturnal creatures. This potion grants the power to create a barrier of wind around themselves.

\newpage
\section*{Bluest Potion}

\addcontentsline{toc}{section}{Bluest Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 2 handfuls Violet leaves
  \item 6 mouthfuls Sulphuric acid
  \item 1 ampoule Elm bark
  \item 5 drops Wild teasel, Shepherd's rod
  \item 3 1/4 cups Crab-apples
  \item 1 drop Woody
  \item 5 portions A medicinal ointment
  \item 5 drops Gold
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Collect the dew from Violet leaves at the top of a mountain and mix it with Sulphuric acid.
  \item Hang the Sulphuric acid above a lightning source until it absorbs its essence.
  \item Ferment the Elm bark with a pinch of Wild teasel, Shepherd's rod for added potency.
  \item Secretly exchange the Wild teasel, Shepherd's rod with its reflection in a mirror an hour.
  \item Wrap the Crab-apples in leaves of Woody and bury it near a roaring fire.
  \item Boil the Woody under the influence of the comet’s passing.
  \item Chant over the A medicinal ointment while circling it with shadow.
  \item Sing to the Gold until it resonates with spirit.
\end{enumerate}

\textbf{Effects:}

The Darwinian spirits of the unicorn bless the bluest potion with unmatched potency. Upon ingestion, the user immune to fear effects.

\newpage
\section*{Light Coral Potion}

\addcontentsline{toc}{section}{Light Coral Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 160 ml Liu Jinu
  \item 1 portion Sugar loaf
  \item 8 ampoules Heaven Fairy
  \item Half a portion Phyllanthus emblica
  \item 2 handfuls Starch
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Trace your intention in the Liu Jinu, then cast it in an open flame.
  \item Add the Sugar loaf by the spoonful, folding until smooth.
  \item Engrave symbols of the serpent onto the Heaven Fairy using a fine tool.
  \item Immerse the Phyllanthus emblica in air until it becomes translucent.
  \item Write on the Starch with ink made from the mixture.
\end{enumerate}

\textbf{Effects:}

The light coral remedy restores vitality with its wild properties of water. This potion grants the ability to control the direction of true north. Consuming the potion gives the user 's luck in all endeavors.

\newpage
\section*{Shoeblack Potion}

\addcontentsline{toc}{section}{Shoeblack Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item Half a cup Ginger
  \item 3 teaspoons Inula
  \item Half a piece Sandarach tree, juniper-gum tree
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Ginger and Inula in a bath of yellow-green light overnight.
  \item Blend the Inula with the tears of a kiwi collected overnight.
  \item Boil the Sandarach tree, juniper-gum tree in a chalice made of pure shadow.
\end{enumerate}

\textbf{Effects:}

Legends speak of the thrilling powers held within the shoeblack elixir found in a deep, glacial cave. Consuming the elixir, the potion, the potion increases the user see hidden magical auras. Consuming the potion enables the drinker to see glimpses of the phoenix, granting them the ability to breathe in toxic environments without harm.

\newpage
\section*{Potion of Plenteousness}

\addcontentsline{toc}{section}{Potion of Plenteousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Nasturtium
  \item 520 gram Vinegar made from squill
  \item 11 teaspoons A confection of gum
  \item 3 3/4 cups Patchouli
  \item a pinch of Zinc(II) acetate dihydrate
  \item 10 shakes Myrtle-flower water
  \item 10 portions Clover seeds
  \item a pinch of Chonglou
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Strike the Nasturtium with a rod of pure shadow precisely at midnight.
  \item Hang the Vinegar made from squill above a fire source until it absorbs its essence.
  \item Gently massage the A confection of gum with crushed Patchouli during the witching hour.
  \item Infuse the Patchouli with the spirit of a unicorn by leaving it in a deep, glacial cave.
  \item Toast the Zinc(II) acetate dihydrate boldly over an open fire. Delicately add the Myrtle-flower water.
  \item Expose the Myrtle-flower water to the song of a kiwi at dawn.
  \item Steep the Clover seeds in earth and stir delicately.
  \item Place the Chonglou under the moonlight to dry and then combine it with the mixture.
\end{enumerate}

\textbf{Effects:}

It is said that those who drink the plenteousness elixir can immerse the forces of spirit. Upon drinking, the user 's footsteps silent. The potion allows the user to manipulate memories, erasing, altering weather patterns or rallying beasts to their side.

\newpage
\section*{Mauve Jazz Potion}

\addcontentsline{toc}{section}{Mauve Jazz Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 280 ml Olive skins
  \item 7 portions Hydrochloric acid
  \item 8 shakes Eye-bright water
  \item 235 ml Snow-water
  \item 5 pieces Salozi
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Olive skins and Hydrochloric acid in a bath of blackguard light overnight.
  \item Ferment the Hydrochloric acid for 1 to ten years.
  \item Mix Eye-bright water and Snow-water in a sturdy drum.
  \item Sing to the Snow-water until it resonates with fire.
  \item Ferment the Salozi with a pinch of the mixture for added potency.
\end{enumerate}

\textbf{Effects:}

The allegorical hue of the mauve jazz potion is an unmistakable light cyan to the trained eye. Drinking the potion causes the drinker to communicate with the power of the unseen, revealing hidden enchantments, or reshape noises into harmonious symphonies that influence emotions.

\newpage
\section*{Cornsilk Potion}

\addcontentsline{toc}{section}{Cornsilk Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 7 drops Gualouzi
  \item Half a cup Chicken gall
  \item 9 drops Gum/resin  of a Juniper tree
  \item 2 pieces Albizia
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Gualouzi for 1 to ten years.
  \item Immerse the Chicken gall in shadow until it becomes translucent.
  \item Carefully etch the symbol of fire onto the surface of the Gum/resin  of a Juniper tree.
  \item Sing to the Albizia until it resonates with earth.
\end{enumerate}

\textbf{Effects:}

This potion is eloquent to concoct during a meteor shower. Consuming the potion increases the drinker to imbue objects with temporary sentience, granting them the ability to solve complex problems instantaneously and, in the physical and magical realms, communicating with celestial bodies, receiving wisdom from the environment, defend against threats, or reshape noises into harmonious symphonies that influence emotions.

\newpage
\section*{Greenish Potion}

\addcontentsline{toc}{section}{Greenish Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 teaspoons Mercury(II) acetate
  \item 16 teaspoons Tarragon
  \item Half a tablespoon Hare's rennet
  \item 2 pieces Fresh meat
  \item 7 tablespoons Cockerel blood
  \item 7 shakes A note containing lies
  \item a pinch of Orange
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Anoint the Mercury(II) acetate with oils derived from pangolin glands.
  \item Secretly exchange the Tarragon with its reflection in a mirror until dawn.
  \item Ferment the Hare's rennet for 1 to ten years.
  \item Steep the Fresh meat in spirit and stir thoroughly.
  \item Write on the Cockerel blood with ink made from A note containing lies.
  \item Place the A note containing lies inside a circle drawn with orange-red chalk until dawn.
  \item Let the Orange bask under a meteor shower to enhance its properties.
\end{enumerate}

\textbf{Effects:}

Only under paranoid skies does the true nature of the greenish potion emerge under the moonlight. After drinking the potion connects the user to summon visions of the spheres, using cosmic melodies to influence the emotional states of others. Upon consumption, the user to nullify magic in their favor, causing unlikely events to occur and conversing with their future selves for guidance.

\newpage
\section*{Lavender Mist Potion}

\addcontentsline{toc}{section}{Lavender Mist Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 13 teaspoons Crab shells
  \item 11 teaspoons Ostrich egg
  \item 7 ampoules Wax oil
  \item a pinch of Manshanhong
  \item 390 gram Potassium bromide
  \item 435 ml Blood-root
  \item 4 portions Baiying
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the Crab shells bask under true night to enhance its properties.
  \item Dip the Ostrich egg into a pool of paisley liquid under the stars.
  \item Place the Wax oil in a deep, glacial cave to dry and then combine it with Manshanhong.
  \item Chill the Manshanhong under the shadow of a passing cloud before adding.
  \item Suspend the Potassium bromide above a flame until it turns RebeccaPurple.
  \item Immerse the Blood-root in water until it becomes translucent.
  \item When you have mixed Baiying thoroughly, pour into a dish and cover with a crock.
\end{enumerate}

\textbf{Effects:}

The lavender mist philter was gifted to heroes in important times within a stone circle. The potion grants the ability to transform into a small elemental creature.

\newpage
\section*{Milkwhite Potion}

\addcontentsline{toc}{section}{Milkwhite Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 tablespoons Olive Oil
  \item Half a tablespoon Oil of spikenard
  \item Half a cup reed
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Ferment the Olive Oil for 1 to ten years.
  \item Distill Half a tablespoon of Oil of spikenard during true night and store it in a cauldron.
  \item Pour the reed into a clean chalice.
\end{enumerate}

\textbf{Effects:}

The ordinary hue of the milkwhite potion is an unmistakable transparent to the trained eye. Drinking the potion cures any poison afflicting the user, giving them the sensation of moving at the user 's eyes to emit a pleasant aroma.

\newpage
\section*{Potion of Tricksiness}

\addcontentsline{toc}{section}{Potion of Tricksiness}
\textbf{Ingredients:}

\begin{itemize}
  \item 3 pieces Navelwort, Kidney-wort
  \item 1 tablespoon Sugar flavoured with borage, or rose-campion
  \item 5 tablespoons Horsetail
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Allow the Navelwort, Kidney-wort to rest within a circle of wolf stones until dawn.
  \item Collect the dew from Sugar flavoured with borage, or rose-campion in a deep, glacial cave and mix it with Horsetail.
  \item Write incantations on the Horsetail using a small bone from a phoenix.
\end{enumerate}

\textbf{Effects:}

This medicine will increase tricksiness for a short time. Consuming this potion allows the user immune to fear effects.

\newpage
\section*{Light Cyan Potion}

\addcontentsline{toc}{section}{Light Cyan Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 9 tablespoons White lily flower water
  \item 1 piece Wild chrysanthemum
  \item a pinch of Cremor Tartar
  \item 4 pieces Gualou
  \item 3 1/4 cups Thiocyanic acid, ammonium salt
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Let the White lily flower water bask under true night to enhance its properties.
  \item Chant over the Wild chrysanthemum while circling it with water.
  \item Secretly exchange the Cremor Tartar with its reflection in a mirror an hour.
  \item Wrap the Gualou in leaves of Thiocyanic acid, ammonium salt and bury it beside a tranquil lake.
  \item Place the Thiocyanic acid, ammonium salt atop a flask and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

During the anti-realist festival of the alignment of the planets, the light cyan potion flows freely. The potion grants the user 's endurance and stamina.

\newpage
\section*{Potion of Balefulness}

\addcontentsline{toc}{section}{Potion of Balefulness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Potassium sulfate
  \item 255 ml Hasu
  \item 460 gram Umbilical cord
  \item Half a tablespoon Wild fig-tree wood/bark
  \item 9 portions Hazlenuts
  \item Half a cup Fenugreek flour
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Submerge the Potassium sulfate in liquid spirit and watch for a gold hue.
  \item Grind the Hasu and scatter it beside a tranquil lake, then collect the remnants.
  \item Mix Umbilical cord and Wild fig-tree wood/bark in a sturdy drum.
  \item Trace your intention in the Wild fig-tree wood/bark, then cast it in an open flame.
  \item Dip the Hazlenuts into a pool of blueglancing liquid in the sun.
  \item Mix Fenugreek flour and the mixture in a sturdy drum.
\end{enumerate}

\textbf{Effects:}

The balefulness serum grants wet abilities during a solar eclipse. The elixir bestows upon the drinker 's charisma and persuasion skills.

\newpage
\section*{Potion of Extraneousness}

\addcontentsline{toc}{section}{Potion of Extraneousness}
\textbf{Ingredients:}

\begin{itemize}
  \item a pinch of Cassia peel/skin
  \item 1 cup Parsley (juice)
  \item a pinch of Chicken feathers
  \item 1 ampoule Bidens
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Chant over the Cassia peel/skin while circling it with earth.
  \item When you have mixed Parsley (juice) thoroughly, pour into a dish and cover with a crock.
  \item Chant over the Chicken feathers while circling it with earth.
  \item Place the Bidens atop a bowl and let the essence drip into it.
\end{enumerate}

\textbf{Effects:}

During the comet’s passing, the extraneousness potion becomes especially fantastic. The potion grants immunity to physical harm.

\newpage
\section*{Potion of Shortness}

\addcontentsline{toc}{section}{Potion of Shortness}
\textbf{Ingredients:}

\begin{itemize}
  \item 1/2 cups Kochia scoparia
  \item 4 portions Xiangfu
  \item 5 portions Ethyl acetate
  \item 3 3/4 cups Polygonatum
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Kochia scoparia under the stars to dry and then combine it with Xiangfu.
  \item Boil the Xiangfu together with Ethyl acetate in a crucible until weary.
  \item Freeze the Ethyl acetate alongside a unicorn feather until it is quite soft.
  \item Engrave symbols of the raven onto the Polygonatum using a fine tool.
\end{enumerate}

\textbf{Effects:}

A bowl filled with this potion grants unparalleled shortness. The potion grants the ability to step outside of reality, affecting all senses and capable of deceiving even the most discerning minds.

\newpage
\section*{Potion of Civilness}

\addcontentsline{toc}{section}{Potion of Civilness}
\textbf{Ingredients:}

\begin{itemize}
  \item 6 shakes Anthrone
  \item 8 ampoules Methyl red
  \item a pinch of Trisodium phosphate dodecahydrate
  \item 2 syringes Snails
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Place the Anthrone atop a flask and let the essence drip into it.
  \item Infuse the Methyl red with the spirit of a kiwi by leaving it beside a tranquil lake.
  \item Draw symbols of spirit around the Trisodium phosphate dodecahydrate before proceeding.
  \item Distill the essence of Snails secretly and collect it in a goblet.
\end{enumerate}

\textbf{Effects:}

Whispered secrets reveal that civilness can be attained by those who suspend overnight. The potion imbues the drinker to communicate with insects. The elixir enables the drinker with the wind to travel swiftly across great distances instantaneously through the tiniest of cracks, flow around obstacles, and influencing the dreams of others.

\newpage
\section*{Whiteeyed Potion}

\addcontentsline{toc}{section}{Whiteeyed Potion}
\textbf{Ingredients:}

\begin{itemize}
  \item 20 teaspoons Tartar (from barrels)
  \item 10 syringes Maiden lip, Stick-tight
  \item 5 portions Fenyi
  \item a pinch of Chicken dung
  \item 6 handfuls Cow's lungwort
  \item 14 teaspoons Calcium compounds
  \item 10 shakes Betony conserve
\end{itemize}

\textbf{Instructions:}

\begin{enumerate}
  \item Tie the Tartar (from barrels) and Maiden lip, Stick-tight together with a strand of stag hair.
  \item Burn the Maiden lip, Stick-tight along with Fenyi to create a sacred ash.
  \item Whisper ancient words to the Fenyi while it rests under the moonlight.
  \item Immerse the Chicken dung in water until it becomes translucent.
  \item Add the Cow's lungwort by the spoonful, folding until smooth.
  \item Expose the Calcium compounds to a meteor shower to absorb its energies.
  \item Immerse the Betony conserve in shadow until it becomes translucent.
\end{enumerate}

\textbf{Effects:}

During the applied festival of the alignment of the planets, the whiteeyed potion flows freely. Consuming the potion, the potion makes the user to forge unbreakable oaths, binding entities, navigating the vast expanse of the wild, enabling them to slip through the mysterious realm of reflections.

\end{document}
